\documentclass[11pt]{article}

% to set margins as i inch
\usepackage{fullpage}

% set paragraph spacing
\setlength{\parskip}{10pt}

% to include links in the table of contents
\usepackage{xcolor}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=olive,  %choose some color if you want links to stand out
}




\begin{document}

% titlepage
\begin{titlepage}
\title{Free Canvas}
\author{Alex.X.L}
\date{\today} % automatically changes every compilation
\maketitle
\thispagestyle{empty} % removes page number from this title page
\end{titlepage}



% table of contents, auto generated. Have to click build twice.
\tableofcontents
\newpage % same function as MS Word page break






\section{Title ideas}
Title should invoke questions, be easy to pronounce, and be less than 5 words. 

1. Aliens in Oceania

2. \textbf{Oceania of Stars}

3. The Oceania Syndrome

\section{Opening Narrations}
Opening narration should contain hooks, or at least prompt questions in the reader, however simple the questions may be.

1. NARRATION: Oceania was a nation that never outgrew Industry. With its orderly government, peaceful civil life, and at its heart a Factory Array - a magnificent, sentient entity that sprawled across the continent, producing every one of humanity's needs, many considered Oceania to be utopia. [Child running with ball. She falls over.] It was not. [Lucca stands afar. The ball rolls towards his feet.] However, while most imaginings of utopias in the bygone ages attempted to spin heaven into hell, Oceania was \textit{not} a dystopia either. [Lucca picks up the ball and walks to the kid.] It was something stranger, harder to understand, and perhaps more beautiful than both - Oceania, was humanity. [The child stands up, Lucca throws the ball and she catches it. Lucca walks on.]


\section{Possible Narratives}
They are in the form: goal, setback, response

1. A civil servant is ecstatic about the new alien sightings in his country. 

Despite his privileges, his desire to meet and study them is met with heavy resistance by the government for which he works. 

As he discovers the true origin of the aliens, he learns about humanity's own history, and a grand conspiracy emerges that threatens the future of the people on earth. 

He has to utilise the few centuries of planning by the country's founders to defeat said conspiracy.

\section{Questions Round 1}
Questions that flesh out each sentence in previous section.

\textbf{Why is it important that he is a civil servant? How does it play into the story?}

- He uses his authority to bypass normal barriers; his job is to investigate. 


\textbf{Why is he ecstatic about aliens?}

- He has a fascination with science and space. He is curious.


\textbf{What are some of his privileges?}

- He can visit notable figures and be greeted without guard. 
He has connections with many interesting and knowledgeable people.


\textbf{What does he want to learn about the aliens?}

- What the aliens look like, where they come from, whether there is a cross-species community in the universe. 
How smart the aliens are, what their world views are, what emotions they feel.
What their art looks like, what their science looks like, what their history looks like.
How they organise their society.


\textbf{What are the types of resistance he faces? }

- The government assigning him jobs away from his interest.
His job allowing him little time to explore.
His contacts suspiciously silent to his questions.
Eventually ordered not to investigate further.


\textbf{Why does the government want to stop him?}

- The aliens are actually not aliens, but instruments for the government's conspiracy.


\textbf{What is the origin of the aliens?}

- Human consciousness trapped.


\textbf{What is special about humanity's history?}

- The government was established by a secret society that sheperded humanity after world war 3. While the society valued peace and progress, their descendants (the government) has degenerated. 


\textbf{What is the conspiracy?}

- The government out of pity for humanity, wants to euthanise it by using the aliens to make everyone fall asleep in sync.


\textbf{Is he alone in his fight?}

- He will be joined by an astrophysicist, a historian and a neuroscientist.


\textbf{How did the country's founders foresee all this?}

- they were a secret society that watched over human history, and developed sophisticated mathematical science to describe the tendencies of the evolution of human societies.


\section{Necessary Plot Points}
Introduce to setting.

Lucca works at the Department of Anomalous Phenomenon. He hears about alien sightings somehow.

Lucca visits locations and tries to investigate. 

1. Star watcher

2. Susan's place next to a lighthouse.

His director Alma notices his absence from assigned tasks. Alma warns him to stop investigating or he will be fired. 

Lucca remembers conversation with mum when he was small, when his mum told him aliens are already in Oceania. Here we learn Lucca's distaste of the mundanity of life.

Lucca's enthusiasm only grows, but he has to find ways to investigate without the government's notice.



Lucca finally gets into contact with an alien but it's not what he was hoping for.



Lucca finds out what the aliens really are - carriers of a plague, currently raging in Oceania.

Lucca tells Susan that they have to leave Oceania.

Their efforts are stopped by the government. They give up, but Susan tells Lucca she will stay by his side.




Lucca and Susan walk through the city and discover the scribing on the Oceania Trainline's side glasses, tall concrete buildings, and underground shelters. 

They decode the message - it was a message left to them by the earliest builders of the city, to warn them about the Human Institute. 

At the same time, a revolution is brewing. 




The government's conspiracy succeeds and makes everyone sleep, except for a rare few people. 

Lucca finds them, and together they discover the "weapon" created by the founders of the city to destroy the object. 




\section{Ideas}
Ideas that I think are cool.

Using the City Loop and the concrete buildings littered across the city, to form a weapon that destroys something.

The (very) long and slightly shorter stripes on the fences around the trainline, become a morse code message when viewed at high speed.

People having memories of a different life, but can't find those events in their past. It turns out they are memories from their future - human minds have evolved.

Images/ flashes of a person appear at different locations and different times. This is due to when that person was destroyed, the pieces of their existence were scattered across spacetime. 

A scientist who is a fraud, with an equally distasteful view of themselves, proves themselves wrong by doing an act of good.
\newpage






\end{document}