\documentclass[11pt]{article}

% to set margins as i inch
\usepackage{fullpage}

% set paragraph spacing
\setlength{\parskip}{10pt}

% to include links in the table of contents
\usepackage{xcolor}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=olive,  %choose some color if you want links to stand out
}




\begin{document}

% titlepage
\begin{titlepage}
\title{What is to be Done}
\author{Alex.X.L}
\date{\today} % automatically changes every compilation
\maketitle
\thispagestyle{empty} % removes page number from this title page
\end{titlepage}



% table of contents, auto generated. Have to click build twice.
\tableofcontents
\newpage % same function as MS Word page break






\section{Research}

	\subsection{Narrative techniques}
	Read books from the Conspiracy Fiction genre, Mystery genre and Romance genre. 
	\subsection{Character building}
	Read any good book and think about how i am made to care.
	\subsection{Pacing}
	Find courses or read books and think about how the author creates a natural pace for the story to progress.
	\subsection{Deliverable}
	Write a compilation of the form "For the area of ... I learned ... from the book ..."
	
\section{Plan}
	\subsection{Decisions}
		Decide on the format of the story. Episodic, or a single story.
		
		Decide on the central thesis of the story.
		
		Decide on the primary conflict of the story.
		
		Decide on the resolution to that conflict.
		
		Decide on the spark to that conflict.
		
		Decide on the main developments of the conflict.
		
		Decide on all characters involved including their developments.
		
	\subsection{Deliverable}
		A synopsis of every chapter.
		
\section{Writing}
	Note down all main clues and threads running throughout the story.
	
	Start writing the scripts for every chapter in detail, visualising the panels.
	
	\subsection{Deliverable}
	A complete script.

\section{Story board}
Sketch out all panels from the chapters. SEND TO AN EDITOR.

\section{Draw}
Before committing to a style, draw out chapter 1 in both thick and thin markers. SEND TO AN EDITOR.

After style is selected, start seriously drawing every chapter. Do NOT take massive shortcuts; take it easy because life is long.

\section{Publish}
Publish onto Webtoon or Reddit.

\newpage


	




\end{document}