\documentclass[11pt]{article}

% to set margins as i inch
\usepackage{fullpage}

% set paragraph spacing
\setlength{\parskip}{10pt}




\begin{document}

% titlepage
\begin{titlepage}
\title{Synopsis for The Aztoria Syndrome}
\author{Alex}
\date{\today} % automatically changes every compilation
\maketitle
\thispagestyle{empty} % removes page number from this title page
\end{titlepage}

\newpage % same function as MS Word page break







\section{Skeleton}
	\subsection{Theme Statement}
	A celebration of history and humankind.
	\subsection{Two-Sentence Summary}
	Lucca is a member of the Civil Protection Institute that watches over the lonely city of Aztoria. Through the unravelling mysteries, he finds himself among history's greatest conspiracy and a city on the cusp of a grand revolution.
	\subsection{Apparent Story Questions}
	What is wrong with the city? $\rightarrow$ 
	What is the Aztoria Syndrome? $\rightarrow$  
	What is the history of the city, and humankind? $\rightarrow$ 
	Will, and how, will humans triumph?
\newpage




\section{Synopsis}
	\subsection{Act 1 - Wanderings}
		\subsubsection{Beneath the City Lights}
		The shore of Aztoria is full of colossal concrete structures with unknown purpose. 
		Lucca sees a flashing image of a woman in black. 
		
		In Aloh's communal dining space, Lucca partakes in a psychological operation by the CPI to lure out a murder confession, allowing them the chance to obtain a lighter sentence. 
		
		Lucca encounters an alien looking creature.
		First instance of hearing the song "Get on the A Train".

		\subsubsection{Monster in District 14}
		Monster is sighted in District 14 at night.
		Lucca investigates, remembering his encounter at night. 
		
		Turns out to be an old man who is a sleep walker who has been doing it ever since his wife passed away. 
		Lucca places his coat onto the old man and disperses the crowd.
		
		One of the residents – a girl – acts oddly.
		
		\subsubsection{Professor Lambda's Sorrow}
		Professor Lambda is the retiring head of neuroscience at Aztoria University. 
		Lucca is assigned to conduct the handover. 
		
		Professor Lambda has one big regret for his career, and acts with burden. 
		Him and Lucca just have a casual stroll through the university, interacting with curiosity. For example, Lucca asks the nature of consciousness, and Lambda describes how it is made of Currents of Information, travelling through spacetime. Lambda picks up a ring magnet and demonstrates how magnetic fields can shut down brain functions.
		They stop by a patient in one of the labs, and the patient describes their experience of dreaming about walking around the labs at night.
		
		They meet the new head of neuroscience – Susan, who was a highschool friend of Lucca. 
		Lambda hands over the sum of his lifetime research, and Susan speaks the pledge to the Aztorian State under Lucca’s supervision. 
		
		At the end, Lambda begs Lucca to grant him access to a city-wide broadcasting speaker, which Lucca grants. 
		In a shocking moment, Professor Lambda announces to all people that there is a plague in Aztoria, spilling a state secret, violating Aztorian law, thinking that he was a good scientist in the end.
		
		The plague is spread by black organisms called “Newons” that emerge from a patient’s head during sleep. The Newons are the creatures we have seen.

		\subsubsection{Encounter at City Loop}
		The Directors of CPI interrogate Susan and Lucca for Lambda’s behaviour. 
		They narrowly escape suspicion. 
		CPI, on behalf of the Aztorian State, tasks Susan to come up with a solution to the plague. 
		
		Lucca and Aloh share a quiet moment, discussing recent happenings. 
		We learn that Aztoria is the only city on earth, in the year 2591. 
		The government uses a powerful branch of mathematics - Societal Evolution Dynamics - to estimate the future, and influences of current decisions manifesting in the future, and that has been the way of decision making for the last 400 years.
		
		Susan discovers that the Newons are destroyed by a magnetic field. 
		She produces a blueprint for a magnetic beam pistol and sends Lucca to mass produce it at the Factory Array. 
		
		Susan remarks with unease, why the Government hadn’t come up with a solution way earlier, since it was so easy. 
		The thought gives Lucca intense dread and suspicion for the Aztorian Government, and the CPI under it.
		
		First instance of reader seeing a ring magnet, with metal cylinders surrounding it, acting as a weapon to destroy Newons.
		
		\subsubsection{What Happened in Year 72}
		Lucca and Susan have a primary school reunion with the class of 72. Lucca gives a demonstration for how to use a magnetic beam pistol, and best practices during the time of plague.
		
		Mr Williams, a beloved teacher, is absent at the reunion.
		
		The classmates reminisce about Mr Williams, suddenly leaving the class before graduation. They fall silent as Lucca walks into the conversation.
		The classmates task Lucca with getting in touch with him, due to Lucca's position as state agent.
		
		Mr Williams, upon being found, cries murderer at the sound of "class of 72" and shuts Lucca outside the door. 
		Lucca doesn't know what happened in the year 72, because he only joined the class later, accompanying them through highschool.		
		
		Speaking to his classmates, Lucca hears about the disappearance (suspected murder) of Mr Smith - another teacher of class of 72, in the year 72. It had been a cold case for 20 years, ruled out by CPI as an impossible case - the body was also never found.
		
		Lucca suggests that the reason Mr Williams fears the students, is because a killer is among them. This makes the students horrified - a killer in year 72 at the age of 12. The students of the Class of 72 are inhumanly intelligent.
		
		After speaking to Aloh, who suggests that there are actually places that literally will not be searched for another few centuries, Lucca thinks of the cryo chambers of rich people that decided to hibernate themselves centuries ago. Due to contract, the facilities are never touched upon, and society has abandoned the practice anyway. The labs are utterly overgrown, at a very, very remote part of the city.
		
		Indeed, one of the chambers were broken in. Lucca finds the body of Mr Smith, perfectly preserved - a case is finally established, after 20 years. The trauma is to the upper right side of the head, meaning the killer was most likely taller than any child in the class of 72. 
		
		In the end, Lucca speaks to Mr Williams about his solution. 
		He suggests to Mr Williams that Mr Williams was the killer. In reality, Mr Williams acted after witnessing Mr Smith's attempt to kidnap one of the students, and moved away to another corner of the city.
		What Mr Williams did not know, was that the inhumanly smart students later found out as well, on their own, and worked together to mess with the technical details of the case, testified in favour of Mr Williams, turning the case into an impossible puzzle. 
		
		Lucca reveals this to Mr Williams, and decides his sentence will be to meet his students again. Mr Williams breaks down, and finally agrees. 
		
		\subsubsection{The Ground Turns Orange}
		One day walking on the streets, Lucca notes the ground has been accumulating orange dust between the pavements, and the air smells nice. 
		
		Actually, a great fire is approaching from the west, and a west wind is blowing the ash and sand over the city, causing the previous observations. 
		
		Due to the sheer scope of the fire, there is no easy way to put it out. 
		The CPI devises a plan to burn a narrow strip of trees along a “choke point” of the forest mass, sacrificing all the trees to the west of that “combustible corridor”. 
		
		Alma and Lucca play a game of go (Chinese board game with black and white pieces). Alma - enthusiastic, in a strange way - questions Lucca's knowledge on the 3 pillars of Aztoria: the University, the Government, and the CPI.
		
		She ominously concludes that out of the 3, all practical power had always been in the hands of the CPI, who originally developed the equations of Societal Evolution Dynamics.
		As they speak, the CPI marches into the government building and disbands it. 
		
		Susan, working as head of neuroscience, and studying the Newon Plague, discovers a powerful secret and is immediately apprehended by the CPI Directors. Her immediate fate is unclear.
		
		\subsubsection{The Synthesis Project}
		Newon outbreak at the Aztoria University neuroscience labs.
		The CPI immediately deploys magnetic field quarantine. 
		
		Lucca rushes through the panic to the heart of the labs, finding Susan sitting on the ground among a pile of patients.
		Susan tells Lucca that she has discovered the secrets of Aztoria, and will be put to death as a result, working in her position. 
		She connects a few wires and we see Newons emerging from those patients' head, combining into one grotesque, writhing structure. 
		This is the Synthesis Project. 
		
		Lucca is astounded, and demands explanation. Susan reluctantly tells him that the synthesis project needs an attractor
	\newpage



	\subsection{Act 2 - Precession}
		\subsubsection{Precession}
		What is precession? 
		Emma joins Aloh's dining space.
		Lucca uses a go-board to act as a binary language, and obtains information out of Professor Lambda without the threat of a lie detector test.
		The message reveals the nature of Precession.
		\subsubsection{For the Happiness of All Humankind}
		Emma and Lucca try to deduce where Aloh goes during the day.
		It turns out he plays trumpet for his dead comrades on a flower field full of buried corpses.
		\subsubsection{The Human Archives}
		Emma and Lucca study historical records at the Archive of the Institute.
		\subsubsection{The Things Troubling Emma}
		In front of Tom and Kaito, Emma voices her concerns of a forgotten past.
		\subsubsection{Relic From Early Centuries}
		Secrets of Director Alma revealed at the lighthouse.
		A true treasure - an early textbook on Synthesis Mechanics.
		\subsubsection{Once More Beneath the City Lights}
		Tragedy befalls Kaito's class.
		Emma and Lucca wander the city, take the Aztorian Train, and come to a shelter, in which the two realise they are on the cusp of a revolution.
		\subsubsection{Interpretations of a Dream}
		Lucca meets an old woman with dementia at a nursing home, who needs help understanding strange dreams she has. 
		The woman is actually Lucca's mum.
		Second confrontation with the strange doctor Nerezza.
		\subsubsection{Mystery in the Aztorian Sky}
		Lucca investigates an amateur astronomer's observation that a star has disappeared.
		Third confrontation with strange doctor Nerezza.
		A huge object is approaching from the northern hemisphere.
		\subsubsection{The District is Westward}
		In journeying west, Lucca finds district 47 empty, and meets the first great attractor.
		\subsubsection{The Spaceport Revolution}
		Incident at Ocean Spaceport sparks a revolution.
	\newpage




	\subsection{Act 3 - Evolution}
		\subsubsection{Once More the Synthesis Project}
		Institute's plan comes true - Lucca's mother is Nerezza, and she will act as the great attractor for the synthesis event.
		\subsubsection{Birth of the Superstructure}
		The superstructure is born, Lucca examines his life within the collective psyche of all humans. 
		Nerezza appears in front of each character and give them resolution, after which they dissolve into newons.
		\subsubsection{New Human}
		A chance of evolution is real. 
		Lucca finds himself awake, insomniac, along with regular visitors of Aloh's dining space.
		\subsubsection{Aztoria}
		They figure out how to use the weapon planted by the old Century Order to destroy the superstructure.
		The newons rain down towards earth, returning to human bodies.
		\subsubsection{The Warm Currents of Time}
		Nerezza and Lucca share one final moment.
		\subsubsection{Stars on the Ground are City Lights}
		Lucca walks among the rubbles of the city.
\newpage







\end{document}