\documentclass[11pt]{article}

% to set margins as i inch
\usepackage{fullpage}

% set paragraph spacing
\setlength{\parskip}{10pt}

% to include links in the table of contents
\usepackage{xcolor}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=cyan,  %choose some color if you want links to stand out
}




\begin{document}

% titlepage
\begin{titlepage}
\title{Design Document for The Aztoria Syndrome}
\author{Alex.X.L}
\date{\today} % automatically changes every compilation
\maketitle
\thispagestyle{empty} % removes page number from this title page
\end{titlepage}


% table of contents, auto generated. Have to click build twice.
\tableofcontents
\newpage % same function as MS Word page break






\section{Preface}
Einstein said (or someone else, i'm too lazy to check), that many people die with music still left inside them.

The Aztoria Syndrome is my music. 
I don't intend to die before playing this music to the world and people around me. 
It is the culmination of 7 years of ideation, excessive doodling, star gazing, and mellow rumination over many hours of the days, waking and asleep.

I was a different person when I first began this process, and the themes for the story have changed countless times - perhaps too sentimental at the start, and now more practical and tangible.
The one constant is that the story is dedicated to humans, whom I love. 
And also my mum. 
Only recently (past 2 years) have the themes settled into a stable configuration, and I doubt it will change too drastically from now till the end of the project.

I will now tell this story.
\newpage




\section{Skeleton}
	\subsection{Theme Statement}
	History is a process of evolution, not precession.
	We ought to seek human progress.
	\subsection{One-Sentence Summary}
	A practical and curious member of the Aztorian bureaucracy decides to solve the mystery of disappearing citizens and appearance of alien-looking organisms at night; he finds himself among one of history's greatest conspiracies, and a city on the cusp of a grand revolution.
	\subsection{Synopsis}
	Set in Aztoria - last city on earth. 
	It is a city of post-scarcity, and all major needs are taken care of by the Factory Array.
	Jobs still exist and are assigned by the government, for people to pass their times.
	The Civil Protection Institute, along with the government, use mathematics to predict the future trajectory of human society, ensuring peace.
	The subject is named Societal Evolution Dynamics.
	
	Lucca, member of the Institute, investigates cases of varying nature - theft, murder, even whacky monster sightings.
	Aloh, who runs a coffee shop, assists him in many ways.
	Underneath the mundane lives, Lucca notices signs of sinister. 
	He sees alien-looking organisms at night. 
	He sees posters of missing people. 
	A great fire happens, and due to poor management by the government, the Institute takes over and disbands the government. 
	Emma, a computer for the government, has no job as a result.
	She joins Aloh's cafe.
	Lucca's director helps him find out that the Institute has been releasing a plague into the population, and collecting the corpses. 
	The plague's symptoms are extreme sleepiness, fatigue, and depression.
	Patients die after weeks of fatigue in their sleep.
	Plague is spread by black organisms that emerge from patient's heads during sleep.
	The Institute's intent is to keep human population low. 
	They developed the plague with help of professor Lambda, who is an expert in neuroscience, and understands the nature of consciousness to be information currents in spacetime.
	They have also been working on a process that can combine humans into a single superorganism, a being that experiences no internal time and is thus stable forever.
	Lucca also learns that the Institute does all this in fear of something called ``Precession'', that will bring cataclysm if not taken action.
	He obtains insomnia.
	
	Professor Lambda announces the plague to the city out of guilt and is imprisoned.	
	Lucca carefully investigatees the history of the city and the human race, alongside normal tasks assigned by the Institute. 
	Meanwhile, normal people lament the lack of change Aztoria has seen in the past few generations.
	It was as if the city is in stasis.
	Emma has memories of being married to Lucca, something that no one else remembers. 
	She also feels mysteriously happy when it is raining.
	Lucca finds a memoir by an old order of scholars who created the city after a world wide war that wiped out 80\% of humanity. 
	He has an epiphany that the precession the Institute fears, is the precession of ages. 
	From a golden age to a dark age, the precession of history thrusts humans into suffering time and time again.
	For this, the bureaucracy maintains population at a threshold, stalls all technological research, and only allows psychological research, for better refinement of the equations of SED.
	But they have made a mistake in their calculations. 
	The true meta-thesis of history is evolution, not precession. 
	The future of mankind lies in the stars.
	The bureaucracy must be overcome.
	A movement of revolution has been brewing in the dark this whole time.
	Scientists whose dreams were cut, workers whose desire for a better life were subdued, and even previous members of the bureaucracy - the computers at the government that was discarded by the bureaucracy, were all in on this movement, waiting to act.
	Lucca gives a lecture to the city, announcing the Institute's plans and bluntly calls for an end to the bureaucracy, which is the catalyst for the revolution to erupt. 
	The Institute is overrun and reorganised, in preparation for a new form of organisation, one without the coersion of a disconnected bureaucracy, but of true representatives of humankind, with the Aztoria University at the center of power, if one is even needed in the first place.
	
	However, by the time people rush into the Institute, it is just a bit too late, and the Institute's plan has already started, and the entire city is absorbed into the superorganism, except a waking Lucca, and regular visitors of Aloh's cafe, because they have been fed insomniac medication by Aloh.
	Lucca uses a mechanism planted by the old order who created this city, to destroy the super organism.
	The consciousness of people disperse into individual raindrops, and falls down on the city, returning to their standard form.
	Emma realises that her memories are not from the past but from the future.
	Humans are on the cusp of evolution after all - they will become proto-telepathic.
	Lucca walks among the rubbles of the city and feels intense joy for a forever changed humankind with an uncertain future.
	\subsection{Apparent Story Questions}
	What is wrong with the city? $\rightarrow$ 
	What is Precession? $\rightarrow$  
	What is the history of the city, and humankind? $\rightarrow$ 
	Will, and how, will humans triumph?
\newpage






\section{Styles}
	\subsection{Artstyle}
	Character designs will resemble Tintin. Simple, but hopefully effective.
	Environmental shots will showcase a modern but non-generic city scape.
	\subsection{Storytelling}
	Episodic structure, each episode tells one mystery. 
	More classic, more subdued style.
\newpage





\section{Setting}
	\subsection{Earth}
	Northern hemisphere is empty - wiped out by an old war.
	Colossal megastructures still remain as ruins.
	Abandoned spaceports and intercontinental railway networks.
	Only remaining continent with humans is Oceania.
	\subsection{Aztoria}
	Megacity situated on the eastern quarter of the Oceania continent. It is the final city on earth.
		\subsubsection{Material Conditions}
		Post scarcity. Production of all goods are automated. 
		The city has some ancient structures with unknown purpose.
		There is an advanced train line called the Aztorian Train Line, with a CIty Loop near the center, where Aztoria began. 
		\subsubsection{Social Structure}
		The Aztorian government, the Aztorian University, and the Civil Protection Institute, make up the 3 pillars of Aztoria - the Aztorian bureaucracy.
		
		The Government consists of nothing but a group of human computers, who perform computations with the equations of SED that the Institute provides.
		
		The University conducts research permitted by the Aztorian Government.
		
		The Institute acts as the ``arms" of the city - its police, ambulance, and fire brigade combined.
		It also has a central board of directors who actively research SED separate from the University.
		Among them, the First Director is the highest authority.
		
		People can still pick jobs, but their lives no longer depend on it.
		They do it to pass their time. 
		Aloh, for example, asked to take care of a communal space that primarily serves drinks and desserts.
		Scientists are one main area of work, now that mundane services are all automated.
		Above them, a job in the bureaucracy has the highest form of prestige, since they are viewed as guardians of civilisation itself.
		
		Education is valued highly just by mandate of the Institute. 
		To promote sense of social belonging, a class of students stay together until University.

\newpage





\section{Mechanics}
	
	\subsection{Consciousness}
	Information flow across spacetime.
	Flow across space, over time, allows information to pass from one part of the bran to another, and formation of memory.
	It is poetically called the ``currents of spacetime" by Professor Lambda, and sometimes refered to as ``currents of time", or simply ``currents".
	This is facilitated by an electric structure that is the brain.
	It is subject to influence by magnetic fields.
		\subsubsection{Currents}
		Near the end of the story, Emma realises that her memories are carried by warm currents of time, from the future. 
		The newon awakening has caused humans to evolve to become proto-telepathic, using nothing more but the currents of time.
	
	\subsection{Plague}
		\subsubsection{Symptoms}
		Extreme sleepiness, fatigue, dread, depression.
		Bizarre reactions to surroundings.
		Bizarre movements and speech, almost alien.
		Altered state of consciousness.
		\subsubsection{True Mechanics of the Plague}
		It is a gradual separation of the consciousness with the body. 
		In the end stage, the consciousness - collection of currents of spacetime - forms a stable structure separate from the brain.
		This structure can take arbitrary shape, but most attempt to stay in shape of a human, but comically fails, and appear grotesque and alien.
		The structure is the black organism that seeps out of the patients head during their sleep - their mind has literally left their body. It will be refered to as a ``newon".
		It is so stable that no information can leave the boundaries of the structure - that's why it appears black.
		Death occurs only because the structure has no way to recombine with the body, and the body is left to rot while the consciousness wanders till the end of time, deforming further.
		
		Upon destruction, the currents of time disperse into the universe.
		\subsubsection{Transmission}
		During sleep, black organisms seep out of the patient's head and wander about, infecting anyone they come into contact with.
		This is because the organisms have affinity to one another, and draw each other out (probably due to the electromagnetic origins of consciousness).
		\subsubsection{Destruction of Transmission}
		A powerful and concentrated magnetic field differential will disrupt the organisms.
		If by the time of destruction, the physical body was still alive, the currents will return to the body.
		Otherwise, they disperse into the surrounding.
		\subsubsection{Immunity}
		If an individual is unable to sleep, they are unable to let their consciousness escape their body, thus immune to death by this plague.
		\subsubsection{Treatment}
		Terminal illness. 
		Death is inevitable.
		Though, preventative measures can be taken such that if someone is hyper alert and insomniac, the initial transmission/contact does no effect to pull the person's consciousness out.
		
	\subsection{The Grand Synthesis}
	Plan of the Institute to integrate all of humankind's consciousness into a single superstructure.
		\subsubsection{Chain Reaction}
		In general it is possible to merge consciousness in the nonstandard form - the newon form. 
		One on one, it requires physical contact, but if there is a large enough concentration, people in the surrounding can spontaneously lose their consciousness to it.
		\subsubsection{Great Attractor}
		To create a species wide chain reaction, they need a cite of nucleation - a great attractor - a newon that is so perfect that it retains the person's likeliness perfectly. It is now capable of transmitting info in and out of its boundary, gaining colour once more.
		
		The people who volunteer to become an attractor, have to abandon their bodies and live as an attractor. Unless the Institute intends to begin the Synthesis of mankind right away, these attractors must be put in perfect solitude. 
		
		The only two attractors created in history escaped, and the Institute put the project on hold. 
		The first one escaped to district 0, and accidentally caused a small scale synthesis event, merging all residents of that district. 
		From then on, she \textit{was} the district.
		The second one was Nerezza, Lucca's mother. She did not straight up disappear, but promised the Institute to fulfill their plans in the future, so that they will not create any more attractors. 
		Nerezza wanders the city in the outer regions, never stopping long in a single place in fear of the newons attracting towards her and starting the synthesis event. 
		Her real body is severly mentally impaired. 
		Lucca grows tired of caring for her and sends her to a nursing home, which he intensely regrets.
		\subsubsection{Superstructure}
		The object that is the amalgamation of all human consciousness. Upon destruction, Nerezza's existence is scattered across spacetime. That's why brief images of her can be seen at all points in the story, in weird places.
	
	\subsection{Electromagnetism}
	Given a loop of wire, no matter the scale, if an electric current runs through the wires, a magnetic field will be generated in a donut-like shape engulfing the loop. 
	The shape of the magnetic field at the center of the loop is a straight line shooting in both direction to the infinite, along the axis perpendicular to the plane of the loop.
	
	\subsection{Weapon of the Order - Aztoria}
	``When in trouble, get on the A Train", sing the older people. 
	It was a clue passed down the generations by the scholars who created this city. 
	
	The City Loop is actually a colossal loop of wires hidden in the concrete. 
	Upon activating a hidden power source, the loop generates enough magnetic field to destroy a superstructure the size of the entire human race. 
	If this is done when the bodies have yet to decay, the currents will return to the bodies. The sight looks like a massive rain from the sky.
	
	Instructions to use the weapon are inscribed as horizontal striped markings of uneven lengths, on the side shields of the train line. 
	The messages hidden in these markings will only be apparent when the train starts moving - the stripes appear like flashes through the window, long and short. 
	It is Morse Code.
	
	The weapon is simply named ``Aztoria".
	
	\subsection{Societal Evolution Dynamics}
	Mathematical, formalised system describing theorems of evolution of human societies. 
	Originally created in the warring era when scholars across the earth were tasked by the Earth Federation with finding a way to predict and prevent wars.
	
	Includes characteristics of fluid dynamics, thermodynamics, linear algebra.
	Main high level process is constructing a Jacobian detailing the partial derivatives of a set of inputs and outputs for a certain human system. 
	Solving the tensor equation gives the required changes in configuration space in order to achieve desired outcomes in the real world space.
	
	\subsubsection{Precession}
	One meta-theorem of history birthed from following theorems: 
	
	\begin{enumerate}
		\item Humans alter their surrounding conditions.
		\item Surrounding conditions alter humans.
		\item A capable society alters their surroudings favourably.
		\item A favourable surrounding produces a complacent society.
		\item A complacent society alters their surroundings negatively.
		\item A negative surrounding produces humans capable of withstanding it.
	\end{enumerate}
	
	On the largest time scales, this forms an inconceivable cycle, and results in a periodic timeline of golden and dark ages. 
	History repeats.
	
	\subsubsection{Evolution}
	The real meta-theorem of history.
	
	History is a process of evolution, birthed from the continual resolution of contradictions. 
	Each set of contradictions defines an epoch.
	The transition between epochs are where history happens.
	A new standard is established, and human society reaches ever higher heights. History does not repeat.
	
	The main contradiction of the epoch before the birth of Aztoria was an economic one, the resolution of which was a world-wide war.
	Out of this end to the epoch birthed 3 things:
	
	\begin{enumerate}
		\item Unification of humankind, where they found refuge in Oceania. The end of Imperialism and Nationalism.
		\item The automated Factory Array - the disappearance of scarcity and currency.
		\item The study of Societal Evolution Dynamics.
	\end{enumerate}
	
	Other than that, it has left Aztorians the primary contradiction of today: the stability offered by a bureaucracy versus the desire for progress by the people.
	
	Eventually, the bureaucracy loses its standing. 
	What used to be a guardian of the new civilisation has long ceased to being a progressive force. 
	It will eventually lose to the people and disappear from history. 
	Thanks to the SED they developed, the people now have what they need to lead a future of never ending progress.
	The dreams of humankind are crying out.
	
	However, should the bureeaucracy continue to resist, the people will fall, and the bureaucracy along with them. 
	A common ruin to the contending parties.
	Older forms of society will return. 
	Life will return to prehistoric violence, and all will be lost.
\newpage






\section{Characters}
	\subsection{Lucca}
	Early 30s. Wears shirt, windcoat, glasses.
	New member of the Institute that Director Alma takes a liking towards.
	Used to be mechanical engineer at the Factory Arra, promoted to a member of the bureaucracy for sincere performance.
	Practical, logical, a bit cruel in humour. 
	Underneath the cold practicality is a warm sincerity.
	Carries unease and terror for abandoning his mum.
	\subsection{Aloh}
	Late 80s, but healthy due to the abundance and great living conditions of Aztoria.
	Wears jumper over shirt, glasses.
	Runs a communal space that serves drinks and desserts, with a band performing in the background. 
	Used to perform at the army band, prior to the collapse.
	Secretly visits the flower grown battlefield where his fallen comrades lie, and play the trumpet for them.
	Secretly part of the revolutionary movement, and a member of the old order of scholars.
	Feeds his visitors insomniac medication in preparation for the coming synthesis plan of the Institute.
	\subsection{Director ALma}
	Late 60s. 
	Fluffy hair like Einstein. 
	Always seen wearing uniform of the CPI.
	Highly respected director of the Institute.
	Mischievous at times, serious at times. 
	Guides Lucca towards the truths of this city.
	Likes listening to ``Get on the A Train".
	Secretly member of the revolution.
	\subsection{Professor Lambda}
	Late 90s.
	Head of neuroscience of Aztoria University.
	Contributed to technologies such as a loophole-free lie detector, mind reader, and chief engineer of the Plague.
	Stubborn and sharp.
	\subsection{Kaito}
	One of Lucca's highschool classmates.
	Early 30s.
	Wears shirt.
	Teacher, just like his own teacher whom he admired.
	Secretly the next ``First Director" selected by the Institute, and acts as such.
	Intense love for education and the next generation.
	Hatred towards the possible darkness of human nature.
	\subsection{Nerezza}
	Doctor who wanders the outer rims of the city.
	Wears black trenchcoat, carries a suitcase.
	Appears to be in her early 30s.
	Mischievous, cryptic, cruel, sophisticated, well-read on history.
	Secretly an attractor, and Lucca's mum. 
	Laughs when she sees suffering.
	Seems to always know what events will happen.
	
	At the end of the story, as the superstructure is annihilated, her existence is scattered across spacetime. 
	This causes still-images of her to appear at various points in the story. 
	\subsection{Emma}
	Lucca's highschool classmate, early 30s.
	Wears casual clothes, loose and comfortable. 
	Computer at the Government, later turned singer at Aloh's shop.
	Playful and sharp - one of the top performing students all through her education.
	Childlike.
	Enjoys seeing rain for unknown reasons - the image brings her joy. 
	Believes the Institute has taken away her memory of a normal life, a mundane and peaceful life with Lucca.
	
	At the end of the story, we realise that her memories are from the future.
	\subsection{Tom}
	Lucca's highschool classmate, early 30s.
	Wears plain suit typical of a physicist.
	Astrophysicist at the Aztorian University. 
	
\newpage






\section{Acts}
	\subsection{Act 1 - Wanderings}
		\subsubsection{Beneath the City Lights}
		In Aloh's cafe, Lucca partakes in a psychological operation to lure out a murder confession.
		Lucca, Aloh, Alma, Institute introduced.
		Alien looking organisms introduced. 
		\subsubsection{Monster in District 14}
		Monster is sighted in District 14 at night, in front of a tree.
		The monster turn out to be an old man who is sleepwalking, due to anxiety about the district expansion projects that threaten to destroy those trees that represent memories with his late wife.
		Lucca tries to help migrate the projects but is met with the stubborn face of the Aztorian Government.
		\subsubsection{New Plague}
		Lucca helps Professor Lambda retire, witnessing his labs.
		At the end of the day, Lambda announces a terrible plague to the city out of guilt. 
		He is imprisoned afterwards.
		\subsubsection{Encounter}
		Lucca attends highschool reunion, but one of their belvoed teachers was missing.
		Years ago he left just before their graduation as well, for unknown reasons.
		Lucca is tasked to find him, contact him, and ask him to hand them graduation certificates personally.
		He finds the teacher but is met with a strange doctor named Nerezza who proclaims to help patients undergo euthanasia, and the teacher is her client.
		\subsubsection{The Ground Turns Orange}
		The ground turns orange, the air smells nice.
		When Lucca was small, he asked mum ``why does it smell nice in winter?"
		To which she answered ``because people are burning firewood."
		Orange dust is being blown by a west wind.
		A great fire is approaching Aztoria from the west. 
		The Institute efficiently carries out a plan to burn a strip of trees across the narrow channel of trees that connects the major Aztorian forests with the western forests.
		Afterwards, the Institute disbands the government, putting Emma out of job.
		\subsubsection{Wandering's End}
		Chaos erupts in the Aztorian University neuroscience labs. 
		The first synthesis event happens, and ends, with the revelation that the Institute's plans are to avoid ``precession".




	\subsection{Act 2 - Precession}
		\subsubsection{Precession}
		What is precession? 
		Emma joins Aloh's cafe.
		Lucca uses a go board to act as a binary language, and obtains information out of Professor Lambda without the threat of a lie detector test - he will answer he does not know any information because he really doesn't; he will once he gets home and decodes the messages.
		The message reveals ``precession, not in space, but in time."
		\subsubsection{Home Invasion Investigation}
		An interrogation of a girl who is the sole survivor of a home invasion reveals a sinister truth.
		\subsubsection{For the Happiness of All Humankind}
		Emma and Lucca try to deduce where Aloh goes during the day.
		He plays trumpet for his dead comrades on a flower field full of buried corpses.
		\subsubsection{The Human Archives}
		Emma and Lucca study historical records at the Archive of the Institute.
		\subsubsection{The Things Troubling Emma}
		Emma voices her concerns of a forgotten past.
		\subsubsection{Interpretations of a Dream}
		Lucca meets an old woman with dementia at a nursing home, who needs help understanding strange dreams she has. 
		\subsubsection{Relic From Early Century}
		Secrets of Director Alma revealed at the lighthouse.
		A true treasure - the records of the early century.
		\subsubsection{Ancient Plague}
		Tragedy befalls Kaito's class.
		Emma and Lucca wander the city, and come to a shelter, in which the two finally figure out what precession means.
		\subsubsection{Mystery in the Aztorian Sky}
		Lucca investigates an amateur astronomer's observation that a star has disappeared.
		A huge object is approaching from the northern hemisphere.
		\subsubsection{The Town is Westward}
		In journeying west, Lucca finds district 0 empty, and meets the first great attractor.
		\subsubsection{The Aztoria Syndrome, Solved!}
		Lucca tells all secrets to the city, and revolutionary movements brew and erupt.





	\subsection{Act 3 - Evolution}
		\subsubsection{World's End}
		Institute's plan come true - Lucca's mother is Nerezza, and she will act as the great attractor for the synthesis event.
		Nerezza told the Institute a while ago, that she will ``start the synthesis at the centre of Aztoria, coinciding with the eternal center of humankind."
		\subsubsection{Distant Memory}
		Flash back arc of world war 3 and the order of scholars.
		\subsubsection{Birth of the Superstructure}
		The superstructure is born, Lucca examines his life within the collective psyche of all humans. 
		Despair.
		\subsubsection{New Human}
		A chance of evolution is real. 
		Lucca finds himself awake, insomniac, along with regular visitors of Aloh's cafe.
		\subsubsection{Aztoria}
		Lucca sees images of Nerezza again, and suddenly understands something.
		They figure out how to use the weapon planted by the old order to destroy the superstructure.
		\subsubsection{Currents of Time}
		In the superstructure, Emma speaks with Nerezza in front of a painting.
		Emma realises her memories are from the future.
		Nerezza congratulates her that she will get along with Lucca.
		Outside, Nerezza also speaks to Lucca.
		Nerezza forgives Lucca as his mother. 
		They share one final moment together, talking about the future of civilisation.
		Lucca said he knew he could succeed when he saw her image, because when the superstructure was destroyed, the great currents sent the scattered pieces of her existence across spacetime.
		Nerezza leaves, Lucca falls asleep.
		\subsubsection{Beyond the Infinite}
		Lucca walks among the rubbles of the city. He comes to Emma lying on the ground, eyes stared wide open. 
		Humans are forever changed.
		Their eyes meet.
		After a long and tense moment, Emma smiles, suggesting she still knew who Lucca was. 
		The end.






\end{document}