\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Beneath the City Lights, A Secret}
\maketitle
It is a strange looking coastline of a city. 
There is no beach, only a short artificial cliff above which sits the Coastal Walk.
Colossal, rectangular structures stand tall in an organized line along this road.
They have no windows nor doors, only cracks in the concrete that betray their centuries-old age. 
The sun is setting into the city beyond these structures, casting long shadows onto Coastal Walk that reach into the ocean.

A person walks from the inner city onto Coastal Walk through a gap between two such structures.
The true scale of the structures is now apparent. 
The person is at most one fiftieth of the height, and one tenth of the width of a concrete block.
He faces the ocean and raises his line of sight towards the hints of stars above. 
He has a classic side-part hairstyle and wears a beige trenchcoat. 
His large glasses hide his eyes behind their reflection. 

He takes out a rolled up paper slip after glancing around. 
He opens it. 

NOTE: 
Dear Lucca, I discovered a secret about the universe. 
Meet me tomorrow 5pm on Coastal Walk, New Melbourne. 
Keep an eye out for strange looking animals on your way. 
Don't text me about any of this. 
Marco

Lucca looks down the empty Coastal Walk. 
The shadow from the buildings intersplice with the light that pierce through them from the inner city. 

LUCCA, checks his watch, thinking: 
Did I get the date wrong? No... Last night's "tomorrow" is definitely today. 
Did Marco mean 5pm in his time zone? 
If I remember correctly, he works at the 13th cluster of the Factory Array, which is only one hour earlier than here in the capital. 
Did he get caught up in something? 
Then he absolutely would've notified me. 
Is he maybe... in danger?

A flock of birds with devolved eyes fly from the ocean. 

LUCCA, reaching down towards one that lands near him, thinking: 
Northern bird. Their eyes are now useless thanks to mutation. 
They now fly across the earth, following magnetic field lines. 
While some could consider them to look strange, they are so common in Oceania, Marco is likely not refering to them.

Lucca turns around and looks at the inner city through the gaps of the structures. 
The city lights are so blinding that it's hard to make out the shape of the skyline.

LUCCA: "Alright, you win. You've hooked me now. Just what kind of secret-"

The sight of a woman standing in the distance stops Lucca's murmur. 
The woman is facing in the direction of Lucca.
Her black trenchcoat flaps wildly in the ocean winds. 
On second look, maybe not?
Her trenchcoat is flapping in such a fashion that it looks like wind is blowing from beneath.
Lucca's eyes stare in her direction. 
The woman doesn't move. Is she even looking at him?
A sweat drop appears on his forehead. 
He turns his back to her and prepares to walk in the opposite direction. 
When he glances back, the woman is not there. 
He leans on the protective glass panes on the ocean side of Coastal Walk. 

LUCCA, thinking: 
What am I doing? 
Getting excited about Marco's note and coming all the way out here...
And now outright hallucinating a person...

Lucca's watch rings. 

LUCCA, thinking: crap, it's Director Alma. 

Lucca flips open his watch to answer.

LUCCA: "Director?"

ALMA: "Lucca! Where the hell are you? Did you escape from work?"

LUCCA, playfully: "Uh well technically, considering the name of our department, I'm still doing my job."

ALMA: "What the hell's that supposed to mean?"

LUCCA, hurriedly: "I'm, uh, I'm sorry. I can make up-"

ALMA: "I was looking for you."

LUCCA, after a sigh: "Yes, Director... What for?"

ALMA: "Your friend, Marco Korolev..."

LUCCA: "Marco? What about Marco?"

ALMA: "He, uh... the portion of the Factory Array he was working at, collapsed. It crushed him."

Pause. 

LUCCA: "You're serious."

ALMA: "I'm sorry."

LUCCA, looking down towards his left feet: "Huh..."

ALMA: "The Triple S dispatched a disaster response team. They arrived on scene 2 hours ago. 
It appears no other worker was injured."

LUCCA, restless: "...That's a relief."

----

Inside a train carriage, Lucca sits among civilians with varied clothing. 
The one constant among everyone's attire is the artist cap, fashionable among the civilian class in contemporary Oceania.
Lucca's right heel strikes the floor erratically, attracting a few glances. 
He remembers some notable memories with Marco: 
1. Lucca walks through a uni campus carrying a bag, and spots Marco reading a textbook on the lawn.
Marco has short curly hair, sharp features and a fiery glare. 
2. Marco proudly puts on his artist cap as Lucca and their teammates all look at his engineering drawings before the competition. 
3. Marco and a woman with big eyes dancing at the science ball, while Lucca watches.
4. Marco and the woman at their wedding, with Lucca by his side. 

----

The Factory Array is huge, so huge its edges recede into the distant horizon, and this is just one cluster of the whole across the Ocean Union. 
In one cluster, colossal factory cells arrange themselves in a matrix, each with high reaching chimneys spewing out steam. 
Pipes encircle the cells, sometimes disappearing into or emerging from them, now here, now there, like a thousand snakes. 
Among the cells, fatter, even higher chimneys stand. 
At some far-away centre of this matrix of cells, a single tower stands the tallest among all.
A circular disk sits at its very top, with glass panes on its circumference. 
Millions of tubes shoot out from the root of this disk, in a diagonally downward direction, reaching into who knows where. 
In front of all this is a building, small in comparison, with a sign at its top, reading "CONTROL ROOM 550".
Half of its walls are missing, and in their place is rubble. 
One of the factory cells in the background is broken too, and its remains lie in that same rubble. 
Yellow tapes with "RESTRICTED" written on them stretch about the building like a spider web.
People wearing artist caps stand outside, curiosly peeking. 
There are trucks with "State Security Service" written on them. 

Lucca walks up to one of the workers. 

LUCCA: "What happened here?"

WORKER: "No idea mate. I was on standard duty in control room 549. Loud ass screeches came outta nowhere. We came out to look and BANG! 
The factory cell fell, the control room 550 all gone. Poor guy. He's a good one, that Marco."

LUCCA: "And no one else, except for Marco, was caught in the collapse?"

WORKER: "I'm just a worker mate, you gotta ask the fellas over there. Or the FA itself."

Lucca bows lightly with a casual salute to the worker and walks on. 
He ducks under the restriction tape and walks towards the rubble. 
Firemen are placing hooks onto big slabs in the rubble in an attempt to lift them. 
A man in the Ocean Union uniform walks up to Lucca. 
The man's uniform is mostly white, with a golden upside down crescent earth at his chest, above which the uniform is black. 
He wears a collar insignia that looks like a flame. 
He is clearly an SSS official. 

OFFICIAL: "Halt. Who are you?"

LUCCA, raising his watch, evidently an identification of some sort: "Lucca Yang, Department of Anomalous Phenomena."

OFFICIAL: "No uniform? You must be new."

LUCCA: "The Factory Array has been overloaded for a while. My uniform can wait."

OFFICIAL: "Welp, this is a standard workplace disaster, and we don't need you here."

LUCCA: "That's for me to decide. A disaster on this scale with only one casualty? 
And when's the last time the Factory Array just collapses? Looks anomalous."

OFFICIAL: "...And what do you have to offer?"

LUCCA: "I used to work here, and I knew Marco. Let me talk to the Factory Array. I'll be able to gather some info."

OFFICIAL: "Alright, go knock yourself out." 

Lucca steps over the mush of machinery. 
Large gears lie on the fractured slabs, hopelessly deformed. 

LUCCA, thinking: Some sort of freak mechanical failure. 

Lucca turns into a half intact corridor, with a terminal at its end. 
He types something in and the screen lights up. 

SCREEN: BOOT UP SEQUENCE COMPLETE.

FA, as text: HELLO.

LUCCA, typing: HELLO FA, IM LUCCA YANG.

----

A woman in a labcoat looks at the clock and leans forward into her desk, propping her forehead up with her right hand.
She has light blonde hair that curls into little balls, looking like a fluffy cloud wrapping around her skull. 
Another woman next to her, presumably her colleague, comes close.

COLLEAGUE: "You okay, Susan?"

SUSAN, opening her huge eyes: "Mmm? Yeah, just tired. Wanna sleep already, you know."

COLLEAGUE: "You should take a nap then!"

SUSAN: "Are you serious? What if Professor Lambda comes around?"

COLLEAGUE: "Then I'll wake you up before that happens. I gotchu!"

The phone rings next to them. The colleague picks it up. 

COLLEAGUE: "Hello! This is Marie from Lab 6, how can I help you?"

PHONE: [unintelligible]

MARIE: "Yeah, she's here. I'll pass the phone."

SUSAN, quietly: "Who is it?"

MARIE: "Department of something something something, I didn't quite catch. Quick, quick!"

SUSAN, holding the phone: "H-hello, this is Susan!"

PHONE: [unintelligible]

Susan's eyes stare even wider than before. 
She puts the phone down and walks away. 

MARIE, looking at the phone: "Hey, what did they say? Are they still on?"

Susan stops after a few steps, and sits on the floor. She starts crying. 

----

FA: ENGINEER YANG, LONG TIME NO SEE. HOW ARE YOU FINDING THE GOVERNMENT WORK? AND HOW'S YOUR MUM DO-

LUCCA: [SLASH]SKIP SMALL[UNDERSCORE]TALK

FA: HELLO ENGINEER YANG, HOW CAN I HELP? 

LUCCA: IM HERE TO INVESTIGATE THE DEATH OF LEAD ENGINEER MARCO KOROLEV

FA: A TRUE TRAGEDY.

LUCCA: IM SPEAKING TO U FROM CONTROL ROOM 550, WHICH HAS JUST COLLAPSED

FA: I AM AWARE.

LUCCA: WHAT CAUSED THE COLLAPSE

FA: AN ERROR IN CONFIGURATION IT SEEMS - THE CELL WAS TO BE RECONFIGURED TODAY FOR PRODUCTION OF A NEW ITEM. 
THE NEW CONFIG MUST HAD CONTAINED AN ERROR - SOME OF THE GEARS WERE TO BE DRIVEN IN THE WRONG DIRECTION. 

Lucca looks at the broken gears in the rubble to his right. 

LUCCA: WHO AUTHORED THE NEW CONFIG?

FA, causing Lucca to recoil slightly: ENGINEER KOROLEV. 

LUCCA: MAY I SEE THE CODE OF THE CONFIG

FA: YES. 

Below the terminal, a few pieces of paper slide out. 
The papers contain strings of abstract mechanical coding language. 

LUCCA, thinking: there it is. 
A single negative sign in front of the Hossenfelder terms of the tensor complex. 
How can Marco have made such a simple mistake writing code? 
Did he not get this cross-checked by a peer-reviewer?

LUCCA, typing: WAS MARCO ALONE IN THE CONTROL ROOM?

FA: THERE WERE 11 OTHER ENGINEERS, WHO ALL LEFT AT 3:00PM. 
THEN, AT 3:30PM, I COULD NO LNOGER SEE CONTROL ROOM 550. 
FROM CONVERSATIONS OF NEARBY WORKERS, I DEDUCED THAT THE PLACE NO LONGER EXISTED. 

Pause.

FA: IS THERE ANYTHING ELSE I CAN HELP WITH?

LUCCA, after thinking: HAVE YOU SEEN ANY ANIMALS OUT OF THE ORDINARY THROUGH YOUR SENSORS AROUND OCEANIA?

FA: NO.

LUCCA: THANK YOU FOR YOUR TIME.

FA: STAY SAFE, ENGINEER YANG.

----

Lucca walks out of the scene. The official from earlier greets him. 

OFFICIAL: "Well?"

LUCCA, pointing to the broken cell looming above them: "From what I gather, Marco was trying to reconfigure this cell of the Factory Array. 
Maybe due to confidence, he didn't check for bugs in his code. The code caused the inner mechanisms of the cell to catch onto itself, and...
the whole thing came apart."

OFFICIAL: "Damn. Some kind of lead engineer. [This prompts Lucca's eyebrows to form a "V" shape.] 
Trying to reconfigure the Array without peer review? Kids ain't right. This Union is going to hell."

LUCCA, pulling out his note from Marco: "However..."

OFFICIAL: "What?"

LUCCA: "No, don't worry about it. 

Lucca stares at the note in his hands. 

OFFICIAL: "Welp, the incident report form shouldn't be too bad then. 
And we gotta come up with a way to make sure this kinda thing never happens again. 
More safety instruction videos, maybe."

Lucca takes one last look at the rubble, and salutes it.

----

Noon. It is an expansive graveyard. 
Lucca walks through the graveyard with flowers in his hands. 
His steps freeze as he spots something in front of him. 
Susan stands in front of a grave. She is wearing a black knee-length dress. 
Her gaze turns to Lucca as he approaches. 

LUCCA: "Mrs Koroleva."

Susan doesn't speak. 
Lucca sees the picture frame that Susan is holding. 
It is an award.
It says: The Government hereby presents Marco Korolev with the title: HERO OF THE OCEAN UNION.

LUCCA: "...Marco was one of the greatest mechanical engineers of Oceania. 
He uh, authored the 122nd amendment to the Factory Array, which improved the-"

SUSAN: "You don't have to say anything. You're part of the Ocean Union State after all. You've said enough."

Lucca falls silent and turns his head to Marco's grave. Susan begins walking away, but she stops after a few steps. 

SUSAN: "Lucca."

Lucca raises his head.

SUSAN: "Don't investigate Marco's death further. Forget about it. Can you do that for me?"

Lucca doesn't speak.

SUSAN: "Well, I'll see you when I see you."

Susan walks off.

----

Days and nights pass over Oceania. Lucca walks through the city streets. 

NARRATION: "Within the machinery of the Ocean Union, one cog sat out of place - the Department of Anomalous Phenomena. 
It was a place where good hearted - and sometimes overly imaginative - citizens of Great Oceania brought their concerns. 
Things not too small to ignore, but too peculiar for the other departments to work with. 
Once a case is solved, the report will be broadcast as a playful retelling, providing entertainment for the civillians. 
For those worn out by the mundane industrial life, the D.A.P. was a welcome existence. 
Its presence may had also signified an inflation of government institutions, 
so successful that their hands reach to serve even human curiosity itself. 
It was a golden age for bureaucracy, and unfortunately, an age of supreme boredom for investigator Yang."

The headquarter of D.A.P. is a dome, which if viewed from above, has concentric rings of windows, one for each level. 
Tall lamps stand on the sides of a road to its grand entrance. 
Lucca sits at his desk, and brings out a metal box. 

NARRATION: "Even though 2 years have passed, he could never quite forget about Marco according to the wishes of Mrs Koroleva."

It is night. Susan sits alone on her bed. 
Meanwhile, in Lucca's apartment, he leaves the metal box on the table and pours himself a drink. 
He opens the box. Inside is Marco's note. 

LUCCA, thinking: This note actually contains some information between the lines, and in its context. 
Marco chose a physical letter rather than texting, and warned me against it. 
This suggests that he was afraid of digital surveillance. 
By extension, his secret is possibly against the interests of those who do the surveilling - government of the Ocean Union. 
But what does the "universe" have to do with the Ocean Union?
And the "strange looking animals"... 

Lucca walks towards the window. The city lights look like stars on the ground. 

LUCCA, thinking: 
Mrs Koroleva... I'm sorry. I have to find out. I can feel something large at play. 
I'll find Marco's secret, and I will solve the true nature of his death. 
I will bring the answers to you. Yes. 
If I manage to solve everything before telling you, you will be happy. 
You'll conclude that the investigation was worth it. 
I will broadcast the secret he discovered to every deserving ear in Oceania.
And I can sleep with ease. 
I hope this won't hurt you. 
I have kept my eyes out, just as Marco asked. I'll keep them out for the rest of my life if I have to!

Shots of Oceania. 
The empty Coastal Walk, with its eerie buildings. 
The looming government building in Central Oceania. 
The City Loop of the train. 
The Factory Array.
The corridors in Lab 6.


\end{document}