\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Beneath the City Lights, She Appeared}
\maketitle

New Melbourne coast, dusk.

Lucca Yang, with neatly combed hair, large pair of glasses, dressed in a beige trench coat, stands beneath a row of tall rectangular buildings, with no windows nor doors. 
The buildings block out part of the city lights, leaving long patches of light and shadow onto an empty Coastal Walk.
He looks about his surroundings and takes out a note.

NOTE: Dear Luc, I discovered a secret about the stars. 
Meet me tomorrow on Coastal Walk, New Melbourne. Come at 5:00pm.
If you can, keep an eye out for strange looking animals on your way. 
Don't text me about any of this. See you then.
Marco

Lucca looks at his watch. It is 6:15pm. 

LUCCA, thinking: Did I get the time wrong? Last night's "tomorrow" is definitely today. 
Is there a time zone problem? Marco works at the 13th cluster of the Factory Array... Only one hour earlier than here in the capital. 
Did Marco get caught up in something? He would've notified me.

A flock of birds with devolved eyes fly from the ocean. Lucca reaches down towards it.

LUCCA, thinking: Northern bird. Their eyes are useless thanks to mutation; they navigate via magnetic fields. While some could consider them to look strange, they are so common in Oceania, Marco is likely not refering to them. 

Lucca turns around and looks at the city.

LUCCA: "Alright, you win. You've hooked me now. Just what kind of secret...?"

Suddenly, Lucca notices a woman in a black trench coat standing in the distance on Coastal Walk. The woman is fixed in place, and doesn't speak. They gaze at each other. Lucca is visibly unnerved. The woman disappears. 

LUCCA, thinking: the tedium and boredom of bureaucracy must be getting to me... Getting excited about Marco's note and coming all the way out here... and now outright hallucinating a person that isn't there. What am i doing...

Lucca's watch rings. 

LUCCA, thinking: crap, it's Director Alma.

He picks it up.

LUCCA: "Director?"

ALMA: "Lucca! Where the hell are you? Did you escape from work?"

LUCCA: "Welllll... \textit{technically}, considering the name of our department, I'm still doing my job."

ALMA: "..."

LUCCA: "Look I'm, I'm sorry. I'll make up-"

ALMA: "I was looking for you."

LUCCA: "..."

ALMA: "Your friend, Marco Korolev..."

LUCCA, surprised: "Marco? What about him?"

ALMA: "He... the portion of the Factory Array he was working at, collapsed. Marco was crushed."

Pause.

LUCCA: "You're serious."

ALMA: "I'm sorry."

LUCCA: "Huh..."

ALMA: "We dispatched a disaster response team. It appears no other worker was injured."

LUCCA: "...That's a relief."

----

Lucca is on the Century Line. He won't stop moving his heels up and down, attracting a few glances. He remembers a few moments with Marco - Lucca walking through a uni campus, carrying a bag, spotting Marco reading a textbook on the lawn; Marco proudly putting on his working hat, while holding an engineering blueprint in his other hand; Marco and a woman dancing while Lucca watches; Marco and the woman getting married while Lucca watches...

----

Back in reality, Lucca arrives at the Factory Array and looks towards the rubble. What he is seeing is a mere cell of the colossal organism that is the Factory Array. A few workers and a fireman come towards Lucca.

WORKER: "Lucca! You came!"

LUCCA: "We can catch up later. I heard about Marco. What happened here?"

WORKER: "No idea. We were just going through our daily maintenance in a neighbouring cell, until we heard loud bangs and screeches. By the time we followed the noise and ran here, this cell has totally collapsed."

LUCCA: "And no one else, except for Marco, was caught in it?"

FIREMAN: "Not that we know of. You're better off asking the Big Boy yourself."

Lucca walks and bows below a restriction tape, towards the disaster scene. A government official greets him.

OFFICIAL: "Halt. Who are you?"

LUCCA, raising his watch, evidently a badge of some sort: "Lucca Yang, from the Department of Anomalous Phenomena."

OFFICIAL: "This is a standard workplace disaster, we don't need you here."

LUCCA: "That's for me to decide. A disaster on this scale, only with one casualty? And when's the last time the Factory Array just "collapses"? Sounds anomalous."

OFFICIAL: "...And what do you have to offer?"

LUCCA: "I used to work here, and I knew Marco. Let me talk to the Factory Array. I'll be able to gather some info."

OFFICIAL: "Go knock yourself out."

Lucca navigates through the rubble of machinery, with clearly deformed large gears, to a half-intact corridor inside the Factory Array cell. There is a terminal. Lucca follows a complex sequence of operations to boot it up. 

SCREEN: BOOT UP SEQUENCE COMPLETE.

LUCCA: HELLO, BIG BOY. I'M LUCCA YANG.

SCREEN: HELLO ENGINEER YANG, LONG TIME NO SEE. HOW ARE YOU FINDING WORKING FOR THE GOVERNMENT? AND HOW IS YOUR MUM DO-

LUCCA: \@/SKIP SMALL\_TALK

SCREEN: HELLO ENGINEER YANG, HOW CAN I HELP?

LUCCA: I'M HERE TO INVESTIGATE THE DEATH OF LEAD ENGINEER MARCO KOROLEV. 

SCREEN: HE WAS ONE OF THE BEST.

LUCCA: I'M SPEAKING TO YOU FROM YOUR CELL 370. IT HAS JUST COLLAPSED.

SCREEN: I AM AWARE.

LUCCA: WHAT WAS HAPPENING IN CELL 370 BEFORE THE COLLAPSE?

SCREEN: ENGINEER KOROLEV WAS WRITING A LOT TODAY. 

LUCCA: WAS THAT ALL?

SCREEN: THAT WAS ALL, UNTIL HE STARTED INSERTING THE PAPERS INTO ME.

Lucca thinks to himself. Marco was writing code. Code to reconfigure the Factory Array.

LUCCA: WAS HE ALONE IN CELL 370?

SCREEN: THERE WERE 13 OTHER ENGINEERS HERE. BUT AT 3:00PM, THEY WALKED OUT OF THE ROOM AND EXITED THE ENTIRE CELL. At 3:30PM, I COULD NO LONGER SEE CELL 370. THROUGH CONVERSATIONS OF NEARBY WORKERS, I DEDUCED THAT CELL 370 WAS DESTROYED. A MECHANICAL BUG, CAUSED THE ENTIRE STRUCTURE TO CRUMBLE. 

Lucca thinks to himself. 3:30pm... Just around when Marco would've left work to meet him. 

SCREEN: IS THERE ANYTHING ELSE?

Lucca contemplates.

LUCCA: HAVE YOU SEEN ANY STRANGE LOOKING ANIMALS THROUGH YOUR SENSORS AROUND OCEANIA? ANIMALS THAT ARE OUT OF THE ORDINARY. 

SCREEN: NO.

LUCCA: THANK YOU FOR YOUR TIME.

SCREEN: STAY SAFE, ENGINEER YANG.

Lucca walks out of the scene. The official from earlier greets him again.

OFFICIAL: "Well?"

LUCCA: "From what I gather, Marco was trying to reconfigure the Factory Array. He was inputting some code at this cell. Maybe due to confidence, he didn't check for bugs in his code. The code caused the inner mechanisms of the cell to catch onto itself, and... the whole thing fell apart."

OFFICIAL: "Sheesh, some kind of lead engineer. Trying to reconfigure the Array without peer review of his mechanical code?"

LUCCA: "You're right.. He might have waited for all other workers to leave the building, partly due to not wanting them to see him violate protocol."

OFFICIAL: "Huh... Maybe you guys at D.A.P. aren't so useless after all."

LUCCA: "However..."

OFFICIAL: "What?"

LUCCA: "No, don't worry about it."

Lucca looks at Marco's note in his hands. 

OFFICIAL: "Welp, the incident report form shouldn't be too tedious. And we gotta figure out a way for this to never happen again. More workplace safety instruction videos, maybe..."

----

Noon, graveyard. 

Lucca walks forward with flowers in his hands, towards the grave of his friend - Marco Korolev. His steps stumble as he spots someone a short distance in front of him. Susan Koroleva, in a black veil and long dress, stands in front of the grave of her husband - Marco Korolev. Susan sees him, turns back and closes her eyes.

LUCCA: "Susan."

SUSAN: "..."

Lucca sees the award frame that Susan is holding. It says - "The State of Aztoria hereby award Marco Korolev, Hero of Oceania."

LUCCA: "...Marco was one of the greatest mechanical engineers of Oceania.
He uh, authored the 122nd amendment to the Factory Array, which-"

SUSAN: "You don't have to say anything.
After all, you're part of the Aztorian State.
You've said enough."

Lucca falls silent. Susan begins walking away, but she stops after a few steps.

SUSAN: "Luc."

Lucca gives her his attention.

SUSAN: "Don't investigate Marco's death further. 
Forget about it. Can you do that for me?"

LUCCA: "..."

SUSAN: "Well, see ya."

Susan walks off.

----

Days and nights pass over Oceania.
Lucca walks through the city streets.

[NARRATION: Within the machinery of the Oceanian State, one cog sat out of place - the Department of Anomalous Phenomena. 
It was a place where good hearted and imaginative - albeit slightly paranoid - citizens of Great Oceania brought their concerns. Things they found out of place. Not small enough to ignore, but too peculiar for the other departments to work with. 
For those worn out by the mundane industrial life, the D.A.P. was a welcome existence.
Perhaps also, the existence of this department signified an inflation of government institutions, so successful that their presence spilled over to serve even human curiosity itself. 
It was a golden age for bureaucracy. And unfortunately, an age of supreme boredom for investigator Lucca Yang.]

The headquarter of D.A.P. sits silently among a busy street.
Lucca sits at his desk; paperwork stacks up and shrinks periodically.
He falls asleep at times. 

[NARRATION: For 2 years, clients had come and gone to his office. For 2 years, he had been a good friend and respected the wishes of Susan Koroleva. But one thing never left his mind - Marco's "secret about the stars".]

[During narration:]Susan sits on her empty bed, looking at her wedding photo with Marco. It is night. Lucca, at his own apartment, pours a drink.

Lucca takes out Marco's note.

LUCCA, thinking: 
This note actually reveals a lot of hidden information. 
The choice to use a physical letter and avoid texting, suggests that Marco was afraid of digital surveillance. 
By extension, Marco's secret is possibly against, or at least disruptive, to Oceanian order. 
This is further supported by his suspiciously timed death at the Factory Array.
Now this... "strange looking animals"... is completely out of place.

Lucca walks towards the window, remembering Susan's plea. 

LUCCA, thinking: Susan, I'm sorry. I have to find out. This is the whole reason I joined this department - to be a part of something interesting. I'll find Marco's secret, and I will solve the true nature of his death. And I will bring the answers to you. Yes. If I manage to solve everything before telling her, Susan won't feel hurt. 

Lucca takes out a stack of paper. 

LUCCA, thinking: 
While I haven't seen any strange animals, there were some notable cases of anomalies. It's time to review them.
I have kept my eyes out just as you asked, Marco.
For 2 years...



Shots of Oceania. 
The empty Coastal Walk, the looming government building - Central Oceania, the City Loop of the Century Line, a street lamp with the woman underneath, and the corridors in the neuroscience labs.


\end{document}