\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Susan and Lucca Celebrate}
\maketitle


Lucca and Susan sit in a room. Above them are the Directors of all major departments of the Ocean Union. Susan trembles. Lucca notices.

[Lucca eases the mood; Directors tell them they are getting awarded "Hero of the Ocean Union".]

[Lucca and Susan sit on the Continental Express. Susan thanks Lucca for easing the mood. Susan exclaims that they are now heroes of the Ocean Union. Lucca is silent. They go to Aloh's bar.]

SUSAN: "Hehe... Don't just stare at me, join me!"

LUCCA: "Not staring at you, I'm staring at your glass. Aren't you drinking too much?"

SUSAN: "What? How dare you tell me how to drink!"

LUCCA: "You know what I think? I think we both know something's not right. And you are trying to ignore it."

SUSAN: "You're such a buzzkill... [leaning over to Lucca] Living is already such a drag, at least let me enjoy this moment."

LUCCA: "You're only fooling yourself. Tomorrow you will be sober. By next week your excitement will be over. Then life goes on year after year. A continental conspiracy looms, and nothing changes."

SUSAN: "It's funny... It's like you can't wait to live out the rest of your life in your head. Like you can't wait for your whole life to be over."

This takes Lucca aback. Susan drinks while Lucca thinks. The silence goes on for an uncomfortably long time.

SUSAN: "Aloh! Bring me a mike!"

ALOH, instantly appearing next to her and bowing: "Here you go, Miss Koroleva."

SUSAN, royally: "Thank you!"

The sound system screeches, the people of the cafe watch Susan as she steps into the center. 

SUSAN, singing a famous song: "Precession of history... Evolution of human deeds... City lights have a tale to tell, and an end is a start as well..."

Susan drags Lucca to a dance. He remembers their university days, of Marco and him inviting Susan to a dance. Lucca kept stepping on Susan, prompting Marco to take over. 

It's unknown how long Susan and Lucca danced in Aloh's cafe until Susan collapsed.

----

Lucca places Susan onto her bed and walks off. He spots her drawings on the table - of her and Lucca. Lucca has a pitiful and moved smile.

Lucca decides it's a good opportunity to search her house for Marco's secret. 
Meanwhile Susan dreams and thinks she is waking up, to look for Lucca.
As she sees Lucca in a dark room, we switch to Lucca's perspective. 

A deformed creature is standing in the doorway, with vaguely Susan-like shape. 
Susan is still sleeping in her bed.




\end{document}