\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Beneath the City Lights, She Appeared}
\maketitle

New Melbourne coast, dusk.

Lucca, with neatly combed hair, large pair of glasses, dressed in a BEIGE trench coat, stands beneath a row of tall rectangular buildings, with no windows nor doors. 
The buildings block out part of the city lights, leaving long patches of light and shadow onto an empty Coastal Walk.
He looks about his surroundings and takes out a note.

NOTE: Dear Luc, I discovered a secret about the world. 
Meet me tomorrow on Coastal Walk, New Melbourne. Come at 5:00pm.
If you can, keep an eye out for strange looking animals on your way. 
Don't text me about any of this. See you then.
Marco

Lucca looks at his watch. It is 6:15pm. 

LUCCA, thinking: Did I get the time wrong? Last night's "tomorrow" is definitely today. 
Is there a time zone problem? Marco works at the 13th cluster of the Factory Array... Only one hour earlier than here in the capital. 
Did Marco get caught up in something? He would've notified me.

A flock of birds with devolved eyes fly from the ocean. Lucca reaches down towards it.

LUCCA, thinking: Northern bird. Their eyes are useless thanks to mutation caused by radiation; they navigate via magnetic fields. While some could consider them to look strange, they are so common in Oceania, Marco is likely not refering to them. 

Lucca turns around and looks at the city.

LUCCA: "Alright, you win. You've hooked me now. Just what kind of secret...?"

Suddenly, Lucca notices a woman in a black trench coat standing in the distance on Coastal Walk. The woman is fixed in place, and doesn't speak. They gaze at each other. Lucca is visibly unnerved. The woman disappears. 

LUCCA, thinking: the tedium and boredom of bureaucracy must be getting to me... Getting excited about Marco's note and coming all the way out here... and now outright hallucinating a person that isn't there. What am i doing...

Lucca's watch rings. 

LUCCA, thinking: crap, it's Director Alma.

He picks it up.

LUCCA: "Director?"

ALMA: "Lucca! Where the hell are you? Did you escape from work?"

LUCCA: "Well technically no... I'm investigating an anomaly, as my job entails."

ALMA: "..."

LUCCA: "Look I'm, I'm sorry. I'll make up-"

ALMA: "I was looking for you."

LUCCA: "..."

ALMA: "Your friend, Marco Korolev..."

LUCCA, surprised: "Marco? What about him?"

ALMA: "He... the portion of the Factory Array he was working at, collapsed. Marco was crushed."

Pause.

LUCCA: "You're serious."

ALMA: "I'm sorry."

LUCCA: "Huh..."

ALMA: "We dispatched a disaster response team. It appears no other worker was injured."

LUCCA: "...That's a relief."

----

Lucca is on the Century Line. He won't stop moving his heels up and down, attracting a few glances. He remembers a few moments with Marco - Lucca walking through a uni campus, carrying a bag, spotting Marco reading a textbook on the lawn; Marco proudly putting on his working hat, while holding an engineering blueprint in his other hand; Marco and a woman dancing while Lucca watches; Marco and the woman getting married while Lucca watches...

Back in reality, Lucca arrives at the Factory Array and looks towards the rubble. What he is seeing is a mere cell of the colossal organism that is the Factory Array. A few workers and a fireman come towards Lucca.

WORKER: "Lucca! You came!"

LUCCA: "Long time no see. I heard about Marco. What happened here?"

WORKER: "We haven't the slightest clue. We were just going through our daily maintenance in a neighbouring cell, until we heard loud screeches. By the time we followed the noise and ran here, this cell has totally collapsed."

LUCCA: "And no one else, except for Marco, was caught in it?"

WORKER: "Not that we know of. You're better off asking the big boy yourself."









\end{document}