\documentclass[11pt]{article}

% to set margins as i inch
\usepackage{fullpage}

% set paragraph spacing
\setlength{\parskip}{10pt}

% to include links in the table of contents
\usepackage{xcolor}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=olive,  %choose some color if you want links to stand out
}




\begin{document}

% titlepage
\begin{titlepage}
\title{Design Document for Oceania of Stars}
\author{Alex Li}
\date{\today} % automatically changes every compilation
\maketitle
\thispagestyle{empty} % removes page number from this title page
\end{titlepage}


% table of contents, auto generated. Have to click build twice.
\tableofcontents
\newpage % same function as MS Word page break 



\section{Premise and Plot}
	\subsection{Premise}
	Alien sightings reveal conspiracy.
	\subsection{Plot}
	A civil servant is ecstatic at the rumours of alien sightings across Oceania, and wants to investigate.
	
	His investigation is met with heavy resistance by the government for which he works.
	
	Despite this, he manages to find an alien, but it's not what he was hoping for. The alien's origin reveal a grand conspiracy that threatens the future of humanity.
	
	He has to carry out the final steps of a century long plan by the founders of his country to defeat the conspiracy. 
	\subsection{Plot points}
	Lucca works at the Department of Anomalies. 
	...
\newpage
\section{The Conspiracy}
	
	
\newpage
\section{Characters}

\newpage
\section{Chapters}
	\subsection{Beneath the City Lights, She Appeared}
	
	\subsection{Star Watcher}
	Amateur astronomer sees star disappear at the same time every day. It is an image of Nerezza. Lucca cannot begin to understand.
	\subsection{Paradox at the Factory Array}
	Another cell at the Factory Array collapsed. Lucca interviews the engineer - sole survivor - sitting on the ground. The AI she created for the Factory Array broke down, killing everyone. The AI contemplated the Fermi Paradox. When it came to the engineer, the AI asked her what her last words were. She told it a simple paradox, leading to its destruction. The sun rises over the rubble of cell 2120.
	\subsection{Phantom Around the Galaxies}
	Physics student comes to Lucca about anomaly in galactic mass. They discover together it was an old unsolved mystery in 21st century physics - dark matter. Susan wakes from her bed, walks to the desk and starts drawing. 
	\subsection{Organism}
	The Dark matter and Fermi Paradox combine together to suggest that aliens are all around the galaxies. Lucca hypothesises that Marco was refering to aliens. Lucca finally encounters a truly bizarre organism, witnessing what Marco saw. Lucca tries to take a photo but the image does not reveal the organism. He brings it to Tom but Tom says if instruments cannot capture it, it cannot be studied. Lucca then posits that the organism may only be perceptible by consciousness. He goes to the neuroscience labs, meeting Professor Lambda. In an unknown location, a few people are discussing that Lucca has been enquiring about aliens. Back at the labs, Lucca and Lambda take a walk through the place, and Lucca sees Susan sitting. 
	\subsection{To Capture an Alien}
	Susan is ecstatic to see Lucca and asks what he is doing here. Lucca stumbles on his words and hides his investigation. Instead, he says he is investigating aliens. Susan finds this amusing. Susan speculates whether the government knows and warns Lucca to be careful, while she points to 2 suspicious people following them in the distance, implying them to be government agents. Lucca wonders if he is endangering Susan. 
	\subsection{For All Humankind's Happiness}
	Lucca visits Susan's 
	\subsection{My Truest Heart For You}
	
	\subsection{Once More Under the City Lights}
	
	\subsection{Interpretation of a Dream}
	
	\subsection{Approaching the Nest}
	
	\subsection{Professor Lambda's Sorrow}
	
	\subsection{Project Hypnos}
	
	\subsection{History's End}
	
	\subsection{New Human}
	
	\subsection{Oceania}
	
	\subsection{The Warm Currents of Time}
	
	\subsection{Stars on the Ground are City Lights}
	
	

\end{document}