\documentclass[11pt]{article}

% to set margins as i inch
\usepackage{fullpage}

% set paragraph spacing
\setlength{\parskip}{10pt}

% to include links in the table of contents
\usepackage{xcolor}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=olive,  %choose some color if you want links to stand out
}




\begin{document}

% titlepage
\begin{titlepage}
\title{Oceania of Stars}
\author{Alex Li}
\date{\today} % automatically changes every compilation
\maketitle
\thispagestyle{empty} % removes page number from this title page
\end{titlepage}



% table of contents, auto generated. Have to click build twice.
\tableofcontents
\newpage % same function as MS Word page break






\section{Beneath the City Lights}

Lucca walks at the south-eastern shore of Oceania. Shots of the city skyline, with an eerie row of oddly uniform buildings with no windows or doors. 

Lucca takes a letter out of his pocket and reads it.

LETTER: "Luc, I discovered a secret about the world. 
Meet me tomorrow 6pm at the abandoned shoreline, near the City Loop. 
Pardon the strange way of communication. 
Don't text me about this. Marco"

Marco doesn't show up. Lucca starts considering the possibilities. Did I get the time wrong? Did Marco get caught up in something? Did Marco forget? (IN THAT ORDER.) ...Is Marco in danger?

Suddenly, an image of a woman in black appears briefly, and disappears. This startles Lucca. 

\section{Lucca's internal journey}
	\subsection{Lucca asks mum about heat death}
LUCCA: "Then, what's the point?"

MUM: "Hm?"

LUCCA: "What's the point of humanity existing, if we know there is no way for it to survive something in the future?
Are you going to tell me that death is what makes living meaningful?"

MUM: "Son, you're speaking to your mum. You should know that I won't just spit out the same old rhetoric that everyone spouts without much thought.
You know i always try to understand you."

MUM: "You want a solution right? Well you have forgotten about something - cosmic civilisations. 
We have no idea what they will be capable of, and the effects that even their presence could have on the universe."

LUCCA: "Then, we have to spend every resource on solving that problem right now! And don't tell me that 'the problem is too far away', that's what they all say. That's what people said about the greenhouse effect back in the 21st Century, before environmental catastrophe almost wiped them all out!"

MUM: "Sure, sure. You want humanity to be an enlightened, advancing society with never-ending progress, like a train driving full speed towards its destinations. I actually think that's a very kind thing to wish for.
But hey, even on a train like that, it's worth while to stop along some stations, step outside and watch the flowers."

	\subsection{Lucca and Susan, at Susan's house}

Lucca suggests that Marco's death could be related to the Government.
Susan slaps him. 

LUCCA: "I'm, I'm sorry, I have to... ask uncomfortable questions.
If this really is the case, then it could spell trouble for the people of Oceania. 
If Marco's secret is hidden forever, who knows what will happen to us all?"

SUSAN: "It's funny... It sounds like you can't wait to live out the next 50 years of your life today. It's as if you can't wait for your whole life to be over."

This shocks Lucca.

SUSAN: "You're just like Marco... 
Never leave a stone unturned. 
Never leave a question unanswered."

LUCCA: "Questioning the Institutions is how truth will thrive, and humans, alongside it..."

SUSAN, emotional: "Who cares what the Government is doing?"

SUSAN, leaning over her table: "
That's the problem with you, Marco...
Always burying your head in history books...
Some kind of 'Hero of Oceania', Marco...
What question is so great, that it's worth dying for?
What cause is so great, that it's worth dying for!?"

SUSAN: "Before that cause, there is LIFE!"

Susan stumbles towards Lucca, hitting him on his shoulder: "A life, spent with me..."



\section{Marco's journey}



\section{The Conspiracy}
A conspiracy to euthanise humanity.

	\subsection{Origin}
	The Director of Future History discovers that humanity is heading towards a dead end. 
	


\section{Anomalies}
Main mysteries that Lucca will have to solve.

0. Marco's death

1. Iron shortage in Oceania.

2. Coastal buildings with no windows nor doors

3. City Loop inscriptions

4. Dark Matter

5. Fermi Paradox

6. Newons

7. Nerezza's images

8. Government adversion to rocket science


\section{Secrets of the world}
These secrets hold the key to the future of humankind.

1. The solution to Dark Matter and the Fermi Paradox is alien civilisations. 
The Dark Matter halo around the galaxies surround the outer rims. 
This is the galactic habitable zone. 

2. An alien is in Oceania. 
Aloh, manager of a communal dining space, came from the stars. 
He is here to lead humanity to its future.

3. Humans have evolved. 
Leading a mostly carefree existence, the human brain has expanded its abilities, to be able to interpret Currents. 
As a result, humans are now proto-telepathic, and can anticipate into the future.

4. Consciousness is Currents of spacetime.

5. The Century Order long ago set in motion a plan to stop Project Chronos.
The City Loop is a giant loop of wires.
The coastal buildings are magnets.
The Department of Anomalies was founded to keep watch of the Government.









\end{document}