\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Beneath the City Lights}
\maketitle

[skip intro]

Aloh's dining space.

ALMA: "For good vibes everywhere, if you have feelings they can't tame...
Hop on board without a care, just come get on the A Train..."

Lucca takes a sip from the soup. 

LUCCA: "Spendid! Liz, you're becoming more and more professional.

LIZ: "Really!?"

LUCCA: "At this rate, you may even surpass Mr Aloh over here!"

ALOH: "Hey, check this out."

NEWSPAPER: "COOKING SHOW MURDER: ARREST FOR MURDERER IS ON THE WAY."

LUCCA: "Oh, the one with the insufferable judge."

ALOH: "Can't annoy anyone now that he's dead."

LIZ: "That's a bit harsh..."

ALOH: "Wow, the CPI has gathered proof! And they also know where the killer is!"

LUCCA: "Finally. 
Awfully slow of them this time.
2 months to solve a simple murder?"

LIZ: "CPI..."

LUCCA: "The Civil Protection Institute. 
You would've met them before."

LIZ: "Yeah... back when i was on the show, after the murder, they put me through a lie detector test."

Brief silence.
Singing in the background.

LUCCA: "Liz. 
Was it really harsh when Aloh talked about the judge being dead?"

LIZ: "What do you mean...?"

LUCCA: "I mean that, the judge was also harsh to you.
When he mercilessly threw your dish - your late father's signature dish - into the trash can, and spat on it."

LIZ: "...You... watched the show too?"

LUCCA: "Of course, that's how I knew who you were when you first came to this communal dining space."

LIZ: "Anyway... he was mean, but... he didn't deserve to die."

LUCCA: "Liz, do you really believe that?"

LIZ: "Yeah..."

LUCCA: Satisfied.

LIZ: "Hey, Mister Lucca, next time you should come watch my competition live."

LUCCA: "You know I'm too busy to do that."

LIZ: "What do you do all day anyway?"

LUCCA: "It's a secret."

ALOH: "You gotta realise that the obnoxious behaviour of the judges are all for show. 
They wanna keep the audience entertained.
Hmph! They probably can't even cook!"

Someone: "ALOH!"

ALOH: "Coming~~~"

LIZ: "I can only imagine... being poisoned like that."

LUCCA: "Well, we don't know that. 
The cause of death was never announced by the CPI."

LIZ: "Oh yeah."

LUCCA: "Hm.
The Civil Protection Institute will catch the killer tonight!
Why? Why announce it like this?
Maybe to provoke some kind of response...
Maybe even...
Redemption."

Lucca looks to his right.

LUCCA: "Liz? What's wrong?"

Lizs eyes are wide. She is profoundly terrified.
Background singing.

LUCCA: "You want to tell me something."

LIZ: "Iwsm."

LUCCA: "What was that?"

LIZ: "It was me."

LUCCA: "It was you what?"

LIZ: "It was m-me... who poisoned the judge... 2 months ago..."

LUCCA: "..."

LIZ: "Oh!"

LIZ: "I shouldn't have done it!"

LUCCA: "Does anyone else know?"

LIZ: "No... there's no one i can trust..."

LUCCA: "Good earth! Well, you need to, damn... be careful!"

LIZ: "Yeah... I know..."

LIZ: "These 2 months were only bearable after meeting Aloh and you. 
I can't..."

LIZ: "They said they will catch me tonight?
I wonder w-where they are now..."

LIZ: "Oh... to think I could escape the CPI..."

Lucca places a hand on her shoulder.

LUCCA: "You trusted me, and you told me the truth.
And that's important.
Admitting your mistake, regretting it, is the first step to rehabilitation.
And after that, there is still life..."

LIZ: "Mister Lucca..."

She sees the entire dining space of people standing behind her.

LIZ, horrified: "Lucca, you..."

LUCCA: "That's right. I come from the Civil Protection Institute."

LIZ looks down, defeated.

LUCCA: "The CPI knew from the very beginning. 
Our Lambda Detectors are flawless at detecting lies. 
You did not pass the test."

LIZ: "Then, why did you wait for 2 months..."

LUCCA, as if gently explaining to a child: "The CPI has mathematics, sophisticated enough to predict the probability of certain events.
When applied to you...
We saw that there was a higher than 50\% chance that you would admit your wrongdoing.
It would help greatly in the Institute's judgement of you.
We have been waiting to capture that moment.
In the meantime, you were unlikely to endanger anyone else, and... I could keep an eye on you if you did."

LIZ: "..."

LUCCA: "You have the potential to be an excellent cook!
I look forward to your re-emergence."

They take her away.

[skip outro]

ALOH: "Goodness, lost a whole night of visitors."

LUCCA: "The institute will reward you for sure."

ALOH: "Hah! Tell your director - "

ALMA: "I'm director Alma."

ALOH: "Oh! I didn't know! What an honour! Your singing was spectacular!"

ALMA: "You're too kind."

ALMA: "Lucca, well done on the psychological operation."

LUCCA: "Liz never saw the things hiding around her until it was too late..."

ALMA: "It's a matter of whose shoes you're standing in.
You may know one or two things that the average Aztorian citizen doesn't. And I know some things that you don't.
And my higher-up, knows things that I don't.
And Aztoria, the city itself, probably hides things that none of us knows."

NARRATION:
Often, if you wander beneath the city lights, you will see them -
the exemplary sentinels of Aztoria.
They are the Civil Protection Institute.



\end{document}