\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{New Plague}
\maketitle

At night, professor Lambda feels intense cosmic terror. He panics while seeing mundane things in his room. He slams his hand into the table, as narration begins.
A Newon looks in the background.

[NARRATION: What is a scientist?
The word can be traced to the ancient language of Latin - "scientia"...]

\ 

\ 

Lucca is chatting with other institute agents.
He receives a call from his watch.

ALMA: "Lucca, come to my office."

\ 

Alma's office.
She is listening to "get on the a train".
A gyroscope spins on her desk.

LUCCA: "Director Alma."

ALMA: "I want you to help Professor Lambda retire."

LUCCA: "Professor Lambda? THE professor Lambda?"

ALMA: "Yes. Head of Neuroscience, did service to Aztoria for 40 years.
Helped with many neuroscientific inventions we enjoy today."

LUCCA: "An admirable individual...
Erm, shouldn't a more experienced person conduct this handover?"

ALMA: "Oh, Luc. 
Don't be deluded by the bureaucracy.
It's really not that complicated.
Besides, the new Head of Neuroscience might be a pleasant surprise to you."

LUCCA: "Oh?"

ALMA: "Bring the sum of Lambda's knowledge to us.
Make sure the new Head speaks her pledge.
That's all."

\ 

\ 

Lucca stands in front of the University.
He walks into Lambda's office.

LAMBDA: "I've been waiting for you."

[NARRATION: Due to abundance, the people of Aztoria live to 120 - the natural lifespan of a human.
Though, it is not out of the question that humans should evolve to beyond that number.]

LAMBDA, holding up a rocket model: "Rocketry fascinated me when I was young...
I actually wanted to pursue aerospace engineering.
But the Government and the Institute INSISTED that neuroscience was the way of Aztorian science."

They now walk along the corridor of the labs.

LAMBDA: "These are our testing rooms."

They walk into a patient room.
Lambda sits down next to a woman and asks her experiences.

WOMAN: "Very very tired. 
And sleepy. 
At night, I dream about walking around the labs, even though I'm actually sleeping in bed."

LAMBDA takes notes and hands them to an assistant.
He asks to go to the toilets for a while.

ASSISTANT, to LUCCA: "Rumour has it Professor Lambda has one big regret.
But no one knows what it is."

LUCCA: "How do you know he has a regret then?"

ASSISTANT: "Very often, he will look at the labs and sigh.
We're pretty sure there's something he wants to do but didn't get to.
And today is his last day.
Do you think you can help him?"

LUCCA: "My abilities are limited in a very human way.
That is to say, I can't read minds.
Professor Lambda, maybe. But not me."

ASSISTANT: "You're from the Institute, right? 
That makes you half a sleuth.
Surely you can help him."

LUCCA: "I'll see what I can do."

\ 

\ 

Interior, Institute.

DIRECTOR ROBERT: "Has Lambda been retired?"

ALMA: "All is taken care of. Don't worry."

DIRECTOR ROBERT: "Who did you send?"

ALMA: "Lucca, the new recruit."

ROBERT: "The NEW? RECRUIT?? You are insane."

ALMA: "You need to chill a bit.
Come sit down and listen to some jazz, Director Robert."

ROBERT: "Is Lucca already in on the Synthesis Project?"

ALMA: "Yep. He's already in. 
Aztoria's secrets are still safe within the Institute, among people we can trust.
And Lucca is someone I trust."

\ 

\ 

Lucca and Lambda walk pass an A Train scale model.
Looking at it, Lambda starts reciting a speech.

LAMBDA: "What is a scientist? 
The word can be traced to the prehistoric language of Latin - "scientia". 
Scientia is to know. 
In time, when Aztoria matures, it will describe one of the most prestigious positions in society, right under the Institute and the Government. 

So what is a scientist? 
A scientist is someone who seeks knowledge and shares the truth. 

Why does a scientist work?
To protect the happiness of all humankind.

The Aztoria University will be constructed in dedication to all the future scientists of the world."

LUCCA: "That was the speech..."

LAMBDA, nodding: "400 years ago, Aztoria began right here, at the centre of the train line's City Loop. 
The old scholars of earth gave that speech to the entire city."

LAMBDA, turning to Lucca: "Consider pursuing science yourself?"

LUCCA: "Before graduating from the Aztoria University, I did have a choice to stay back. 
Instead, I chose to be a mechanical engineer at the Factory Array."

LAMBDA: "And you must have received a promotion to the Institute.
That's a wise life decision.
Bureaucrat is a good position.
You get to organise every one of our decisions."

LUCCA: "I don't know if I should bear that kind of responsibility."

\ 

\ 

In the gardens, they meet the new head of neuroscience.

LAMBDA: "The new head is waiting for us over there."

Seeing her, Lucca's eyes light up.
She turns to look at them, and also is visibly surprised.

LUCCA: "Susan! You're!"

SUSAN: "I knowwwww! I'm so excited! And I'm excited to see you here, Luc."

LAMBDA: "You two know each other?"

SUSAN: "Yeah, from primary school till highschool."

LAMBDA: "That will make things super smooth then. Let's get right to it."

\ 

\ 

They walk pass a corridor.
Lambda immediately redirects Lucca away from the corridor.
The reader can see an alien looking organism in the background.

\ 

Outside Lambda's office, Lambda hands Lucca a usb.

LAMBDA: "Here, these are the sum total of my research over my life time."

LUCCA: "Thank you." 

LUCCA, turning towards Susan: "Now, Susan, you need to speak your pledge to Aztoria."

He hands her the script, and holds a voice recorder up.

SUSAN: "A bit twisty on the tongue."

LUCCA: "You should be familiar with it by now."

SUSAN: "I, a citizen of the Humanist City State of Aztoria, upon having conferred on me the high calling of the Aztoria University’s Head of Neuroscience, entering this role I pledge once again:

To dedicate all my intellect and strength to the preservation and improvement of - the knowledge of humankind, and to work in good conscience wherever it is required in Aztoria;

To preserve and develop the noble traditions of Aztorian science, to be guided in all my actions by Humanist Philosophy, and the principles of  Societal Evolution Dynamics, and to always bear in mind the high calling of an Aztorian scientist, and my responsibility to the people and to the Aztorian state bureaucracy;

To be an honest, diligent, disciplined and tireless fighter for knowledge, to guard strictly all state secrets;

And above all, to obey all laws and orders of the Aztorian State, under the guidance of the Computers of the Aztorian Government… and its Protectors at the Civil Institute; (looks over to Lucca and smiles)

And if through regressive intent I break this solemn oath, then let the Aztorian law, through the Civil Protection Institute, deliver its justice, and let the universal hatred and contempt of Humanity… fall upon me... I swear to be loyal to this oath as long as I live.”

LUCCA: "Wonderful."

LAMBDA: "Now that it's over, may I have a few minutes with Susan?"

LUCCA: "Sure."

LAMBDA: "Come in."

He shuts the door behind Susan.

\ 

\ 

Interior, Alma.

ALMA: 
"Lambda... More than a secret, more than a plague… Today may go down in the history of Aztoria as one of the most important. 

On the day of handover, you will be forced to examine your career - and your life. The future of all of us rests in this tiny, suffocating disturbance of balance. 

Not that the future hinges on you alone - if you don’t do it, Susan will. If she doesn’t, her successor will. Such is the real prediction of SED. But only, one more century down the drain, one more tear lost in the cosmic ocean. And I won’t be there to witness it. What will you do, Professor Lambda?"

She looks at the clock. The day is about to end.

ALMA: "Maybe I placed too much hope in Lucca."

\ 

\ 

Patients walk pass Lucca accompanied by scientists.
The patients look at him with a certain dread.
One of them looks a bit deformed.

Soon, Susan walks out of the room hurriedly.

LUCCA: "Susan, are you okay?"

SUSAN, with tears in her eyes: "Yep. Don't worry about it."

LUCCA, watching her walk away, thinking: This confirms it. 
The nature of this regret is transmittable, like a disease.
Within 10 minutes. 
From Lambda to Susan.
Kind, joyful Susan from highschool.
The regret is likely tied to their position, and their field.
A single secret dispensable within minutes.
Lambda... What do you know that the rest of us don't?"

Lambda walks out of his room. 

LAMBDA, thinking: 
Poor Susan, the burden lives inside you now.
But you will have a comfortable life, and come to be respected.
I got my reward of a prestigious life, and I am about to leave this building without consequence.
Hah! That must be the kind of person...
Old, despicable Lambda.
I am the worst scientist humankind has had the displeasure of knowing.

LUCCA: "Professor Lambda."

Lambda halts.

LUCCA: "We all have regrets.
I am no man of science, but I have regrets.
What the neuroscience labs are studying, I have no idea.
But I get the sense that you want to tell me something.
You have a choice here.
You can ignore that regret, leave here and never look back.
You live out the rest of your days, enjoying the peace and abundance that Aztoria gives us.

Or, you resolve it today.
I don't know the consequences, for I'm not involved in the convolutions of institution deep enough.
But you will live up to the weight of the sacred name you had chosen to bear upon yourself - a true scientist."

LAMBDA: "Where is this coming from? There is no such thing as a regret."

LUCCA: "Lambda, a scientist shares the truth and works to protect the happiness of humankind."

LAMBDA: "A scientist also keeps all state secrets."

LUCCA: "By the authority of the Aztorian Bureaucracy, I command to SPILL that state secret!"

LAMBDA: "That's a contradiction in terms. 
Look, I am not going to-"

LUCCA: "You're a scientist."

\ 

Lambda stops speaking. 
He looks at Lucca.
After a long time, he starts walking towards the speaker. 
Shots of.
Lucca.
Susan, distraught.
Alma, looking at the clock.

Suddenly, he turns it on!

LAMBDA: "Citizens!"

Alma IMMEDIATELY STANDS UP AND LOOKS TOWARDS THE CITY!
Susan stops walking.
Lucca stands with arms crossed. Eyes hidden under glasses.

LAMBDA: "There is a new plague within Aztoria! 
Right here, in the heart of the neuroscience labs!"

LAMBDA: "Symptoms involve extreme fatigue, sleepiness, death results in sleep after days of malnutrition.
Plague is spread by plague carriers - black organisms that emerge from your head when you're asleep.
My colleagues, I'm sorry, that's what we've been studying. 
A plague of Aztorian design!
Save yourselves! 

I say it again!
There is a new plague within Aztoria! 
Symptoms include..."

\ 

\ 

Nerezza SHARPLY smiles.
Aztoria University.
Birds land.

LUCCA, looking at the university: "See, you were a good scientist, professor Lambda!"



\end{document}
