\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{A Doctor of Death}
\maketitle

Interior, night, Lucca's apartment.
Lucca picks up the phone. 

PHONE: "Oh thank the earth, you haven't changed your number!"

LUCCA: "...Emma!"

EMMA: "Heehee, you still remember me, Luc."

LUCCA: "What's the matter?"

EMMA: "Have you heard? 
There's a primary school reunion coming up.
Well, I guess that's my job, to tell you that. 
Ehehe."

LUCCA: "Wow... Sweet, tell me the location and time, and I'll meet you all there."

\ 

\ 

On the Aztoria Train.
A sound of humming comes from Lucca's left.
Lucca turns left, a bit taken aback.

It is a woman in black.

LUCCA: "Uh... excuse me."

The woman stops singing.
She slowly opens her eyes and turn to look at Lucca.

LUCCA: "I zoned out. Where is this train going?"

WOMAN: "Barassi."

LUCCA: "Thanks."

LUCCA, remembering his vision at the shore: "May I ask your name?"

WOMAN: "I am Nerezza. You?"

LUCCA, extending his hand for handshake: "Lucca. Nice to meet you."

NEREZZA: "Sorry, I am carrying a suitcase. Nice to meet you."

LUCCA: "What do you do?"

NEREZZA: "I'm a doctor. I travel the outer rims of this city."

ANNOUNCEMENT: "YOU HAVE REACHED -- BARASSI STATION. 
THANK YOU FOR BOARDING THE AZTORIAN TRAIN -- PROVIDING THE BEST TRANSPORT SERVICE FOR HUMANKIND.
CHANGE HERE FOR -- WATERLOO -- STATION."

\ 

\ 

Night, school reunion.

CLASS REP: "Good evening!

Reunions rarely had this much traction before the extinction.

It's clear that our beautiful times under the Aztorian education system had not faded from our memories.

It's especially an honour for our teachers to accompany us!

Mr Young!
Mrs Petrov!
Mr Sodhi!"

CLASSMATE MURMURING: "And Mr Willians? Where is he?"

CLASS REP: "Mr Williams is ill, so he couldn't be here. Well then...
Class of 2578, let's introduce ourselves!"

PETER: "I'm Peter! I overlook the food delivery of District 21."

EMMA: "Emma. I work as a computer for the government."

MARY: "Mary. Mother of three."

TOM: "Tom. Astrophysicist."

KAITO: "Kaito. I'm a teacher."

SUSAN: "Susan. Head of neuroscience."

PERSON before Lucca: "...Managing a desalination plant."

LUCCA: "Lucca. I work for the Civil Protection Institute."

CLASS REP: "Speaking of which, we will let Lucca demonstrate for us the Institute's new invention to combat the plague."

LUCCA, on stage: "I'm sure you have heard of the new plague. 
It is the Newon Plague.
Plague carriers are things that look alien. 
We call then "Newon"s.
But, there's no need to panick.
As long as you destroy it before it touches you, it will be okay."

LUCCA, taking out a torch looking pistol: "This is a magnetic beam pistol.
The working principle is simple.
It is an electro-mechanical device.
Through the Institute's genius, they figured out that in order to destroy a Newon, a magnetic field will suffice.

To create a magnetic field, a LOOP OF WIRES is needed. 
Send electricity through the loop, and the loop creates a magnetic field.
It is that simple.
To enhance the magnetic field, we place metal cylinders around the loop.
These metal cylinders, become magnetized, adding to the magnetic field.

In summary, the magnetic field destroys the Newon, and electricity through a loop of wires creates a magnetic field.

We will soon mass produce these magnetic beam pistols and distribute them to the populace. 
We will keep you updated. 
Don't worry - the Institute looks out for all of us."

CLASS REP: "Thank you for that presentation, now..."

\ 

\ 

Outside, night.
Lucca is sitting on the stairs.
Kaito walks up to him, towering over him.

KAITO, smiling: "Why is Lucca sitting out here alone?"

LUCCA: "Kaito...
Mr Williams is ill, is he?"

KAITO: "Truth is, no one really knows where he is."

TOM: "What a shame."

EMMA: "He was such a lively person!"

SUSAN: "Serious at times."

KAITO: "For me to do well at my job, I'm in his overwhelming debt."

MARY: "It was so weird, when he left out of nowhere."

SUSAN: "Wasn't that... Just before our graduation?"

PERSON: "I wonder why..."

CLASS REP: "Hey! I have an idea. 
Why don't we have another makeshift graduation ceremony, so that Mr Williams can hand us our certificates himself?"

MARY: "Luc, you're from the Institute. 
You should be able to find him effortlessly."

TOM: "Great! The task is on you, Luc!"

Emma smiles.

\ 

\ 

Lucca walks through an apartment complex. 
He arrives at a door and knocks on it.
Mr Williams opens the door. 
He looks messed up, badly kept, and a very dreadful spirit.

LUCCA: "...Mr Williams!"

WILLIAMS: "What do you want?"

LUCCA: "Mr Williams, it's Luc from the Class of '78."

WILLIAMS: "I don't know what you're talking about."

LUCCA: "Mr Williams!"

WILLIAMS: "Go away. I have another guest coming soon."

As he says this, Nerezza stands at the doorway.

WILLIAMS: "Come on in."

Nerezza walks in as Mr Williams pushes Lucca out.
Nerezza gives Lucca a smirk.
Lucca is shut outside the door.

\ 

\ 

After a while, Nerezza comes out.

LUCCA, chasing after her: "What are you here for? How is Mr Williams?"

NEREZZA: "I am here to fulfill his wish.
He is fine."

LUCCA: "His wish?"

NEREZZA: "Mr Williams doesn't need to live anymore.
Which is fair enough.
I will provide him euthanasia."

LUCCA, shocked: "You what?"

NEREZZA: "In a week, he will no longer exist."

\ 

\ 

Meeting with Emma and Tom. 

LUCCA: "He doesn't recognise me.
I think he doesn't want to."

EMMA: "Does he not want to see us?"

LUCCA: "I'm sorry."

TOM: "Oh well. Life is often disappointing."

EMMA: "Well done, Luc. You did your best."

LUCCA, uncomfortable: "Mmm...."

MARY: "Can you deliver some messages for us at least?"

LUCCA: "I will see what I can do.
I think the more I try to reach him, the more he will hide away.
Unless..."

\ 

\ 

At Mr Williams' door.
Knocking can be heard.
Mr Williams doesn't respond.

LUCCA: "Civil Protection Institute.
I command you to open the door."

Mr Williams suddenly jumps up and runs to the door.

LUCCA: "It's me. I come from the Civil Protectioin Institute.
May I have a word with you?"

MR WILLIAM, shocked: "C... Come in."

Lucca slams a gyroscope onto the table.

LUCCA: "This is a gyroscope.
When you spin the disk in the centre, and place it on the stand on an angle...
The gravitational torque applied over the lowest point causes it to migrate to 90 degrees forward.
This constant action creates a rotation of the spinning axis.
That is the mechanics of precession."

MR WILLIAMS: "Your excellence, I don't..."

LUCCA: "End the pretense at once. Call me Luc. I command you to recognize me as your student."

MR WILLIAMS: "Ok... I'm sorry."

LUCCA: "The lesson of precession. 
That was the final lesson delivered to your dear students of the Class of 78.
Where did you go afterwards?"

MR WILLIAMS: "I had a promotion opportunity offered by the Institute. 
I came to this district, hoping to gain some prestige.
It didn't work out in the end, and nothing much happened for the next 20 years.."

LUCCA: "You could always have come back to us."

MR WILLIAMS: "I couldn't."

LUCCA: "Why?"

MR WILLIAMS: "The truth is... I was... tired, of teaching you guys.
I didn't want to anymore."

This makes Lucca tear up.

MR WILLIAMS: "I was excited when I got a chance to be promoted, for leading the Class of 78.
I was so excited that I didn't even want to greet you goodbye."

LUCCA: "You are pathetic."

MR WILLIAMS, shaking and burying his head: "That's the kind of person I am.
So I don't deserve any of you!
And I don't want to see you!"

He lays there for a few moments. 
Until suddenly, Emma's voice can be heard. 

VOICE: "It's fine, Mr Williams. 
This is Emma.
Are you well? 
I am now a full fledged computer at the government.
If you don't want to see us, we understand. 
If you don't want us to visit, we understand too.
It's all okay... it's all okay with us, Mr Williams."

MR WILLIAMS, tearing up: "Emma... Emma! That's you! Where is your voice coming from?"

Lucca is holding a voice recorder up.
His eyes cannot be seen behind his glasses.

TOM: "Hello Mr Williams, this is Tom! 
Naughty Tom.
I'm an astrophysicist! 
Job is tough, the government doesn't give much permission to do anything, but... It's really great!"

MR WILLIAMS, hot tears: "Tom! I remember! There was another called Albert..."

MARY: "Mr Williams, do you remember me? Mary! (Mr Williams: I do! I do...) 
I'm a mum now! I have three children with Tom, and I named one of them after you!"

MR WILLIAMS: "Oh... Oh Mary."

KAITO: "Mr Williams, thanks to you, I am now a successful teacher at the Glowdon Primary School."

MR WILLIAMS: "Kaito! He became a teacher? 
He was the smartest in class..."

MR WILLIAMS, looking to Lucca with teary eyes: "Is everyone well?"

LUCCA: "They are now all happy men and women. A lot are in important positions in society!
You lucky bastard. They really care for you, you know."

LUCCA, walking out: "They will be meeting together again at this place on Friday.
Do as you like!
But don't make the decision thinking what we think of you or what we deserve.
Do what YOU want to do, or I will make sure everyone remembers you as a loser.
So long!"

Mr Williams is left sitting alone. shook.

\ 

\ 

Friday, reunion.

CLASS REP: "Let's welcome our special guest!"

Mr Williams walks in accompanied by Emma.
The entire room ERUPTS in applause and cheer.

Mr Williams is stunned.
They bring him to the table and hand him a bouquet of flowers.

Mr Williams sees the people as children in his memories.
He bows down in deep gratitude and sheds a warm tear.

\ 

\ 

Unknown interval later.
Train station.
Lucca is walking down the stairs of the station.
He sees Nerezza. 

NEREZZA: "Member of the Institute."

LUCCA: "You..."

NEREZZA: "Looks like Mr Williams had other ideas.
You will keep him this time."

LUCCA: "..."

NEREZZA: "You may be able to save one person, but you can't save a civilisation.
Some illnesses are too deeply rooted, much, much deeper than the Newon Plague.
Something like, say, the AZTORIA SYNDROME. (Lucca is startled)
If you want me to be honest with you, you should know that...
In a few months, you will see an Aztoria that's a barren wasteland right where it stands."

She laughs hysterically as she walks up the stairs.

\end{document}
