\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{What Happened in Year 72}
\maketitle

Interior, night, Lucca's apartment.
Lucca picks up the phone. 

PHONE: "Thank the earth, you haven't changed your number!"

LUCCA: "...Tom!"

TOM: "Hah! You still remember me."

LUCCA: "Oh man what's, what's up dude?"

TOM: "Have you heard? 
There's a primary school reunion coming up.
Well, I guess that's my job, to tell you that. 
Haha!"

LUCCA: "I only joined you guys in highschool...
Can I still come?"

TOM: "Who cares!
You still know us for 6 years. 
Only reason we call it a primary reunion is because 20 years sounds a lot more like a cause for celebration than 14 years."

LUCCA: "Sweet, tell me the location and time, and I'll meet you all there."

\ 

\ 

Night, school reunion.

CLASS REP: "Good evening!

Reunions rarely had this much traction before the extinction.

It's clear that our beautiful times spent under the Aztorian education system had not faded from our memories.

It's especially an honour for our teachers to accompany us!

Mr Young!
Mrs Petrov!
Mr Sodhi!"

CLASSMATE MURMURING: "And Mr Willians? Where is he?"

CLASS REP: "Mr Williams cannot be found. Well then...
Class of 2578, let's introduce ourselves!"

PETER: "I'm Peter! I overlook the food delivery of District 21."

EMMA: "Emma. I work as a computer for the government."

MARY: "Mary. Mother of three."

TOM: "Tom. Astrophysicist."

KAITO: "Kaito. I'm a teacher."

SUSAN: "Susan. Head of neuroscience."

PERSON before Lucca: "...Managing a desalination plant."

LUCCA: "Lucca. I work for the Civil Protection Institute."

CLASS REP: "Speaking of which, we will let Lucca demonstrate for us the Institute's new invention to combat the plague."

LUCCA, on stage: "I'm sure you have heard of the new plague. 
It is called the Newon Plague.
Plague carriers are things that look alien. 
But, there's no need to panic.
As long as you destroy it before it touches you, it will be okay."

LUCCA, taking out a torch looking pistol: "This is a magnetic beam pistol.
It sends out a pulse of magnetic field so that you can target Newons at range.
The working principle is simple.
Through the neuroscientists' genius, they figured out that in order to destroy a Newon, a magnetic field will suffice.

To create a magnetic field, we use an electromagnet. 
Send electricity through the ring, and the ring creates a magnetic field.
To enhance the magnetic field, we place metal cylinders around the loop.
These metal cylinders, become magnetized, adding to the magnetic field.

We have begun mass production of these magnetic beam pistols and eventually they will be distributed to the populace.
We will keep you updated. 
Listen for the city wide broadcasts.
Don't worry - the Institute looks out for all of us."

CLASS REP: "Thank you for that presentation, now..."

\ 

\ 

Outside, night.
Susan is sitting on the stairs.
Kaito walks up to her, towering over her.

KAITO, smiling: "Why are you sitting out here alone?"

SUSAN: "Kaito...
Mr Williams is ill, is he?"

KAITO: "Truth is, no one really knows where he is."

TOM: "What a shame."

EMMA: "He was such a lively person!"

SUSAN: "Serious at times."

EMMA: "A bit dumb, though."

TOM: "But he always taught us to do the right things! 
Anf gave us tips on how to lead a happy life!"

KAITO: "For me to do well at my job, I'm in his overwhelming debt."

MARY: "It was such a shame when he left."

SUSAN: "Wasn't that... Just before our primary school graduation?"

PERSON: "I wonder why..."

The students look at one another with suspicious eyes.

CLASS REP: "Hey! I have an idea. 
Why don't we have another makeshift graduation ceremony, so that Mr Williams can hand us our certificates himself?"

MARY: "Luc, you're from the Institute. 
You should be able to find him effortlessly."

TOM: "Great! The task is on you, Luc!"

Kaito smiles.

Emma smiles.

\ 

\ 

Lucca walks through an apartment complex. 
He arrives at a door and knocks on it.
Mr Williams opens the door. 
He looks messed up, badly kept, and a very dreadful spirit.

LUCCA: "...Mr Williams!"

WILLIAMS: confused

LUCCA: "Mr Williams, I'm Luc from the Class of '78."

WILLIAMS: "Class of 78..."

LUCCA: "Sorry, class of 72, for primary school."

WILLIAMS: eyes turn wide, starts shaking.

WILLIAMS: "Murderer... murderer..."

LUCCA: "What?"

WILLIAMS: "Class of 72..."

WILLIAMS: "Murderer!"

Lucca is shut outside the door.

\ 

\ 

Meeting with class again. 

LUCCA: "And that's all he said."

KAITO: concerned.

LUCCA: "I think he was scared.
Was there a murder or something back when he was teaching?"

EMMA: "Well... Mr Smith..."

The people in the class are startled.

LUCCA: "Tell me more."

TOM: "It was our history teacher, Mr Smith.
He taught us for the first 3 years, and then he had to leave the school for 3 years.
He returned to us in our final year - 72."

LUCCA: "And he didn't make it till the end of the year did he."

SUSAN: "No..."

LUCCA: "Got it. Mr Smith, murdered in 2572. 
I will be able to find the rest of the details from the CPI database.
And who killed Mr Smith?"

The class is silent.

LUCCA: "Hello?"

TOM: "We never found out. The case was never solved."

LUCCA: "An UNSOLVED case? 
By the CIVIL PROTECTION INSTITUTE?"

SUSAN: "Well actually, officially, he was only missing.
He was never found."

KAITO: "Finding someone is a piece of cake by the CPI.
So either Mr Smith escaped all of civilisation, or he died and was disposed of."

LUCCA: "Ok. 
I say the following with caution."

LUCCA: "From Mr Williams' reaction, I have a strong feeling that he knows who the murderer is, and that the murderer...

is a member of the Class of 72."



The classmates are shocked.

TOM: "Hold your glasses, Luc, a primary student committing murder and getting away with it from the CPI. Do you realise how fucking dumb that is?"

LUCCA: "The Class of 72 and 78 is not exactly known for its mediocre students.
You are all outstanding and excellent people."

SUSAN, tugging on his clothes: "Come on, Luc... You're scaring me."

LUCCA: "What happened in the 3 years that Mr Smith was absent?"

MARY: "Mr Williams was our substitute teacher, teaching us history."

LUCCA: "That would explain why he is personally afraid... The previous history teacher died while teaching the class of 72."

SUSAN: "Luc..."

LUCCA: "If you want to ever see him again, we are going to solve this case.
I will take the short route."

LUCCA, opening his watch: "Agent Ethan."

ETHAN: "Hey."

LUCCA: "Bring a Lambda Detector to my location in the next 20 minutes. 
We are going to catch a lie."

ETHAN: "That's too little time!"

LUCCA: "Take the Aztoria Train. It's way faster."

LUCCA, thinking: No one is trying to leave. 
That's a... good sign?

\ 

\ 

They ask all the classmates if they killed Mr Smith.

"Did you kill, or cause the disappearance of Mr Smith?"

Afterwards, Lucca looks at the results with dread.

LUCCA: "No one... !"

LUCCA: "Epsilon Current signal from the brain of..."

LUCCA, looking at his classmates: "No... It can't be!"

Lucca leaves.

\ 

\ 

CPI database.

LUCCA: "Smith... 72..."

LUCCA: "Here!"

LUCCA: "Mr Smith. 35, unmarried... deceased parents."

LUCCA: "...whereabouts unknown.
Signs of struggle in classroom where he was last seen. 
Note by Ian: this is a false clue - Class of 72 testified that the class was having a fight among themselves.
Note by Ian: certain surveillance cameras destroyed in the school.
Mr Smith's DNA was found on them.

Note by Ian:
The body is literally nowhere to be found in all of Aztoria.

DECLASSIFIED ADDENDUM POST LAMBDA:
Possibly succumbed to the Newon Plague while swimming in the ocean."

LUCCA: "Director Ian... Did you consider the possibility that one of the students was a killer?"

\ 

\ 

Aloh.

LUCCA: "What do you reckon, Aloh? Where could you possibly hide a body in Aztoria?"

ALOH: "What you learn by being so old is that... Whatever a human says or writes down, you have to take it with a grain of salt.
No one knows 100\% what they're doing.
Even the Civil Protection Institute.

You said they checked everywhere in Aztoria?"

LUCCA: "Yes. It was Director Ian.
Or rather, agent Ian, back then."

ALOH: "I can think of a few places where they do not check, and will not even consider to check for another few hundred years. 
For example, pre-extinction contracts."

LUCCA: "Contracts...?"

ALOH: "You can think of a few places, can't you?"

LUCCA: ...

ALOH: "Consider, back in the 21st Century, before the fracturing of the Earth Federation, when the most powerful and wealthy had the means to preserve themselves and themselves only..."

\ 

\ 

Cryo chambers. 
Sunlight streams through an overgrown lab. 

Lucca walks through the chambers.

NARRATION: At one point in history, it became fashionable to put oneself in cryo sleep, to wake up in the far future. 
A 500 year long contract.

Temperature cold enough to slow bodily functions and decay, to a halt.

Of course, some did it simply to see their investments grow.

(Cryptocurrency is the way of the future!")

When they wake, what would they think of this future?
Hunger and want are eliminated.
Infrastructure is at an insane level.
Such an advanced society sees no value in their primitive investments.

These people sleep, on the backs of noble people who built their civilisation.
Engineers who designed the cryo chambers... scientists who researched human biology... people who built these with their hands, at the factories... None of them will get to see the future."

Lucca stops in front of one chamber that has been opened in the year 72.

LUCCA: "I see."

It is Mr Smith, with a trauma to the right side of his head.

\ 

\ 

School.

EMMA: "Ah... So good to be back."

TOM: "This was where I climbed onto the roof once and got in trouble."

EMMA: "Twice."

TOM: "This was where I stole a girl's pencil and chewed it up."

TOM: "And this was where-"

LUCCA: "Yeah ok Tom.
You're truly a wild spirit."

\ 

\ 

As they walk through the school, Lucca takes note of the cameras.

Classroom.

EMMA: "On the day Mr Smith arrived, we knew our time with Mr Williams was gonna end..."

Flashback. 

Mr Williams leaving the classroom, the students running up to him and hugging him.

WILLIAMS: "He's your rightful teacher. 
Far smarter than I could ever be.
He will send you through highschool."

EMMA, crying: "Mr Williams...

WILLIAMS: "Emma, you're fierce and clever. 
Even though I couldn't bring you the high level knowledge that Mr Smith would have, I hope you learned a few things about happiness and how to treat others."

WILLIAMS: "And Tom, no more pencil chewing!" 

WILLIAMS, standing up: "The last 3 years was an honour! 
You are all going to be building a beautiful Aztoria.
It's gonna be crazy cool!
Class of 72, full speed ahead towards a bright future!"

TOM: "Of course, being the careless person he was, he left all his stuff on his desk.
So he had to return to the school one more time to get it."

They now walk around the teacher's office.

TOM: "Hey! That's still his stuff.
We gotta hand it back to him when he comes to the reunion!"

\ 

LUCCA: "I've heard enough. I would like to speak to one of you in private."

"Susan."

\ 

\ 

At Mr Williams' door.
Knocking can be heard.
Mr Williams doesn't respond.

LUCCA: "Civil Protection Institute.
I command you to open the door."

Mr Williams suddenly jumps up and runs to the door.

LUCCA: "It's me. I come from the CPI.
May I have a word with you?"

MR WILLIAMS, shocked: "C... Come in."

LUCCA: "You can relax now. 
I have solved the murder case of year 72.
And I have found the body of Mr Smith.

There are two parts to the story. 
The first part - the killer."

WILLIAMS: terrified

LUCCA: "The person who killed Mr Smith... was you."

WILLIAMS: terrified

LUCCA: "Susan failed her lie detector test. 
She was involved in Mr Smith's demise."

\ 

Flashback.

End of the day. 

SMITH: "Susan. 
Could you please stay back after school?"

SUSAN: "...Okay."

\ 

Empty classroom, dusk.

SUSAN: "What do you need me for?"

SMITH, after closing the door: stares at her twistedly.

SUSAN: "Mr Smith?"

SMITH starts advancing towards her.
Susan starts crying.

Mr Williams stops outside the door and turns to look at it.

SMITH: "I broke all security cameras. 
You can't 

The door knocks.

Smith opens it. 

It was Mr Williams. 

WILLIAMS: "Susan. Leave the building."

She did.

The door closed behind her. 

\ 

\ 

WILLIAMS: "How... how did you know it wasn't Susan who-"

LUCCA: "As soon as there's a body, there's a case, and it's painfully obvious.

The trauma on his body is at the top of his head. 
Judging by the angle of attack, the culprit had a height just a bit above Mr Smith.

None of the students had enough height to reach there naturally."

WILLIAMS: remorseful

LUCCA: "...Afterwards, you brought him with you in your suitcase.
And the rest is history."

LUCCA: "You are a murderer, Mr Williams, and you can't see your students in the class of 72."

WILLIAMS: "In the heat of the moment, I...
That's the kind of person I am!
After teaching the students all those years, I couldn't solve a problem without violence!
I don't deserve any of the students!
And I don't want to see them!"

He lays there for a few moments. 

WILLIAMS: "...Are you here to arrest me now?"

LUCCA: "That brings me to the second part of the story."

LUCCA: "Mr Williams, do you really think you could escape the CPI alone?
You probably lived the last 20 years of your life in constant fear, not knowing how the investigation went, nor what happened to the students.

Mr Williams, your bright students knew this whole time!"

WILLIAMS: shocked

LUCCA: "At some point, they must've known something was wrong. 
And their decision was to help you! All of them!"

LUCCA: "I noticed the atmosphere was off during the reunion.
I felt a tinge of disconnect, as if I was Luc at second, and a CPI agent at first."

LUCCA: "Though you chemically cleaned all of the blood, and your DNA would be naturally found in that classroom anyway, you still left all the signs of struggle!"

\ 

flashback

EMMA: "Come on, Tom! Is that the best you can do!?"

TOM: "This punch is for Susan and Mr Williams! HYAAAAAAA-"

EMMA: "Well fuck you!"

Emma throws Tom to the side of the classroom, then strikes a table onto the ground.

Susan sits in the corner, shaking.

LUCCA, narrating: "Not only they helped cover your tracks, your students testified for you, turning the case into an impossible puzzle!"

Mr Williams begins crying.

LUCCA: "I'm sure Mr Smith has commited more crimes in the time he had to escape from your school."

WILLIAMS: "This whole time...?"

Suddenly, Emma's voice can be heard. 

VOICE: "It's fine, Mr Williams. 
This is Emma.
Are you well? 
I am now a full fledged computer at the government.
If you don't want to see us, we understand. 
If you don't want us to visit, we understand too.
It's all okay... it's all okay with us, Mr Williams."

MR WILLIAMS, tearing up: "Emma... Emma!"

Lucca is holding a voice recorder up.
His eyes cannot be seen behind his glasses.

TOM: "Helloooooo Mr Williams, this is Tom! 
Naughty Tom.
I'm an astrophysicist! 
Job is tough, the government doesn't give much permission to do anything, but... giving lectures is really great!"

MR WILLIAMS, hot tears: "Tom! I remember! There was another called Albert..."

MARY: "Mr Williams, do you remember me? Mary! (Mr Williams: I do! I do...) 
I'm a mum now! I have three children with Tom, and I named one of them after you!"

MR WILLIAMS: "Oh... Oh Mary."

KAITO: "Mr Williams, thanks to you, I am now a successful teacher at the Glowdon Primary School."

MR WILLIAMS: "Kaito! He became a teacher? 
He was the smartest in class..."

SUSAN: "I'm a neuroscientist, working for the happiness of humankind."

MR WILLIAMS: "Susan..."

MR WILLIAMS, looking to Lucca with teary eyes: "Is everyone well?"

LUCCA: "They are now all happy adults. A lot of them are in important positions in society!
Oh you lucky bastard... They really care for you, you know."

LUCCA, walking out: "They will be a meeting together again at this place on Friday.
Do as you like!
But don't make the decision thinking what they think of you or what they deserve.
Do what YOU want to do, or I will make sure everyone remembers you as a loser!
No! I will also arrest you for murder!
So long!"

Mr Williams is left sitting alone. shook.

\ 

\ 

Friday, reunion.

CLASS REP: "Let's welcome our special guest!"

Mr Williams walks in accompanied by Emma.
The entire room ERUPTS in applause and cheer.

Mr Williams is stunned.
They bring him to the table and hand him a bouquet of flowers.

Mr Williams sees the people as children in his memories.
He bows down in deep gratitude and sheds a warm tear.

\ 

\ 

Unknown interval later.
Train station.
Lucca is walking down the stairs of the station.
He sees Nerezza. 

NEREZZA: "Member of the Institute."

LUCCA: "You..."

NEREZZA: "So... Mr Williams, hey?"

LUCCA: "How do you know about him?"

NEREZZA: "I have many customers. 
And Mr Williams, one of them.
Well, used to be."

LUCCA: "I can only guess..."

NEREZZA: "You may be able to save one person, but you can't save a civilisation alone.
Some illnesses are too deeply rooted... Much, much deeper than the Newon Plague.
Something like, say, the AZTORIA SYNDROME. (Lucca is startled)
In a few months, you will see an Aztoria that's a barren wasteland right where it stands."

She laughs hysterically as she walks up the stairs.

\end{document}
