\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{The Synthesis Project}
\maketitle

Newon outbreak at the Aztorian University Neuroscience labs!
The Institute rushes over.

LUCCA, horrified: "Haven't the neuro labs stopped their research since Lambda's expose?"

RACHEL: "He did expose, but did you remember any action taken?
I think the Institute helped develop the magnetic beam pistol to combat the Newons, and afterwards, we all assumed no more research was done."

LUCCA: "...who is directing the research now then?"

\ 

Emergency quarantine team arrives.

OPERATOR A: "Agents! Help the scientists escape!
We are deploying emergency quarantine cover!"

They set up a magnetic field within which the Newons can't escape.
Agents help the scientists escape, destroying newons in the process.
Lucca runs into the labs.

\ 

Through the corridors, Lucca sees an opened gate.
He descends the stairs behind it.
He reaches the bottom floor. 
It is a wide open space in dark, with many human bodies lying around, with Susan sitting at the centre.
Susan is facing away from Lucca.

LUCCA: "Susan. And Lambda before you.
Chief engineer of the Plague."

SUSAN, turning around, dreadful eyes: "Hello Luc.
I knew you would find me."

LUCCA: "Susan, explain."

SUSAN: "The Synthesis Project is a failure. 
When the mass of Newons reach a critical mass - around 150 Newons, it breaks apart again.
We need a great attractor, a site of nucleation...
Only then, will we achieve Newon Synthesis."

LUCCA: "Merging Newons together... for what?
Susan... Just what the hell is a Newon?"

SUSAN: "Come with me."

\ 

They now walk through a series of rooms, with windows to peek inside.

SUSAN: "Ever since the 2nd Cognitive Revolution, we understood the material composition of consciousness.
Professor Lambda told us that consciousness are made of Information Currents, travelling through time."

They walk pass a room with a patient with their head plugged into a device.

SUSAN: "The human brain is electric.
When you apply a magnetic field to it, it ceases to operate normally."

SUSAN, picking up a strong magnet: "For example, when I pick up a really powerful lab-grade magnet and place it next to my head...
I-I-I-I k... k-k-k I k-ant."

SUSAN, placing the magnet down: "I couldn't speak normally."

SUSAN: "And that is why magnetic fields destroy Newons."

LUCCA: "Are you saying..."

SUSAN: "Newons are Currents, separated from the brain, trapped inside a boundary of space.
Newons are human consciousness, deformed and imprisoned!"

LUCCA: "That's why they appear black! 
Information cannot leave that boundary!"

\ 

LUCCA: "And the Newon Plague..."

SUSAN: "The real mechanics of the Plague involves the natural attraction of Newons towards one another.
Especially when someone is asleep...
A Newon is able to escape the host's brain, and draw out the Currents from another sleeping host's brain."

LUCCA: "And the Synthesis Project..."

SUSAN: "Well, that is...
that is the Civil Protection Institute's final answer to a question that really plagues humanity...
The Aztoria Syndrome."

\ 

\ 

Interior, Institute.

DIRECTOR KATZ: "Newon outbreak at the Neuroscience Labs."

DIRECTOR FREDA: "Trouble, trouble.
Even announcing the Plague is ok.
The Synthesis Project should be guarded the most securely."

DIRECTOR IAN: "First Director."

FIRST DIRECTOR: "We're almost there.
It's just an outbreak that we will contain efficiently.
Don't panic, act rationally, and we will get there.
The balance of history rests on our shoulders.
We won't screw it up."

\ 

\ 

LUCCA: "You mean to say, that the Institute is killing us all!"

SUSAN: "Preserving us all, Luc. 
Preserving all of human consciousness within a Newon boundary."

LUCCA: "What is the Aztoria Syndrome?
No more opacity!
Tell me everything!"

SUSAN: "Because it's you, Luc, I will tell you.
The Aztoria Syndrome is Precession."

LUCCA: "Precession? Of what?"

They return to the pile of bodies. 
Susan walks towards a disconnected cable.
A machine rumbles.
The Newon mass begin merging again, creating an unsettling scream and a grotesque shape.
Lucca immediately shoots his magnetic beam pistol at it.

SUSAN: "There is no use. 
It is no longer a single Newon. 
The electric current in your magnetic beam pistol is not nearly enough."

The Newon mass begin breaking down again.

SUSAN: "But, synthesis still won't succeed.
There is no attractor to bind them together.
Eventually, they break down."

LUCCA: "Susan, may the universal contempt of humanity fall upon you!"

SUSAN, crying: "Your words hurt as always, Luc..."

\ 

Saying this, Susan falls backwards into Lucca's arms.

LUCCA: "Susan!"

The two enter a bizarre space of the mind.

\ 

SUSAN, flying, eyes closed: "Is it wrong to do things because I'm told?"

LUCCA: "It isn't helpful.
You should first consider what it means for you personally."

SUSAN: "Then, what about Luc? 
Why does Luc work for the Institute?"

LUCCA: "As the Institute slogan goes, I work for the happiness of humankind."

SUSAN: "Institute... Humans. And when the two conflict?"

LUCCA: "Humans take precedence."

SUSAN: "Amazing... I think... I understand you more."


\ 

Back in reality, Lucca is still holding Susan.

SUSAN, eyes closed: "I'm so tired.
It must be the plague...
Luc, you leave here too.
Why aren't you sleepy?"

LUCCA: "No. You come with us. 
You have a lot of questions to answer."

SUSAN: "Ah... Luc, I can see Currents..."

She no longer moves.
Lucca sheds a single tear.
The frame pans over to reveal a deformed Susan in Newon form standing in the background.

LUCCA: "Susan!"

The Newon runs away.

[NARRATION: Susan will wander the earth as a Newon.]

\ 

\ 

At night, Lucca lies in bed.
He turns over.

LUCCA: "I can't sleep."


\end{document}


%LUCCA: "May the universal contempt of humanity fall upon you."
%SUSAN: "You words hurt as always, Luc."

%susan wanders aztoria as a newon.
%nerezza