\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Interpretations of a Dream}
\maketitle

Dusk. City Ray Nursing Home.
Lucca walks into a clean neighbourhood, and an old home within it.
Receptionists see the badge on his shoulders, stand up and bow. 

LUCCA: "I'm here to visit Mrs Gallo."

RECEPTIONIST: "That way."

LUCCA: "Thank you."

As he walks, the nurses look at him with disdain.

\ 

\ 

He arrives at the room.
Mrs Gallo is sitting in her bed.
She wears glasses, has freckles, and looks old.
She speaks very slowly.

GALLO: "Agent of the Institute. 
Thank you so much for answering my problems and visiting me."

LUCCA: "Mrs Gallo, what's troubling you?"

GALLO: "I have been having these dreams.
They make me very confused."

LUCCA, taking a note: "Tell me about these dreams."

GALLO: "I see a young woman wearing a black coat.
Very pretty and strikingly sharp in her gaze."

Lucca, taken aback.

GALLO: "I think her name is Nerezza."

LUCCA: "Have you met her in person before?"

GALLO: "No, I haven't."

LUCCA: "Well Mrs Gallo, I can tell you what I know.
Nerezza is a real person walking around the city of Aztoria.
She is a doctor."

GALLO: "A doctor! 
So young..."

LUCCA: "If you do see her, can you PLEASE immediately call the Institute?
Will you remember to do that?"

GALLO: "Ok."

LUCCA: "Sorry, there's not much else I can help with."

GALLO, kind smile: "Ok. That's all I guess.
Sorry for troubling you."

\ 

\ 

% 2nd visit
2nd visit.
Interior, Mrs Gallo's room.
This time Lucca is preparing some fruits at the sink.

GALLO: "Agent of the Institute, thank you so much for visiting me."

LUCCA, handing her the plate of fruits: "Don't worry about it.
What's the problem, Mrs Gallo?"

GALLO, chomping on the fruits: "I have been having these dreams. 
They make me very confused."

LUCCA: "Tell me about these dreams."

GALLO: "I see a man wearing a beige coat and glasses."

LUCCA: "That's an interesting thing to dream about."

GALLO, chomping on some more fruits: "Mm! I wonder.
Wow, it sure is nice to have the Institute visit me.
Things have been such a drag lately."

\ 

\ 

% 3rd visit
3rd visit.

GALLO, uncomfortable, crying: "Agent... Agent..."

Lucca enters frame.

LUCCA: "Mrs Gallo.
I'm here."

GALLO, stopped crying: "Thank the earth.
I want to go to my armchair.
Help me please."

LUCCA: "Of course."

Lucca holds her hand, waits for her to slowly drop both legs out of the blanket down onto the floor, into her slippers.
She then extends one arm to hold onto Lucca's forearm, and slowly slides off the bed.
She is now standing, facing Lucca, holding onto both of his extended forearms.
The two are very close, and make tiny steps in sync, slowly moving towards the arm chair.
She almost trips once.

GALLO: "Oh!"

They make it to the armchair and she sits down.
Lucca sits down next to her.
She asks him to bring the photo album. 
He does.
They start flipping through it.

The young versions of Mrs Gallo are barely visible.
There is a boy in the photos. 

GALLO: "Mmmm... don't remember any of this.
This looks like a graduation...
Here was my graduation and acceptance into the Neuroscience labs of Aztoria University.
Oh i know him! Professor Lambda! Who could forget? He was a fierce PhD Tutor!
And here it looks like...
I had a son."

The son looks like Lucca.
The pictures afterwards show her bedridden, but happy and with Lucca next to her.
It seems she had been sick for a long time, decades.
The remaining pictures are her alone on the bed, taken with a few nurses on her birthdays.
After the final page, there was a note.

NOTE: It's been hard to form thoughts recently. 
And I'm scared of forgetting this, so I am writing it down here.
Please don't lose this treasure! - I want to die!
My son has abandoned me.
He can't stand me anymore, so he sent me to this nursing home!
Don't forget!

GALLO: "Huh?"

Lucca is tremendously disturbed.
He starts shaking, and looking distraught.

GALLO: "Did I write this?"

Lucca cries.
The door behind them opens. 
Nerezza stands in the doorway.
Lucca is horrified.
She walks towards Mrs Gallo, grinning towards Lucca.

NEREZZA: "Hello Mrs Gallo. 
As promised last week, I've come at the agreed upon time."

GALLO: "Oh, it's you.
The woman in my dreams."

NEREZZA: "Not dreams, Mrs Gallo.
But memories.
I visited only last week.
I see you are finding things difficult."

Gallo looks at the note she wrote and up at Nerezza.
Gallo smiles.

GALLO: "Young doctor Nerezza."

NEREZZA: "Shall we go ahead?"

GALLO: "Yeah. 
Thank you, agent of the Institute.
There was no problem at all.
I wanted to see her."

LUCCA, affirming during sobs: "mm... Mm!..."

GALLO, to NEREZZA: "What's wrong with him?"

NEREZZA, wide grin: "Institute agent syndrome.
Maybe because of loneliness.
They can delude themselves into being too attached to the ones they help."

GALLO: "That kind of makes sense."

NEREZZA: "Mrs Gallo, welcome your well deserved rest."

GALLO, happily: "Mm!"

\ 

\ 

Lucca walks dreadfully out of the place.
The nurses look at him with disdain.
He doesn't look at them.

\ 

\ 

Exterior.

[MUM, narration: Oh, Luc, one more thing.
When you need to find me - when your life depended on it - meet me at our rendezvous point.

LUC, narration: Rendezvous point?

MUM, narration: It's a secret between us two. 
When the time comes, meet me at the centre of the Aztorian City Loop.
There is a patch of grass, where Aztoria began.
You will surely find me there.]

As he thinks this, he walks towards that patch of grass.
There is no one there.
Lucca stands alone in a vast empty space at the centre of the City Loop.

\end{document}

%rendezvous point

%mum comic