\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Mystery in the Aztorian Sky}
\maketitle

Balcony, night.
Alex is stargazing through a telescope.

\ 

[NARRATION: "Alex likes to stargaze.

Nothing compares with the beauty, challenge, and mystery of space.

Darkness and lights of infinite depth.

Convolutions between space and time, uniting as one.

On some level, he must have expected that that's where humanity's future lies.

Pursuing truth, beauty, and knowledge.

Alex dreams that one day, he may go up there himself.

Becoming one with the ocean of stars."]

\ 

Alex works at a construction site.
[NARRATION: "During the day, Alex works like any other.
Be careful Alex, falling asleep is very dangerous when working in such places!"]

COWORKER A: "Careful!"

The coworker catches Alex, but his hammer falls down.

COWORKER A, to people below: "HAMMER!"

\ 

Lunch break. 
Alex clutching his head.

COWORKER A: "Alex, if this happens again, we're gonna have to get you fired for YOUR safety."

\ 

\ 

Riding bike on way home.
Alex passes a patch of grass, parks his bike and observes something in the distance. 

BOY: "Hello!
You dropped something."

The boy hands him binoculars.

ALEX: "Thanks."

\ 

Alex pushes his bike while walking, with the boy next to him. 

BOY: "You look sleepy. 
What's wrong with ya?"

ALEX explains: "Have you noticed how bright the city lights are at night?
I have to stargaze at midnight, when the lights are lower.
That's why i'm sleepy all day.
Does that make sense?"

BOY: "Mmhm. Sounds fun.
Alright I have to go now. See ya!"

ALEX: "See ya."

\ 

\ 

Night, Alex's balcony.
He notices something wrong.
He runs back inside, grabs an image he took in the past, of the same patch of sky, and compares it against the current sky. 

ALEX: "How did I not see this yesterday!
A star, a star at the edge of a constellation, it's gone!"

ALEX, running out of his apartment: "I have to let someone know!"

ALEX, banging on a door: "WAKE UP! WAKE UP!"

WORKER A, opening the door, looking big and scary: "STOP IT YOU LUNATIC!"

ALEX: "WHAAAAA it's a monster!"

WORKER A: "No, idiot.
Whatsh the matter now?"

ALEX: "A star disappeared from the sky!"

WORKER A: "Ah yer crazy, get outta here!
You musta been dreaming."

\ 

Interior, Alex's bedroom.
ALEX: "...Maybe I should call the Institute."

\ 

\ 

Interior, Institute. 
An agent is sleeping on the control panel.
The phone rings, waking him up.

AGENT A: "Hello. Private citizen? Alright, put him through."

PHONE: inaudible.

AGENT A: "Yes, yes, this is the Civil Protection Institute."

PHONE: inaudible. 

AGENT A: "What? A star disappeared?
(grabbing a pen and paper)
Could you provide an exact coordinate?
Yes. Yes."

ALMA, walking in: "What's the problem?"

AGENT A: "An amateur astronomer. He said he saw a star disappear."

RACHEL, leaning against a wall: "Those amateurs are always seeing things."

LUCCA, holding a phone: "The observation towers report no anomaly. 
The star is still there."

RACHEL: "Told ya."

LUCCA: "Maybe it was a passing asteroid?"

ALMA: "Blocking the light from the star. Possibly. 
Check the observatories."

\ 

Rachel: "Hello? State Observatory? Civil Protection Institute speaking.
...No asteroid?"

AGENT A: "Hello? Cyan Hills Observatory? This is the Civil Protection Institute. 
...So no asteroid or anything like that?"

LUCCA: "Hello, Aztoria University Observatory? Can I get professor Tom Misko?"

\ 

RACHEL: "No results."

AGENT A: "I guess that's it. 
A false alarm."

\ 

\ 

Exterior, at a park. 
Tom and Lucca observe the night sky.

TOM: "The stars seem brighter than before."

LUCCA: "Because the city lights are low."

TOM, smiling: "Yeah, romantic, isn't it."

TOM, with binoculars: "Hmm. Nothing wrong with the star, that's for sure."

LUCCA: "What do you think it could have been?"

TOM: "There are many things in space that can obstruct light from a distant star. 
But if it is something in space, the observatories can pick up on it.
In other words, I have no idea."

TOM: "Well. It's time for me to head home.
I'm getting sleepy."

LUCCA, Nerezza standing in the background in a flash: "I don't feel sleepy at all."

TOM: "I too would have a hard time sleeping if there's a mystery going on.
But you have to learn to sleep.
My career depends on it, heh."

\ 

\ 





\end{document}