\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{The District is Westward}
\maketitle

In Aloh's dining space, Lucca is drinking something.
Emma is singing in the background.

LUCCA's thought: "The Institute is killing us all.
A coming Synthesis Catastrophe.
On the other end, a coming revolution against the state authority.
Synthesis must be prevented.
Revolution must happen.
District 47. 
A district that disappeared from history 30 years ago.
The final district to visit."

\ 

\ 

Lucca drives along the great continental road with a map in his lap.
After half a day, he drives past a farmer.
He stops at the side of the road and winds down the window.

LUCCA: "Excuse me, I'm looking for District 47. 
Am I going the right way?"

FARMER: "Yep. Westward."

\ 

\ 

Lucca arrives at the empty district.
Food delivery trucks have long stopped coming here.
Colossal concrete buildings still stand.
Just like the coastal structures, no window, no entrance.
He walks through the empty streets. 
Old Aztorian banners say "For the happiness of all humankind."

Lucca tries to get some extra fuel for his car.
As he walks up to the other cars, they crumble. 

Empty apartment buildings loom above. 
A sound suddenly reverberates over the street. 
It came from one of the apartments.
Lucca investigates.

Lucca arrives at the apartment.
The doorknob falls off as he touches it.
He gently pushes open the door.
Inside is a *young* artist, frantically gathering his fallen over bucket of paint brushes. 

\ 
 
LUCCA: "...hello?"

MR ARTIST: "Hey man, what's goin down?
Haven't seen someone in ages."

LUCCA: "Hi... I'm from the Civil Protection Institute."

MR ARTIST: "The Institute? 
They still care about stuff around here?"

LUCCA: "I... I don't think so. Mr..."

MR ARTIST: "Artist."

LUCCA: "`Mr Artist?'"

MR ARTIST: "Well, yknow. 
I don't really remember my name. So I decided I'll be called Mr Artist.
Cus yknow. I do the... (gestures around his canvas) art thing."

LUCCA: "Um. Mr Artist. Are you aware that your entire district is empty?"

MR ARTIST: "Oh it's empty is it."

LUCCA: "Been that way for 30 years, Mr Artist.
The auto-delivery trucks have been non-operational. 
Where have you been getting your food?"

MR ARTIST: "Food... Yeah. A human needs food to survive, doesn't it.
Look, all this talk about un-necessary details..."

LUCCA: "FOOD is not an un-necessary detail!"

MR ARTIST: "Maybe I'm trying to work something out myself, young man. 
Maybe the Mr Artist you're seeing right now isn't an accurate representation of... Mr Artist."

MR Artist: "I’m tired of talking now. 
I’d like some uninterrupted time painting if you don’t mind. 
Thanks for visiting though. 
It was a pleasant surprise."

The Artist turns around and starts painting. 
The painting is a woman wearing white clothes. 
His movement is mechanical and programmatic. 
He will not respond to anything anymore. 
Lucca walks around his apartment. 
A giant window shows a view of the street, and a window on the building opposite this one, where a woman with white clothes stands. 
Lucca jolts and runs up to the window. 
The woman steps back into the shadow. 

\ 

\ 

Interior, Institute.

AGENT: "First Director, you have a visitor."

FIRST DIRECTOR (as always, we can only see their back): "Come in."

It is Aloh.
The agent exits. The room locks.

ALOH: "Hello, First Director. 
I'm Aloh, volunteered caretaker of a communal dining area.
It's an honour to speak to you face to face."

FIRST DIRECTOR: "Sit down, Aloh. 
Pleased to meet you."

ALOH: "I thought only the Directors are allowed to see you in person.
I'm glad you seem as charismatic and upright as you do."

FIRST DIRECTOR: "This is a one-in-a-million exception.
You said that you wanted to `discuss the nature of Precession'. 
There is no chance I'm not speaking to you after I hear that."

ALOH: "Alright, let's get right to it then. 
First Director. 
Precession is *wrong*."

\ 

\ 

Lucca now walks on the streets again.
He turns a corner.
An old woman with a headscarf sits on the curb smoking.
Her face lights up.

[NARRATION: A cigarette. 
One of those cultural excrements that should have gone extinct in history.
Here in District 47, an old battleground for the future of Aztoria, it appears again.
The people versus the Institute. 
It's clear who won.]

OLD WOMAN, slowly: "A young new face! Where are you from?"

LUCCA: "The Civil Protection Institute. I'm here to investigate the disappearance of this district's people."

OLD WOMAN, nostalgic gaze into air: "The Institute...
`For the happiness of all humankind.'"

LUCCA: "What happened to this District?
Where are all the people?"

OLD WOMAN: "Synthesis.
They are at the diner at the edge of the world."

LUCCA: "They're still alive? Where is this diner?"

OLD WOMAN: "Westward."

As they converse, the woman in white clothes reaches into Lucca's pocket, stealing his car keys. 
This startles Lucca.
When he turns around, the woman is already running away, giggling.
When Lucca turns back to the old woman, she is no longer there.

\ 

\ 







\end{document}