\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{The Spaceport Revolt}
\maketitle



[To be fleshed out.]

Aztoria is in revolt. 
Construction workers at a secret space port refuse to obey the Institute's bureaucrats to cancel their project.
This conflict grows huge, with many people coming outdoors and standing beside the space port.
Lucca reads his prepared notes to the rest of the city from a speaker from inside the Institute.
University professors gather around.
Computer workers from the Government that was disbanded by the Institute a while ago, arrive at the Institute to take hold, guarding the room Lucca is in so he can finish the announcement.
The Directors of the Institute accept capture.
Tom, working from the observatory, reports to Lucca that the giant object is still approaching from the Northern Hemisphere. 

\ 

\ 

Exterior, grand, retired spaceport.
A working man with hat and shovel stand in front of one of the abandoned spaceports, together with hundreds of other workers. 
Colossal demolition vehicles stand in the background.
Director Robert stands in front of the scene, leading a team of Institute agents. 
It is a strike.

DIRECTOR ROBERT: "What's the matter, dear citizens."

WORKER: "We won't demolish this spaceport.
We will wait for the day we can return it to its former glory."

DIRECTOR ROBERT: "The city needs the materials from this spaceport elsewhere. 
I would show you the equations of SED, if you could even understand it."

WORKER: "We've been asked to demolish these one after another. 
This space port represents humanity's final stand against the vast space."

DIRECTOR ROBERT: "Leave the worrying for humanity to us. 
Your job is to live, eat, and not start a scene."

WORKER: "We've waited long enough.
No more destruction! 
We ask for fulfilment of our promise!"

DIRECTOR ROBERT: "










\end{document}