\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{World's End}
\maketitle


Recap: Aztoria is in revolt. 
Construction workers at a secret space port refuse to obey the Institute's bureaucrats to cancel their project.
This conflict grows huge, with many people coming outdoors and standing beside the space port.
Lucca reads his prepared notes to the rest of the city from a speaker from inside the Institute.
University professors gather around.
Computer workers from the Government that was disbanded by the Institute a while ago, arrive at the Institute to take hold, guarding the room Lucca is in so he can finish the announcement.
The Directors of the Institute accept capture.
Tom, working from the observatory, reports to Lucca that the giant object is still approaching from the Northern Hemisphere. 

\ 

\ 

Interior, Civil Protection Institute, broadcast room. 

\ 

LUCCA: "Citizens! There is an emergency! 
Impending disaster from the Northern hemisphere!
It is a massive collection of those plague carriers.
By the time they arrive, we will all be absorbed into that thing!
Do NOT hesistate!
Make your way away from the city if possible!
We have to figure something out on our end.
I sincerely hope to see you all in the future."

\ 

He walks outside the room greeting Emma. 

\ 

EMMA: "What happened!?
Wasn't the Attractor destroyed?"

LUCCA, with dread: "There must...
There must be another Attractor somewhere in this city."

EMMA, horrified: "What? What!? What are we gonna do?"

COMPUTER A: "Find the Attractor, and destroy them."

EMMA: "There is no tiiime! We're done for!"

\ 

Lucca furrows brows intensely while looking down. 
He is tremendously disturbed.

\ 

EMMA, looking at a Director with disdain: "Oh, you! 
Of course you had other Attractors around.
You play with humanity like a toy!"

DIRECTOR ROBERT: "There was only one other Attractor. 
But don't worry about finding her. 
We don't even know where she is."

\ 

Lucca immediately runs outside to an unknown destination.

\ 

EMMA: "Luc!"

\ 

\ 

Nerezza is standing in a grass field.
Lucca arrives. 

\ 

NEREZZA: "Hello, agent."

LUCCA, catching a breath: "Mum."

NEREZZA: "Thank you for coming here. 
I was hoping you find me."

LUCCA: "Our `rendezvous point'.
Space coordinates: at the centre of the City Loop. 
Time coordinate: now."

NEREZZA, with nostalgia: "Dead centre inside the City Loop...
Luc, we're now at where it all began."

NEREZZA: "I saw your revolution. 
I'm really proud of you.
But your struggles are only the backdrop to this one single Project that must be completed."

LUCCA: "Mum, you abandoned your body all those years ago, to become the Great Attractor.
You've worked for the Institute this whole time!"

NEREZZA: "And so have you."

LUCCA: "But you're going to turn against them right?
That's the reason we're meeting here.
You will help stop the Synthesis."

NEREZZA only smiles.

NEREZZA: "What makes you say that?
If I wanted to stop the Synthesis, I would have shot myself with a magnetic beam pistol right at the beginning.
The truth is, I volunteered for this position.
To be the Great Attractor.
I made a commitment to the Institute.
The world must end this once."

LUCCA: "W..."

NEREZZA: "So what did you think you were gonna do?
Kill me, and abandon me again, 
l i k e\ \ \ y o u\ \ \ d i d\ \ \ l a s t\ \ \ t i m e ?"

\ 

Lucca collapses on the ground. 
Nerezza laughs hysterically.

\ 

\ 

Interior, Institute.

\ 

DIRECTOR ROBERT, tearing up: "The Synthesis Project will finally be complete.
I only saw this day in dreams.
First Director too, he will be without burden."

EMMA: "Shut up! Luc is going to find the Attractor and destroy it.
Your project will fail."

DIRECTOR ROBERT: "Whatever you say, miss."

EMMA: "Let me ask you one more thing."

DIRECTOR ROBERT: "Go ahead."

EMMA: "What did you do with my past?
I clearly remember a different life, married and in work.
Do you do this to many people?
And why?"

DIRECTOR ROBERT: "It is simply this - a delusion.
A sign of insanity.
And we've got notes on this - it's not uncommon among patients of the Plague.
Delusions and false realities.
Memories from an imaginary life.
You are mentally insane.
We don't care enough about individual actors enough to control you to that extent, we have no interest in your personal life."

\ 

Emma cries as she hears this. 
She is in anguish.
A fellow computer reaches over to comfort her.

\ 

\ 

Exterior, grass field at centre of City Loop.

NEREZZA: "Really, thank you for coming here.
I didn't need you to come, because soon we will all unite in a dream. 
But I wanted to formally see you one more time before the Synthesis.
Think of it like a punishment, disgraceful son."

\ 

Lucca curls up.
Nerezza walks over and takes the magnetic beam pistol out of his pocket.
Lucca doesn't resist.

\ 

NEREZZA, grinning: "I win."

\ 

Lucca is still curled up.

\ 

NEREZZA, arms raised: "Directors, as promised, I've committed to and will complete your Synthesis.
In exchange, you will not create another Attractor, and I get to choose the location.
Right here at my rendezvous point with Lucca, coinciding with what may be the eternal centre of humankind!"

\end{document}