\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{For the Happiness of All Humankind}
\maketitle

At home, Emma is fumbling with scale models.

\ 

\ 

Interior, Aloh's dining space.

EMMA: "Hey, Luc."

LUCCA: "Mm."

EMMA: "What do you think Aloh is up to during the day?"

LUCCA: "No clue. Why?"

EMMA: "I'm just curious."

LUCCA: "He probably has some secondary job during the day.
Or rather, managing this communal dining space is his secondary job."

EMMA, excited, secretive: "Let's follow him!"

LUCCA: "No."

EMMA: "You're so boring.
Humanity is in threat by Precession, the Institute's on our throat, and you won't even allow us to have some fun."

LUCCA: "Go knock yourself out. 
I'm not following.
You reap the consequences that you sow."

EMMA: "Oh come oooon, Aloh's our friend!
He will be pleased to see us.
Big old bubbly Aloh."

Emma puts her hands to her face, her fingers emulating round glasses.
Lucca shows a disgruntled glare.

\ 

\ 

Following montage ensues.

EMMA: "So what do you like to do in your free time?"

LUCCA: "Walk."

EMMA: "Just walking?"

LUCCA: "I like to wander the city.
What do you like to do?"

EMMA: "Er..."

Emma thinks about playing with her figurines and decides not to answer.

EMMA: "Doesn't walking get boring after a while?"

LUCCA: "You'd be surprised.
I promise, I'm not trying to make it seem more interesting than it is.
There are little mysteries hiding all around the city.
For example, take a look at those tall blocks."

Emma looks.

LUCCA: "Notice anything?"

EMMA: "Yeah. My neck's starting to hurt."

LUCCA: "There are no windows, no doors, just pure concrete.
What could these colossal buildings be used for?"

EMMA: "Concrete reserve?"

LUCCA: "There are more efficient ways to store them. And look, they all look really, really old."

EMMA: "Older than Aloh?"

LUCCA: "Probably!"

Another following montage.

LUCCA: "Another thing about this city.
There're just shelters, everywhere."

EMMA: "I didn't get the sense."

LUCCA: "I swear to Earth, just wander off track for a while.
But that's an adventure for another day."

EMMA: "Wow, so you really just explore the city huh."

LUCCA: "You should try it.
Go knock yourself out.
I can't hang around you every day."

\ 

\ 

Aloh meets a woman in black - it is Nerezza.
This makes Lucca shocked and absolutely absorbed.
He can't quite make out what they are talking about.
While Lucca is looking, Nerezza seems to look back and smirk.
Lucca imemdiately retreats into the shadow.
Emma is confused.
Nerezza walks away.

\ 

\ 

Another following montage.

\ 

\ 

They arrive at an open field - a flower-grown battlefield.
Aloh unpacks the bag he carries, and takes out a trumpet. 
He begins playing a familiar tune.

EMMA: "Ah! That is the Earth Federation Anthem!"

Aloh plays.

[NARRATION: There exist a few places like this in Aztoria. 
Battlegrounds of the old World War 3. 
400 years ago, when the American Continental Empire invaded Oceania, the Eurasian Continental Forces of the Earth Federation descended from the Northern Hemisphere to assist Oceania, fighting a fierce battle for the future of humankind.

The army had bands, musicians who laughed and played with the rest of the soldiers, keeping them company, a reminder of their humanity.]

ALOH, in memory: 
"Stand up! All people of the earth!
Stand up! You prisoners of war!
Machines! Have given us abundance,
now let us make them work for good!

The old world, crumbles into nothing;
all people, arise! Arise!
And then... the vanity of empires,
makes way for humankind!

This is the final struggle!
Solidarity till tomorrow!
The Earth, Federation!
Unites, the human race!

This is the final struggle!
Solidarity till tomorrow!
The Earth, Federation!
Unites, the human race!

There never ever was a saviour,
nor do we rely on kings and priests.
Gotta create a happiness for humankind,
relying on ourselves!

No more heart to kill each other,
century bells ring loud and clear!
The earth is ready for eruption!
For a reborn humankind!

This is the final struggle!
Solidarity till tomorrow!
The Earth, Federation!
Unites, the human race!

This is the final struggle!
Solidarity till tomorrow!
The Earth, Federation!
Unites, the human race!"

After playing, Aloh begins crying.

ALOH, looking up: "They fought for the future of humankind.
Old comrades are gone.
Centuries of time down the drain.
All is right with the world.
But... this trumpet has no more use either."

EMMA, smiling: "Aloh's trumpet exists to bring joy to humankind."

End.

\end{document}