\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{The Human Archives}
\maketitle

Ocean spaceport.
Construction workers look at it.
Some begin the process of rebuilding.

\ 

Interior, Institute.

[NARRATION: Director Ian, SED specialist.]

DIRECTOR IAN: "Secret construction projects have started at the Ocean Spaceport against our directions. 
I warn that this poses a real threat to the stability of humankind's future.
Should we stop it, First Director?"

FIRST DIRECTOR: "Director KATZ will go."

\ 

\ 

Interior, Aloh's dining space.
Aloh is playing the trumpet.
Emma and Lucca are pleased.

EMMA: "Where're you going?"

LUCCA: "To the Institue.
Members have exclusive access to the Institute's library.
I think there must be some books in there that shed light on human history."

EMMA: "ooh! I wanna come! I wanna come too! Can I pleaaaaase come?"

LUCCA: "Alright."

\ 

\ 

Ocean spaceport.

DIRECTOR KATZ: "Hello, citizens."

The people continue to work.

DIRECTOR KATZ, through megaphone: "Get back into the vehicles.
We need to demolish this older part of the district."

The people come down the spaceport and form a line.
It is a strike.

WORKER A: "We don't want to demolish it! It was perfectly fine!
Instead, we want to rebuild the spaceport!"

\ 

\ 

Lucca and Emma are driving.

EMMA: "Where are we going? This isn't the Institute."

LUCCA: "We're making a stop at the Factory Array.
Gonna pick up a uniform, overdue for me.
You are going to wear it."

EMMA: "Ohhh... So I'm gonna pretend..."

LUCCA: "I did say the library was exclusive."

They make a turn and arrive at the powerful Factory Array.

\ 

\ 

DIRECTOR KATZ: "They have formed a strike.
There are scientists from the Aztoria University as well."

DIRECTOR FREDA: "Ugh! What ungrateful people! 
We work tirelessly for the balance of history, and all they know is to demand for more things to go their way!
It's like they don't know who created this city, who fed them and maintained peace, who brought them unprecedented advancements this whole time!"

DIRECTOR KATZ: "We can use a Newon bomb and get rid of that district."

FIRST DIRECTOR: "No. You are insane.
Give them concessions."

\ 

\ 

Emma and Lucca are walking towards the Institute library.
The library is called the "Human Archives".
It stands solemnly above them.

EMMA, holding the uniform: "It looks so clean."

Emma turns it over and notices the symbol on the shoulders.

EMMA: "Gyroscope. It stands for Precession, doesn't it."

LUCCA: "Put it on."

The jacket is too big for her.
They walk through the gates of the library.
An institute agent walks by and notices Emma.

AGENT: "Hello there, new face. Which branch are you from?"

EMMA, sweating profusely: "Eheheh..."

LUCCA: "She's from the SED research branch."

AGENT: "Oh! You must be intimate with the equations then!"

EMMA: "Oh yes. 
The multi-linear transforms and the Jacobian tensors that bring us from the parameter space to the material-outcome space...
They are a pain to hand write."

Agent smiles and walks on.

EMMA: "Phew, that was a close one."

\ 

\ 

Ocean spaceport.

DIRECTOR KATZ: "You have my word.
After we demolish the district, we will consider rebuilding the Ocean Spaceport."

WORKER B: "Really?"

DIRECTOR KATZ: "Yes. 
I will also give each one of you direct access to the Factory Array requests for the next month. 
Now go back to work."

The crowd reluctantly disperses.

\ 

\ 

Interior, Human Archives.
Emma looks at the colossal book cases in awe.
She is still sweating profusely.

LUCCA: "...look, you can take it off now. 
You don't look very comfortable."

EMMA: "Ehehe..."

There is a huge Gyroscope, which Emma climbs on top of.

LUCCA: "This archive contains the sum total of human knowledge. 
There is a copy of it in the Aztoria Unviersity too.
Except that one is a lot less... historical."

EMMA: "Whaaaaaaaa!"

Emma is carrying a lot of books on her head, sitting on top of the gyroscope. The gyroscope tilts.

EMMA: "LUC! HELP ME GET OFF HERE!"

Lucca presses a button. The gyroscope rotates back to a staircase. 
Emma gets off the gyroscope.

They pick out books and read.

LUCCA, flipping through the books: "Interesting...
Even though the cause and development of World War 3 was depicted, there is no record of what brought about its end...
These books are interesting."

EMMA, we see her looking intensely at a children's picture book: "Mmmmm, very interesting indeed."

LUCCA: "So world war 3 happened. 
The opposing sides were the autocratic American Continental Empire against the Earth Federation (centered in Eurasia) that also included Canada and Brazil.
Oceania borrowed military from the Eurasian Continental Forces for defence...

And then the war just `ended', and the Northern Hemisphere was gone.
Oceania was the only surviving continent.
A group of scholars and working people, called the `Century Order', established the New World - a final city on earth, called Aztoria.
The study of Social Evolution Dynamics (wow, that's what the subject used to be called) was born - a rigorous formalised mathematical system capturing emergent laws of how a society evolves.

And that was that, peace and abundance for the next 400 years. 
The end of history."

EMMA: "And here's a series of maps showing the districts of Aztoria over time. 
That's pretty neat.
Look! There used to be a District 47 at the western most part of Aztoria.
But that district is erased from the map for the past 30 years."

LUCCA: "Nice catch, I would've missed it. 
So things DID happen...
The disappearance of District 47, and the Northern Hemisphere...
Those two key events are nowhere to be found.
The Institute might have purged it from contemporary knowledge."

\ 

\ 

Director KATZ enters a book club.
A group of people with working hats sit inside, reading.
A banner reads "for the happiness of all humankind". 
It was one of the older institute banners.
One of the people stands up and prepares to bow and greet the director.
Director KATZ walks up and grabs him.

DIRECTOR KATZ: "Was it one of you that organised the secret construction project at Ocean Spaceport?"

PERSON: "Spontaneous solidarity, your excellence."

DIRECTOR KATZ: "Don't screw around with me."

PERSON: "We know why you - why the Institute is afraid of the strikes.
When we created Aztoria, we anticipated this. 
We know the real predictions of SED.
We know what the SED equations say about your fate, and our fate.
That which you've turned into your badge that you wear, that symbol of humanity's potential to stumble into darkness...
But in reality... The future of Humanity lies in the stars..."

DIRECTOR KATZ, menacingly: "The Civil Protection Institute has weapons you cannot even fathom to turn against you."

PERSON: "So does the Century Order."

DIRECTOR KATZ: "WE are the Century Order! 
WE created the city!"

PERSON: "Not anymore. Not after the first 100 years.
You are now called the Civil Protection Institute.
And many people from the original Order joined the rest of society.
And how can they not? 
The Order was originally made up of ordinary people.
The Century Order went into hibernation."

DIRECTOR KATZ: "Don't do anything stupid."

PERSON: "We won't do anything stupid.
But will you?"

Director KATZ throws him onto the ground and walks out of the book club.

\end{document}
