\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Relic From Early Centuries}
\maketitle

%https://www.youtube.com/watch?v=072wpvM7aS8
%how do lighthouses work?

Petrol station. 
Lucca and Rachel are out of the car.
Rachel drinks from a cup.

LUCCA: "What a case."

RACHEL: "2 months after coming out, the magnetic beam pistol has already been turned into a murder weapon. 
Human's ability to turn anything into a killing tool is astounding."

LUCCA: "yeaah, it's like when we unlocked the atom.
You know, the atom bombs of the 20th and the fusion storms of the 21st."

RACHEL: "I got rest of the day free. 
Do you wanna head back to the Institute?"

LUCCA: "Play around a bit.
We're in District 70 rght? 
I got an old friend to visit."

\ 

\ 

Lucca walks to a lighthouse and a grave.
"In memory of one of the best mechanical engineers in service to Aztoria - Marco Korolev".
He pays his respects. 
A boy and a girl run up to him.

BOY: "Muuuuum! Muuuum! Uncle Luc is here!"

A woman walks up to him.
Lucca turns around.

LUCCA, smiling and lightly bowing: "Mrs Watson."

MRS KOROLEV: "Come in!"

\ 

Interior, house next to lighthouse.
Lucca looks at the lighthouse through the window.

[NARRATION: A long time ago, when humans were spread across all the continents of earth, material needed to be transported via sea. 
For this to be successful, ships needed guidance from a powerful beacon at the shores of destinations.

Now the overseas civilisations are gone, and ships are dead. So die the lighthouses.]

MRS KOROLEV, preparing the dining table: "How's work at the Institute?"

LUCCA, looking at the lighthouse: "A lot happening recently. 
There's a certain level of unease and dread in the day to day.
Like there's something big hiding and I don't know what's going on."

MRS KOROLEV: "Huh... Just like Marco.
And I never knew what he was up to."

LUCCA: "Back at the Factory Array, he always had a group of people to hang out with.
They would discuss history, science, wives and husbands.
It was a lively workplace."

MRS KOROLEV, with moisture in her eyes: "That's great."

LUCCA: "Eh, I'm sure he's told you about that."

MRS KOROLEV: "I hope you're enjoying it in the Institute though. 
Many interesting problems to solve?
Marco really liked you back in the days at the University.
Wouldn't stop talking about you."

MRS KOROLEV, close up: "He was the one who recommended you to Director Alma."

LUCCA, startled: "Director Alma? Marco!?"

MRS KOROLEV, smiling: "Even across a generation, they were good friends.
Probably because of his liking towards history."

\ 

\ 

Outside, Rachel is enjoying her drink.
Nerezza's image flashes before her.
She is startled, and starts chasing in the direction of the image.
This leads her nowhere.

\ 

\ 

Lucca has a meal with the family. 
The 2 children drag Lucca away from the dining table.

BOY: "Uncle Luc, I got something to show you!"

GIRL: "Follow us, uncle Luc!"

Lucca follows. Mrs Watson smiles.

\ 

The children lead him to the lighthouse.

BOY: "There's a treasure!"

GIRL: "Hidden by dad!"

BOY: "Dad said it was the greatest treasure on this earth!"

GIRL: "He promised to show us what it was, but he said we wouldn't understand it until we grow up!"

BOY: "We never got to see the treasure!" 

GIRL: "Uncle Luc is the smart one!"

BOY: "Uncle Luc will help us find the treasure!"

LUCCA: "A... treasure?"

GIRL: "Treasure hidden inside the lighthouse!"

Lucca looks up at the lighthouse that towered over them.

\ 

They enter the lighthouse.
Lucca turns on a torch. 

LUCCA: "It's so well maintained..."

There is a door behind which the treasure lies.
Next to the door is a music player and a black touchpad.

BOY: "That's the door!"

GIRL: "The treasure is inside there!"

LUCCA, studying the surroundings: "Amazing... It's a traditional gear driven mechanism.
A relic from early centuries."

LUCCA, running up the stairs, following the series of gears that run alongside the walls: "If we follow the path of power transmission along these gears, we arrive at..."

The gears terminate at the top, connected to the spinning shield of the lighthouse beacon.

LUCCA: "The spinning shield of the lighthouse beacon.
The spinning motion, when the lighthouse is on, drives the mechanism.
Marco has turned the entire lighthouse into an automaton..."

LUCCA, approaching a power lever: "Does this even work?"

\ 

When he turns the lever, the entire lighthouse springs to life!
A large screech can be heard from the house, and Mrs Korolev rushes to the window, observing the now operational lighthouse.

\ 

Lucca and the children run back down to the ground floor.
Gears are running in the background, but nothing more is happening.
The touchpad is now lit up.
A recording begins to play. 
This makes Lucca shocked.

\ 

RECORDING: "Dear member of the Bureaucracy, please input your favourite song: "

LUCCA: "Marco..."

\ 

After a long contemplation, Lucca enters the following: "Get on the A Train".

\ 

MUSIC PLAYER: "For good vibes everywhere, if you have feelings they can't tame...
Hop on board without a care, just come get on the A Train.

Oh you better hurry, hurry to get on the A Train...
The train will carry, you away from the rain...

The century bells have begun, so take a shelter before the rain...
There is only us all else is none, just come get on the A Train.

Oh you better hurry, hurry to get on the A Train...
The train will carry, ..."

\ 

A secondary group of gears start spinning.
The door opens.

\ 

BOY: "Wow! You really did it!"

LUCCA: "It's nothing too complicated. Just a single gear chain connected to the lighthouse's operation. 
If it was any more fancy I would not be able to figure it out.
It probably wasn't meant to be that impossible to access in the first place."

\ 

The door reveals a single book shelf, with 2 books on it. 
"Synthesis Mechanics", "A Brief History of Humankind".

\ 

LUCCA: "This!"

GIRL, with exaggerated and impressed arms extended: "It's the history of the wooooorld."

Lucca turns the pages, and a note falls out.

NOTE: "Thank you Alma. Thanks to you, everything has fallen in place.
My family are descendants from soldiers from the Eurasian Continental Forces. 
Later, they joined the Century Order who built Aztoria.
These are the books that remain from that age, that the Institute purged.
Please keep them safe, for the happiness of all humankind."

\ 

Lucca is very moved.
Mrs Korolev stands behind, at the entrance of the lighthouse.
The kids are scared and run out of the lighthouse.

MRS KOROLEV: "You found it."

LUCCA: "Ah, sorry, I shouldn't..."

MRS KOROLEV: "You can keep those cursed books."

LUCCA: "Mrs Korolev..."

MRS KOROLEV: "You're just like Marco...
Eventually, curiosity will kill."

Lucca realises something about Marco's death that makes him shiver.

MRS KOROLEV, turning away: "Take these away from me."

LUCCA: "Did the Civil Protection Institute..."

MRS KOROLEV, angry, turning back: "What does it matter what the Institute did?!
I don't care anymore!
What's the point of asking these questions?
What cause is so great that it's worth dying for?!"

MRS KOROLEV, stepping towards Lucca, pleading: "Before that cause, there is LIFE in the present!"

MRS KOROLEV, crying on Lucca's shoulder, while hitting him: "A life... with me."

Lucca stands there, unable to comfort her.

\end{document}

