\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Once More Beneath the City Lights}
\maketitle

LUCCA: "Really?"

ALMA: "Really. I have no need for them anymore.
You can keep them.
Marco was your friend too."

\ 

Interior, desk.
Lucca is reading the book of Synthesis Mechanics.

LUCCA: "Synthesis is to integrate all of humanity's consciousness into a single superstructure.
To understand the mechanics, let us begin with the basics.
(LUCCA: Written like a textbook, go figure.)

Human consciousness consists of information Currents in spacetime.
Normally residing within a human, over an electromagnetic brain, that is consciousness in its *standard form*.

Currents that reside within a deformed boundary separated from a brain, that is a *Newon*.
Such Currents can be said to be consciousness in its *non-standard form*, or simply *Newon form*.

In general, it is possible for consciousness to merge in the non-standard form.
Via physical contact of the boundaries of Newons.
However, when the concentration is large enough, people in surrounding areas can dissolve into Newons and merge as well.

Chain Reaction.
A large enough concentration of Newons, once began merging, creates a chain reaction. 
The dissolution spreads rapidly, eventually engulfing the entire region, like a growing event horizon for a black hole.

In order to artificially start a chain reaction, we require a site of nucleation. 
We call it a `Great Attractor', since that is where all the Newons are attracted towards.

A great attractor is in fact a perfect newon, one where the boundary is kept in perfect stable form, such that the original personhood is retained.
It no longer looks black, because information can leave the region.
And a great attractor can interact with their surroundings.

In summary, a great attractor plus a huge mass of Newons, equals Synthesis."

\ 

Lucca now reads a brief history of humankind.

BOOK: "The Newon bombs were what ended world war 3.
The Hegemonic American Union versus the Neo Degenerative Eurasian Federation.
The final Synthesis Catastrophe."

\ 

\ 

Lucca receives a phone call.
He immediately heads out. 

He arrives at Kaito's school.
All of Class of '78 gather there.
Emma turns around and sees Lucca, and runs towards him, crying.

LUCCA: "Emma! What's wrong?"

EMMA, crying: "Kaito! His... his..." 

TOM: "There was a knifing incident.
Someone got into Kaito's class with a knife, and..."

LUCCA: "Where's Kaito?"

TOM: "Here. Let's go inside."

\ 

Interior, Kaito's school.
A group of Institute agents are there, taking care of things. 
Lucca speaks with some of them. 

AGENT A: "We got it, don't worry."

Lucca nods.
Through the crowd, he can see Kaito sitting at the end of the corridor, looking up.

TOM, to LUCCA: "Let's be careful.
Don't want to make him cry."

They walk up to Kaito.
He looks up at them with no tears, but sheer dread.

TOM (to himself): "Shit, he's transcended crying."

KAITO: "Hey."

LUCCA: "Are you hurt?"

KAITO: "No."

LUCCA: "How many were injured?"

KAITO: "10."

LUCCA: "And..."

Silence.

TOM, interrupting: "What are you thinking right now, Kaito?"

Silence.
Have a few comic panels fixed on one angle, unmoving.
Lucca and Tom stand over Kaito.

\ 

\ 

Dusk.
Aloh's dining space.
The TV in the corner shows a PSA regarding a woman in black.
TV: "Have you seen this woman in your dreams?"

EMMA, to LUCCA: "Hm, I don't think I can sleep tonight.
Let's go around the city."

\ 

\ 

They sit at a riverside bench.
Buildings from across the river cast reflections in the water.
A group of people gather on the opposite side of the river, discussing something.
Nerezza briefly flashes.

EMMA: "Do you think Kaito will be okay?"

LUCCA: "I don't know."

EMMA: "Oh..."

A large debris slowly drift across the night sky.

EMMA: "Ah, that's..."

LUCCA: "The remains of Satellite-2."

EMMA, leaning on LUCCA: "Remember when we were small, we were told many cool things about the future...
Full automation, space exploration, reclaiming the Northern Hemisphere...
But as we grew up, none of those things arrived, did they?
Yet the same stories are told to our children.
Maybe it was foolish to believe in them in the first place.
Aztoria has stood still for 400 years, with nothing changing."

EMMA: "Luc, why do incidents like today happen?
Do the SED equations tell us?
Back when I was studying to be a computer, I was only taught to perform the computations, but not how to interpret them.
Do you know how?"

LUCCA: "The equations are beyond me.
I could only comprehend classical mechanics."

EMMA, looking at the city: "I can't believe it's been 13 years since highschool graduation...
I didn't even believe it during our reunion.
But today, seeing everyone come over to respond to a crisis of one of the classmates, I finally intuitively got it.
We are all adults now."

LUCCA: "And how does being an adult feel like?..."

EMMA, tiredly smiling at Lucca: "Even though we're adults, we don't have a clue do we. 
No one does.
Aztoria... is a weird city."

LUCCA: silence.

The city lights turn off.

EMMA: "Ah, the city lights."

LUCCA: "Guess it's about time. 11pm."

EMMA: "Hey, Luc! Let me show you something. Follow me."

\ 

\ 

Emma and Lucca board the Aztoria Train.

LUCCA: "The Aztoria Train?"

EMMA: "I found something special."

She looks out the window of the Train.
The train track has glass shields on either side.
The glass shield has a single straight line etching.
The straight line is broken at various points into segments.
But the segments are quite long to fit in the view of the window.

EMMA: "The train track has glass shields on the side.
Can you see the patterns on that glass?"

LUCCA: "It's just a long horizontal straight line, etched in."

EMMA: "Not quite, there are breaking points in the line. 
It's actually a bunch of really long segments, some longer, some shorter.
There is no artistic purpose, nor a practical one.
Yet, they are deliberately carved in."

LUCCA: "Hmm... what could a bunch of stripes possibly mean?"

EMMA: "Right? When I first saw it, I couldn't take my eyes off.
I didn't know what to think of it.
But then... The train started."

LUCCA: "!"

AUTOMATED ANNOUNCEMENT: "THANK YOU FOR BOARDING THE AZTORIA TRAIN - PROVIDING THE BEST TRANSPORT SERVICE FOR HUMANKIND.
THIS TRAIN GOES AROUND THE CITY LOOP INDEFINITELY.
AT A STATION, SWITCH TO ANY OF THE MAJOR BRANCHES OF THE AZTORIA TRAIN NETWORK TO EXIT THE CITY LOOP.
NEXT STATION: AZTORIA CENTRAL."

\ 

A group of people board the train, wearing worker hats.
They murmur something in the background, with books in their hands.

Emma is excited now, looking through the window.
The train takes off.

EMMA: "You see now, when the train is moving at full speed, the line just looks like something that turns on and off.
`On' when there is a line, and `off' when there is a gap.
The longer stripes appear to be `on' longer, the shorter stripes appear to be `on' shorter.
We've seen this type of signal back in school, right?"

LUCCA: "...you're right!"

EMMA: "It's a type of message used in war times, pre-extinction."

LUCCA: "Morse Code... Amazing, Emma."

EMMA: "Mr Williams told us, the centre of the Trainline's City Loop was where Aztoria began.
And the City Loop was part of something that existed long before Aztoria.
Maybe the earliest builders of the city were trying to tell us something."

LUCCA: "Do you know how to decode it?"

EMMA: "Does anyone? I don't think Mr Williams told us either.
Oh wait! Let's just ask one of them!"

\ 

She walks to the group of passengers with worker hats.

EMMA: "Hello!
Does any of you have a Morse Code cipher?"

They look at one another.

PERSON A: "You're lucky. I'm currently reading a book on World War 3, there must a Morse Code Cipher table somewhere in there.
Appendices...
Oh look, there you go."

EMMA: "Thank you! I'll take a picture."

PERSON A, tipping her hat, smiling: "Take care, unlikely friend."

EMMA: "Thank you!"

\ 

\ 

Emma and Lucca record the signals on the shield, completing a full trip around the City Loop.
They walk out of the train.
They walk through an array of colossal concrete blocks.
They look like buildings, but there are no windows, no doors.
They briefly look at it in awe.
There are posters with pictures of Nerezza showing "have you seen this woman?"

\ 

They see an entrance to an underground shelter.
They enter.
There are many dead birds on the ground.

EMMA: "Whoa... what is this place?"

LUCCA: "An underground shelter... with many dead birds inside."

EMMA: "Why do you think there are so many dead birds?"

LUCCA: "These blind birds primarily require magnetic fields to navigate. This chamber must have some kind of shielding from magnetic fields.
That means these birds who wander in have no way of getting out."

EMMA: "That's horrible..."

They explore the place.
Emma sweeps the dead birds up.
There are old records and a record player.
They put on music and Emma invites him to a dance.
He isn't very good. 

LUCCA: "Almost stepped on you."

EMMA, seamlessly stepping to the side: "I saw it coming."

EMMA, leaning into Lucca's face: "Here, let me comfort you."

\ 

\ 

EMMA, holding the picture on her phone: "Alright, do you want to start deciphering?"

LUCCA, grabbing the phone, already writing: "I've already started. Let's make it a race."

EMMA: "Whaaaat? Not fair! That's a surprise attack!"

LUCCA: "Come on, `fastest writing hands of the Class of 78', you shouldn't be scared."

EMMA: "Oh, you!"

She starts deciphering, glancing at Lucca's notes.

LUCCA: "No peeking!" 

Emma makes a face.

\ 

EMMA, considering how to say what she's about to say, glancing at LUCCA shyly: "You know...
I had a dream, or a memory...
We were on top of a building, among a lively city...
You were wearing your working garb at the Factory Array...
the world was a... happier place."

LUCCA: "That's a wonderful dream."

EMMA, disappointed: "So it *is* a dream, isn't it."

LUCCA: "I'm done."

EMMA and LUCCA, reading from the message: "`Beware of the Institute. 
Beware of Synthesis.
The Institute is afraid of future history.
In order for humanity to reach the next stage, the central bureaucracy - must be destroyed.
The weapon of the Century Order is Aztoria.'"

They look at each other.

EMMA: "I think I understand..."

LUCCA: "The meaning of precession."

LUCCA: "As Lambda said, precession not in space, but in time.
The Precession that the Institute is afraid of, is not any physical precession, but the precession of ages, precession of history.
From every Golden Age into a Dark Age, humanity is thrust into suffering, again and again.
Intense suffering on a grand, civilisation scale."

EMMA: "Precession... of Ages.
So it's a natural tendency of societies?
And the solution is to inhibit the human potential for change, which has that tendency as a side effect?"

LUCCA: "Do you remember seeing any of this in the SED equations?"

EMMA: "I was not taught how to interpret them, only the general mathematical structures.
At many points, I do remember seeing an output as a large rising and falling waveform, but I assumed that was an artefact of Fourier series, disguised in some form in the computations.
When those waveforms arose, we were told to dampen them."

LUCCA: "Rising and falling waveforms...
Is humanity really doomed?"

EMMA: "Though on the largest scales, the waveforms aren't that visible.
They are superimposed on a slowly and steadily rising trend."

LUCCA: "Emma, what do you think we should do with this information?"

EMMA: "I think... oh, i don't know...
So it is really happening right?
They are going to work on the Synthesis Project."

LUCCA: "Yes. Their pursuit killed Susan."

EMMA, a tear: "Susan? No..."

EMMA: "If that's it, then we're lost.
There is nothing we can do.
Might as well enjoy our time before then.
I'm sure we can enjoy it, Luc.
You can visit and listen to me sing, and..."

LUCCA: "You speak so dramatically, as if we are doomed.
Don't assume anything yet. 
There is still the weapon of the Century Order."

EMMA, solemnly: "Mm."

Shot of city at night.

\ 

\ 

[NARRATION: Newons - Plague carriers of Institute's sinister design, congregate beneath the city lights. 
But something else moves as well.]

Cut to the people with worker hats murmuring in various corners of the city.

[NARRATION: Can you see the city lights go out?
Can you feel the people converge?
Can you hear the silence in the air?
It is the sound of revolution.]


\end{document}

%revolution

%insomnia
