\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{The District is Westward}
\maketitle

In Aloh's dining space, Lucca is drinking something.

EMMA: "Hey, Luc..."

LUCCA: "Alright. 
What misadventure are you thinking of going on this time?"

EMMA: "Not an adventure, just a favour."

LUCCA: "What is it."

EMMA: "May I borrow your access card to the Factory Array?"

LUCCA: "What for?"

EMMA: "Mmmmm there are some clothes I want to manufacture, and some hand tools for..."

LUCCA: "Submit a request to the Institute, and they will access the Factory Array and manufacture it and deliver it to you."

EMMA: "And you ARRRE from the Institute!
Come on!
We can skip all the bureaucracy!"

LUCCA: "Alright. 
Keep it safe. 
And spend no more than 10 kilo Watt hours."

EMMA: "Thank youuu! I love you so much!"

LUCCA: "False. You love the access card to the Factory Array."

EMMA: "Heehee. You caught me."

LUCCA's thought: "The Institute is killing us all.
A coming Synthesis Catastrophe.
On the other end, a coming revolution against the state authority.
Synthesis must be prevented.
Revolution must happen.
District 47. 
A district that disappeared from history 30 years ago.
The final district to visit."

\ 

\ 

Lucca drives along the great continental road with a map in his lap.
After half a day, he drives past a farmer.
He stops at the side of the road and winds down the window.

LUCCA: "Excuse me, I'm looking for District 47. 
Am I going the right way?"

FARMER: "Yep. Westward."

\ 

\ 

Lucca arrives at the empty district.
Food delivery trucks have long stopped coming here.
Colossal concrete buildings still stand.
Just like the coastal structures, no window, no entrance.
He walks through the empty streets. 
Old Aztorian banners say "For the happiness of all humankind."

Lucca tries to get some extra fuel for his car.
As he walks up to the other cars, they crumble. 

Empty apartment buildings loom above. 
A sound suddenly reverberates over the street. 
It came from one of the apartments.
Lucca investigates.

Lucca arrives at the apartment.
The doorknob falls off as he touches it.
He gently pushes open the door.
Inside is a *young* artist, frantically gathering his fallen over bucket of paint brushes. 

\ 
 
LUCCA: "...hello?"

MR ARTIST: "Hey man, what's goin down?
Haven't seen someone in ages."

LUCCA: "Hi... I'm from the Civil Protection Institute."

MR ARTIST: "The Institute? 
They still care about stuff around here?"

LUCCA: "I... I don't think so. Mr..."

MR ARTIST: "Artist."

LUCCA: "`Mr Artist?'"

MR ARTIST: "Well, yknow. 
I don't really remember my name. So I decided I'll be called Mr Artist.
Cus yknow. I do the... (gestures around his canvas) art thing."

LUCCA: "Um. Mr Artist. Are you aware that your entire district is empty?"

MR ARTIST: "Oh it's empty is it."

LUCCA: "Been that way for 30 years, Mr Artist.
The auto-delivery trucks have been non-operational. 
Where have you been getting your food?"

MR ARTIST: "Food... Yeah. A human needs food to survive, doesn't it.
Look, all this talk about un-necessary details..."

LUCCA: "FOOD is not an un-necessary detail!"

MR ARTIST: "Maybe I'm trying to work something out myself, young man. 
Maybe the Mr Artist you're seeing right now isn't an accurate representation of... Mr Artist."

MR Artist: "I’m tired of talking now. 
I’d like some uninterrupted time painting if you don’t mind. 
Thanks for visiting though. 
It was a pleasant surprise."

The Artist turns around and starts painting. 
The painting is a woman wearing white clothes. 
His movement is mechanical and programmatic. 
He will not respond to anything anymore. 
Lucca walks around his apartment. 
A giant window shows a view of the street, and a window on the building opposite this one, where a woman with white clothes stands. 
Lucca jolts and runs up to the window. 
The woman steps back into the shadow. 

\ 

\ 

Interior, Institute.

AGENT: "First Director, you have a visitor."

FIRST DIRECTOR (as always, we can only see their back): "Come in."

It is Aloh.
The agent exits. The room locks.

ALOH: "Hello, First Director. 
I'm Aloh, volunteered caretaker of a communal dining area.
It's an honour to speak to you face to face."

FIRST DIRECTOR: "Sit down, Aloh. 
Pleased to meet you."

ALOH: "I thought only the Directors are allowed to see you in person.
I'm glad you seem as charismatic and upright as you do."

FIRST DIRECTOR: "This is a one-in-a-million exception.
You said that you wanted to `discuss the nature of Precession'. 
There is no chance I'm not speaking to you after I hear that."

ALOH: "Alright, let's get right to it then. 
First Director. 
Precession is *wrong*."

\ 

\ 

Lucca now walks on the streets again.
He turns a corner.
An old woman with a headscarf sits on the curb smoking.
Her face lights up.

[NARRATION: A cigarette. 
One of those cultural excrements that should have gone extinct in history.
Here in District 47, an old battleground for the future of Aztoria, it appears again.
The people versus the Institute. 
It's clear who won.]

OLD WOMAN, slowly: "A young new face! Where are you from?"

LUCCA: "The Civil Protection Institute. I'm here to investigate the disappearance of this district's people."

OLD WOMAN, nostalgic gaze into air: "The Institute...
`For the happiness of all humankind.'"

LUCCA: "What happened to this District?
Where are all the people?"

OLD WOMAN: "Synthesis.
They are at the diner at the edge of the world."

LUCCA: "They're still alive? Where is this diner?"

OLD WOMAN: "Westward."

As they converse, the woman in white clothes reaches into Lucca's pocket, stealing his car keys. 
This startles Lucca.
When he turns around, the woman is already running away, giggling.
When Lucca turns back to the old woman, she is no longer there.

\ 

\ 

Interior, First Director's room.

ALOH: "Precession, your grand thesis of history, is a convoluted distraction, built on observing the human timeline too closely.
Cycles are abstractions. You can fit almost anything into an up and down pattern.
The real thesis of history arises when you observe qualitative changes to human societies across time.
The thesis is called `evolution'."

FIRST DIRECTOR: "And by what ground are you making this claim?"

ALOH: "I'm trained by one of the original scholars of SED, from the Order that created this city."

FIRST DIRECTOR: "!..."

ALOH: "Century Order. Haven't heard that name in a while have you?
Your Institute is but their descendant."

FIRST DIRECTOR: "I could capture you right here."

ALOH: "You know that's unnecessary.
I know that what you are truly afraid of isn't me...
But the real predictions of SED."

FIRST DIRECTOR: "..."

ALOH, sharp stare: "SED predicts that you - the Aztorian Bureaucracy, the Civil Protection Institute, will die and disappear from history."

\ 

\ 

Lucca runs towards the diner.
He enters, the music is loud.
Everyone is dancing in the dark.
Lucca turns on the light and the room becomes silent. 
Everyone is frozen and looks at him.
The artist, farmer and old woman are all there.
The woman in white speaks from somewhere unseen.

LUCCA: "A trick of the light... there is only you."

WOMAN: "Why do you come here?"

LUCCA: "To find important answers.
What happened to District 47?"

WOMAN: "I am District 47."

The people suddenly disappear.
The diner has only a single lightbulb, casting light like a spotlight.
Standing in the spotlight is a lone woman in white.

LUCCA: "The Synthesis event really merged everyone in the district...
What are you exactly?"

WOMAN: "What the Institute calls a `great attractor'.
A perfect Newon.
The all-absorbing core of Synthesis."

Lucca is almost in awe.

WOMAN: "I was a scientist that worked for the Institute, experimenting on Synthesis... and I agreed to become the Great Attractor.
When I understood the implications of what I was studying, I immediately escaped. 
Due to the nature of being a great attractor, it's dangerous for me to be near any civilisation.
So I escaped, to as far from the city as i could.
But since Aztoria takes up the eastern quarter of the Oceania continent..."

LUCCA: "The only way to go was westward."

WOMAN, nodding in pain: "The Institute hunted for me. 
I was the `pinnacle of creation', they said.
The people of district 47 were kind, but in the end..."

As she says this, we see flashbacks.
Her running in the streets, and the Institute in pursuit.
They drop a suitcase from a plane.
It lands and opens, and a mass of Newons come out and rush towards her.
They climb into her, starting the Synthesis event.
The entire district's people dissolve and absorb into her.
She can't continue speaking.

Her face changes into that of the artist, farmer, and old woman.

WOMAN: "And this is all i have left.
Memories and thoughts, and my perception of the people in this district."

Her face returns.

WOMAN: "But the Newons are gone now. 
And I will stay here away from civilisation."

LUCCA: "There is currently a massive Newon Cloud approaching from the skies of the Northern Hemisphere."

WOMAN: "You lie. There is no such thing."

LUCCA: "If you had been anywhere close to humans in the past year, you would know.
Newons are being created via what the Institute calls a plague.
They are so numerous now that you can even see some loitering the city streets at night."

The woman’s eyes widen. And then a bit more. She puts her hands up to her face and starts shaking. 

LUCCA: "My guess is that Newons have been around even before the birth of Aztoria.
In fact, they were probably what wiped out the Northern Hemisphere, ending the Eurasia-American War.
No nuclear winter, no destroyed habitats... A clean mutually assured extinction.
And that mass of Newons began flying towards us, because 30 years ago... a Great Attractor is born in this city."

WOMAN, crying: "Stop! This means... Oh... What in space... What on earth...
What happened to District 47 will happen to the entire human race!
I can't run! 
I can't run!
There IS nowhere to run!
With a mass of Newons that big..."

Lucca observes her crying.

\ 

\ 

Interior, Institute.

ALOH: "The universe was a collection of matter.
Birth of chemistry.
Fighting against entropy, the complex chemical structures that could survive and replicate, did so.
Birth of life.
Evolution.
Birth of consciousness.
The first cognitive revolution.
Birth of society.
Human society hunted and gathered.
Then there was the agricultural revolution.
Food was no longer out of human control.
Birth of land ownership, and eventually, towns, cities, empires.
Birth of serfdom.
Industrial revolution, French revolution. 
Peasants rose up against feudal lords, then crushed, then rose again. End to serfdom, and end to empires.
Birth of industry, machinery, wealth creation on unprecedented scales.
Guided by humanism, liberty, and science and reason.
Two world wars.
First sign of a growing consciousness among humans that transcended national boundaries.
2100 - Birth of the Earth Federation.
Second cognitive revolution - discovery of Newons and Currents.
Earth Federation fractures. 
World war 3.
Birth of Aztoria.
...I wish i could say that we went on to explore the stars."

ALOH: "History is a process of evolution, through the resolution of contradictions, to transition between epochs.
Each epoch is defined by a contradiction.
Each resolution brings humanity to a new height.
The contradictions of yesterday led to the final world war, out of which birthed 3 things:

1. Unification of humankind, where it found refuge in Oceania.

2. The all-producing Factory Array with an all-intelligent production and distribution system. The first sign of true abundance. End to hunger, want; formulation of Central Economic Problem proven inadequate and redefined.

3. The study of Societal Evolution Dynamics. For the first time, humankind has the tool to *consciously* guide its own future.

But it also gave the central contradiction of our epoch: the bureaucracy versus the people. 
Back when the Century Order created Aztoria and became its leader, it knew its own lifespan had an expiry. 
Just like every single organisation that came before in the story of humanity,
Eventually, it was supposed to exit the stage of history, for humans to explore the great beyond.

But how could it? 
They were the owners of human psychology and history.
The future was too important to be let into the hands of the people.
So it clung tight, over centuries, became the Institute we know today.
The human productive potential poses a threat of drastic change, which carries the risk of humans stumbling into a dark age.
So you redirect that energy.
Into useless civil projects.
The creation and destruction of Districts, the expansion and shrinkage of residential complexes.
This meaningless precession of people, centuries of real dreams, impetus, and productive potential down the drain...

\ \ \ \ That is the REAL Aztoria Syndrome!"

\ 

\ 

The woman raises her head, a single tear can be seen, but not much, and she looks determined.

WOMAN: "I am a perfect Newon, but I am still subject to the same physics.
You need to use a magnetic beam pistol to destroy me."

LUCCA: "I agree."

WOMAN, smiling: "...Here I was hoping that one day, when all the Newons are gone, I can go visit my old friends, living somewhere in the city.

\ \ \ \ ...and a gardener, who loved trees... (Mr Tree from `Monster in District 14')"

She bows down her head.
Lucca uses his magnetic beam pistol.
Panels of her destruction are in slow motion.
Each frame shows her form more smudged out, until she fades in the light.

\ 

\ 

ALOH: "So this is the background upon which our story sets itself: 
the bureaucracy which has upheld peace, has long ceased being a progressive force. 
Humans find themselves in a world of nihilism, yet again.
Crime and mass mental suffering returns for the first time in memory.
Aztoria finds itself on the cusp of a new revolution." 

FIRST DIRECTOR: "Impressive. And after saying all that, what are you going to do?"

ALOH: "Nothing."

FIRST DIRECTOR, silence.

ALOH: "It was a pleasure to spill my thoughts to you, First Director.
You have excellent manners.
So long, and let us wait."

ALOH, exiting: "For the happiness of all humankind."

\ 

\ 

It's all over for the time being.
Emma, Lucca, Aloh are all in Aloh's dining area.

LUCCA, holding his access card: "50 kilo watt hours!"

EMMA, ashamed, lips puckered: "I'm shorry, I got carried away...
I thought 10 kilo watt hours would be enough..."

LUCCA: "This can't happen again, Emma.
Energy conservation is vital to the long term survival of a civilisation."

EMMA looks down, still ashamed: "Alright. I'll talk to you and work things through exactly next time."

EMMA, suddenly excited: "Oh oh oh, so what happened to District 47?
It was the Synthesis, wasn't it!"

LUCCA: "Mm."

EMMA: "And you got to see the Great Attractor."

LUCCA: "Mm."

EMMA: "That's crazy...
At least take a picture so I can see."

LUCCA: "That would've been rude."

Emma makes a face.

LUCCA, gazing into the city through the windows: "Now the final fight can come without obstacle."

EMMA: "How's your sleep?"

LUCCA, taking a sip: "Not any better."

\ 

\ 

View of the spaceport.






\end{document}