\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Birth of the Superstructure}
\maketitle


Exterior, Aztoria. 
Nerezza lays down her suitcase. 

\ 

NEREZZA: "All the Newons I've been harvesting, it's time to come out!"

\ 

The suitcase opens, and all the contained Newons inside burst outward, climbing toward her.
They merge into her body and she grows.
Lucca is still devastated in his fetal position with eyes shut.

\ 

NEREZZA: "Won't even look at me?
Witness the birth of the Superstructure."

\ 

Lucca doesn't move. 
People in the surrounding all dissolve into Newons.
The entire city dissolves and flies towards Nerezza, who is standing at the centre of Aztoria. 

Interior, Institute.
Some people around her have dissolved already.
Emma looks out the window towards the City Loop, still with tears in eyes.

\ 

DIRECTOR ROBERT: "Looks like he failed."

EMMA, tired smile: "Yeah."

\ 

The two dissolve.

\ 

\ 

Exterior, Aztoria.
It is a colossal, grotesque object.
The product of the final Synthesis event.
Contained within is the sum of human consciousness.

\ 

\ 

Fever dream segment as all consciousness fly towards one another.
Mr Tree hallucinates seeing his wife - the first attractor.
Professor Lambda sees Einstein.
Alex sees the launch of Sputnik.
Nerezza appears everywhere.
Aloh is the last to dissolve.

Interior of the synthesis. 
Lucca opens his eyes finally. 
Nerezza is singing.

LUCCA: "Mum? Is that you?"

They are in her bedroom, in front of her desk.
Lucca is young.
She is drawing. 

LUCCA: "What are you drawing?"

MUM: "I'm recording a dream."

We see her comics.

LUCCA: "What was your dream about?"

MUM: "It's a vision of happiness. 
A message from another time.
It is raining, and it is a joyous moment."

LUCCA: "So... these pictures are from another time?
When?"

Silence.

LUCCA: "Mum?"

Extreme close up of mum's eye.
She looks disturbing.
Revelation shot of her looking deformed, like a Newon.

LUCCA: "Mum!"

She stands up, menacingly towers over him and pushes him to the floor.
Lucca stands up as an adult, seeing her from outside a building.
He is at the shore. 
Concrete buildings are behind.
He looks backwards.
The land is full of Newons staring at him.
Through the Newon crowd, he sees Emma lie on the ground the distance. 

\ 

\ 

We change perspective to Emma. 
She lies on a beach.
The night sky is sinister, with shifting galaxies and nebulae appearing unusually close to earth.

EMMA: "I was insane."

She sees the first homo sapiens hunting.
They come towards her and gather around her body.

EMMA: "Two hundred thousand years of history.
Two hundred thousand years of murder, rape, starvation, stupidity."

EMMA: "And on the other side, two hundred thousand years of cooperation, progress, and painstakingly slow, but certain, enlightenment."

EMMA: "When I was small, people always seemed to unusually cater for me.
Explain to me things that should be common sense.
If there were lessons teaching me how the world worked in common sense, I surely missed out on all of them.
Like missing out on a grand inside joke between the rest of humanity."

EMMA: "To believe in a delusional life and be absorbed in it...
I took advantage of Luc.
Ah... I messed up for sure."

It starts raining.

EMMA: "Rain... makes me happy. 
Why is that?
At what moment in time was there rain, that was a joyous moment?
Must be another sign... of my insanity."

EMMA: "It's better if I... 
Just stay here."

Emma closes her eyes.
Nerezza stands over her. 

NEREZZA: "I agree. 
That's how you feel at this moment.
Open question: do you think an insane human deserves to live?"

EMMA: "Depends on the practical utility they can provide, I suppose.
As long as they don't harm others, and supporting them is sustainable."

NEREZZA: "And what does `utility' look like?"

EMMA: "Economics is one giant exercise of utility calculus."

NEREZZA: "Your society has reached abundance.
You've eliminated hunter and material want.
What more utility do you need to provide?"

EMMA: "Social utility..."

NEREZZA: "Great. Do you think you can't provide social utility?"

EMMA: "I don't know. 
Maybe try not to harm others with my own delusions?
That's like... social utility in the negatives."

NEREZZA: "I agree."

Emma laughs.

NEREZZA: "I disagree when you say you don't provide value.
Your emotions are at worst still enviable by others.
Your insights are fearsome.
You exude compassion."

Emma, still closed eyes.
She remembers telling Aloh "Aloh's trumpet exists to bring happiness to humankind."
She remembers sitting on the Aztoria Train, noticing the patterns on the side of the tracks, through the windows of the train.
She remembers guarding the door to the broadcasting room with her computer partners.
This makes her smile, and start descending into the sand.
Nerezza is satisfied.

TOM: "Emma! Emma! I finally found you."

EMMA, sleepily opening her eyes: "...Tom? 
Oh, of course you're here. 
Everyone is here.
We're all synthesising. Duh.
i can feel it."

TOM: "It's absolutely insane, this place."

EMMA: "And I'm absolutely insane. Wow, suddenly this place doesn't sound that bad."

TOM: "Huh? What are you talking about."

EMMA: "I don't know.
Maybe I just want to be a slob and lie here.
Whatchu gonna do, Tom?"

TOM: "If you don't get up, i'm going to drag you outta here."

Emma turns away on the beach.

TOM: "Come on, we'll go find Luc.
That'll get you going."

EMMA: "Foolishness to suggest my motivation is tied to one thing or one person."

TOM: "Then what is it?"

EMMA: "`For the happiness of all humankind', dumbass."

TOM: "I think it is simple curiosity.
And recently it just so happened that your memories of a life with Luc has unknown origin.
And so it became the primary mystery."

EMMA: "Whatever you say."

TOM: "Don't you want to know the answer?"

EMMA: "I already do. I don't care anymore."

TOM: "At least take a walk with me along the shore.
We need to find my wife as well."

\ 

\ 

Lucca.
Running through a labyrinth with Newons hiding around every corner.
In every corridor, he sees a memory with mum.
And the surroundings become more insane.

Lucca sits in front of a reception, about to sign the agreement for his mum to be admitted into the nursing home.
His expression is sinister, grotesque.
He thinks that he will be relieved when he does not have to take care of mum anymore.
Watching this scene, our Lucca screams. 
Montage of his interactions with Nerezza.

Newons approach and tower over him, tormenting him.
He clutches at himself crying and asking for forgiveness.

Nerezza waves her hand.

NEREZZA, caressing Luc in her lap: "Synthesis event going smoothly.
Understand your human heart.
Luc! Ask yourself.
Are you really okay with your humanity?"

LUCCA is only capable of repeating: "I'm sorry... 
I'm sorry..."

Nerezza looks at him with a tinge of pity.




\end{document}