\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Aztoria}
\maketitle

Exterior, dusk, Lucca walks through an empty city.
The superstructure sits ominously in the distance, at center of the City Loop.

\ 

LUCCA: "`The trajectory of history is dictated by the movement of masses.' 
How can one person do anything?
Mum...
Sorry, even if you give me a chance to live, I'm powerless alone.
I may live out the rest of my days in Aztoria alone, as the last human..."

\ 

An image of Nerezza appears in the distance. 
This time, it finally struck Lucca.
He remembers his first encounter with the image at shore.
This causes his entire body to tremble.

\ 

LUCCA: "Mum! I finally understand! The meaning of your appearances. There really is a chance!"

\ 

Lucca runs to the shore with a sledge hammer. 
He stands below the towering blocks of building-like concrete structures.
What is the purpose of these structures?
He strikes it with the hammer, once, twice.
Images of Nerezza silently observe him.
On the third strike, a thick layer of concrete breaks away, revealing something shiny inside.

\ 

LUCCA: "Metal?"

LUCCA, looking to his side and seeing the entire row of these concrete structures: "What on earth would the city need colossal sized metal rods for?"

LUCCA, slapping his own head after a pause: "What am i doing? 
There must be others awake like me."

\ 

\ 

Lucca broadcasts a message to the city.

\ 

LUCCA: "Hello, I am Lucca. Awake during these final hours. 
If you are also awake and can hear this, please come to the communal dining space that Aloh was care-taking. 
If you are really awake at this moment, I believe you should be a regular visitor to that place for years.
I will see you there."

\ 

\ 

He arrives at the diner.
All the regular visitors are there. 

\ 

YOUNG MAN A: "Oh dear, Lucca, what the fuck is happening to this city?"

YOUNG WOMAN A: "All i remember was a revolution against the Institute, and when I came to, the city looks like this, with that thing... sitting at the center of the City Loop."

LUCCA: "That thing imprisons the sum of human consciousness, and we are going to destroy it."

MARRIED WOMAN: "Why are we not in it?"

LUCCA: "That thing is the Plague... If we are insomniac, we will be immune to whatever caused the others to break down.
And I suspect over the years, Aloh has been feeding us things that develop insomnia."

MARRIED MAN: "Where is he?"

LUCCA: "I give up trying to understand that man.
I don't think we will see him anywhere on earth again."

HOMELESS PERSON, MEMBER A OF ORDER: "What matters is we are awake, we are material, and we can alter the situation."

LUCCA: "You are from the Order of Scholars, aren't you? 
Do you know what the Order left for us?"

MEMBER A OF ORDER: "The Plague was engineered long before this city, during the final war. 
The Order explicitly mentioned that they left a weapon, a weapon of the order - a mechanism to kill the superstructure."

LUCCA: "Could you please tell us where it is and how it works?"

MEMBER A OF ORDER: "I regret. I don't possess that knowledge. For whatever reason, no one may possess that knowledge, absolutely no one that came after Generation 1 of Aztoria."

HIGHSCHOOL BOY: "Probably to prevent the Institute gaining that knowledge and getting rid of the weapon beforehand."

MEMBER A OF ORDER: "To be clear, the Institute IS what the order became. 
So the earliest scholars must have foreseen the corruption, and guarded the weapon from even themselves."

LUCCA: "The song 'Get on the A Train'... What does it mean?"

MEMBER A OF ORDER: "It is one of those things that were passed on over the ages. 
Presumably it leads to a clue for the weapon."

LUCCA: "I've taken the train before and investigated it.
Look through the window; when the train is running at high speed, the long and short striped patterns on the side walls look like flashes."

MEMBER A OF ORDER: "Morse Code. 
A relic of the past.
Members have gone and decoded it. 
It wasn't very helpful."

LUCCA: "It said `Aztoria'."

YOUNG WOMAN A: "What do we do?"

MIDDLE AGED GENTLEMAN: "I'm not very connected with what has been happening with the Plague. 
So what was the standard way to kill the Plague carriers?"

LUCCA and MEMBER A interrupting each other: "You'd-/ There's-"

MEMBER A: "Sorry, you go."

LUCCA, after a brief nod towards MEMBER A: "Plague carriers, also called `newons', are smaller versions of that thing in the distance. 
It is a boundary that contains Currents of consciousness. 
It is electromagnetic.
It is subject to disturbance by powerful magnetic fields.
We use this magnetic beam pistol to shoot a magnetic field through it.
It disintegrates in no time."

HIGHSCHOOL GIRL: "How does the beam pistol work?"

LUCCA, gradually slowing down as he dawns upon some realisations: "At the centre, there is a tiny loop of wires conducting electricity. 
The electricity and the loop is what generates the magnetic field...
To enhance it, we attach an array of metal rods around the loop; the metal becomes magnetised, adding to the magnetic field..."

LUCCA, another brief pause: "Now, this pistol is clearly too small for that thing."

HIGHSCHOOL GIRL: "So to destroy such a thing, we need a magnetic field.
The most powerful magnetic field, powerful enough to destroy it."

LUCCA: "You are right, i think. That thing works in no different way from the ordinary newons, so it must be subject to the same physics."

HIGHSCHOOL GIRL: "And to generate a magnetic field, you always need a loop of wires with some electric current running through it, right?"

LUCCA: "Y e a h... The physics of magnetism dictates so."

HIGHSCHOOL GIRL: "So if we construct a maaaassive loop or wires, centred around that monstrous thing, and connect it to all of Aztoria's power supply..."

LUCCA: "You are absolutely correct."

MARRIED MAN: "Will we even have enough time to make such a construction?"

LUCCA: "We already have it. 
The Aztoria Trainline's City Loop. 
Its electric tracks can be connected to all the major fusion power stations.
That will generate an electric current powerful enough to melt the entire train line into oblivion. 
With such power, the magnetic field must be strong enough to destroy that thing."

LUCCA, striding: "Have you noticed some strange looking coastal structures? 
Those are actually metal rods, colossal sized metal rods.
The entire city of Aztoria, is a gigantic magnetic beam pistol."

\ 

The entire room is stunned. 

\ 

LUCCA: "I've only been a mechanical engineer for a while, so I don't know how the power stations work exacty. Do we have an electrical or civil engineer here?"

MARRIED MAN: "I am. 
I've studied our power stations during my time at the Aztoria University.
There is really not much to it for what we need. 
The train, during normal operation, travels over sensors that automatically connects the tracks to the power station that the train is closest to.
What we need, it sounds like, is to manually switch on the power to the tracks from every power station at once." 

LUCCA: "There is no time to waste. 
Each person takes charge of one power station.
Lets move, and get on the A Train."

\ 

\ 

The people exchange their contacts and board the trains towards each power station.
They look towards the swarm of newons at the centre with dread but also determination.
They reach their power station and locate the switch. 

\ 

PERSON 1: "Waterloo power station located! Switch located!"

PERSON 2: "Yarra power station located! I've found the switch." 

...

LUCCA: "Coastal power station located! Switch located!"

...

ENGINEER: "Okay, here goes nothing."

OLD MAN. prompting a widening of Lucca's eyes: "Wait, before we switch...
How devastating will the destruction be? 
Are we safe from the magnetic fields?
And the debris?"

ENGINEER: "Oh no. 
I - I haven't thought about that."

LUCCA: "That must be what the underground bunkers are for.
There are shelters all around the city in which magnetic fields are null.
You will find many dead birds inside as a consequence. 
Look for one."

ENGINEER: "My goodness... They planned for everything."

MEMBER A: "They were a unified humankind with a vision for the future.
Almost no problem is unsolvable given enough time."

ENGINEER: "Alright, I've switched the power to connect to the tracks!
And I am running towards the shelter. 
Everyone else do the same!"

\ 

They do.

\ 

LUCCA: "Well done, fellow citizens."

HIGHSCHOOL GIRL: "Thank you, all humans."

LUCCA: "..."

\ 

The tracks become electrified. 
Magnetic fields are generated. 
The colossal metal rods at the coast move!
All the concrete breaks off, as the metal rods are attracted to the giant magnet that is the City Loop. 
They fly towards it as the City Loop lets out one final scream of magnetic fields, piercing the superstructure.
The train line breaks completely as the metal rods smash into it. 

A final full page panel showing the superstructure obliterated over earth.


\end{document}