\documentclass[11pt]{article}

\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Currents}
\maketitle

Interior of synthesis, final moments.
Aloh plays his trumpet.
Nerezza approaches from the side.

\ 

ALOH: "Happy?"

NEREZZA: "Aloh, I couldn't... 
Nothing I do can repay my debts.
We don't deserve you..."

ALOH: "Maximum allowed intervention to produce the minimum desired change.
I haven't crossed any bottom line. 
A few drops of medicine in coffee cups.
I will be fine."

NEREZZA: "..."

ALOH: "Well, it's time for me to leave all of you be."

NEREZZA: "Where are you going?"

ALOH: "A far away city. I am going to lead another child towards its future."

NEREZZA: "Say hello to them for us."

ALOH: "No. You will do it yourself.
One day, humans will join that universal symphony of Galactic History.
Until then..."

NEREZZA: "Hmm. Can I see what you actually look like?"

ALOH: "Don't want to scare you."

NEREZZA: "Alright. So long, Aloh."

ALOH: "Professor Gallo, it's been a pleasure."

\ 

\ 

Now onto Emma.
It is an art gallery. 
Edges of the room are too far to be seen, the area of visibility is bounded by bright afternoon sunlight.
Emma stands in front of a crude drawing of a human face with the caption "space, time, and beyond."
It is a drawing by Lucca.

Duplicate panel shows Nerezza suddenly standing next to her.

\ 

NEREZZA: "This art lacks technique."

EMMA: "And it's beautiful."

NEREZZA, pointing to a classical painting: "Against the one you're looking at, I raise this painting from an epoch of yore. 
Evocative, instinctual, romantic."

EMMA, pointing at Lucca's: "Look, look. Evocative, instinctual, romantic."

NEREZZA: "You would call this romantic? There is fear and awe here?"

EMMA: "Of course. 
When I see this picture, I shudder with excitement and fear...
For the might of humankind.

"A human... Wields a pair of laborious arms... [Image of Alex the construction worker]

"Restless legs that walk the earth... [Lucca running through the city]

"And a brain capable of invention. [Professor Lambda]

"A human has so much depth in thought,
so infinite in feeling and imagination,
so fearsome in reason and determination.
So ingenious in creation."

NEREZZA: "Pride! Hubris?"

EMMA: "What can I say, I am a humanist."

\ 

Nerezza slyly smiles.

\ 

\ 

The two are now at the top of a building.
It is the same building on which Emma remembers embracing Lucca. 
Suddenly, a great beam rips through the fabric of their reality.

\ 

EMMA: "Whoa!"

NEREZZA: "They did it. 
The synthesis is about to end.
Emma, sorry for putting you..."

EMMA: "I don't begrudge you. 
Here in the Synthesis, I could hear Susan talking.
Whatever emerges when this ends, whatever shape I will take...
I, for one, look forward to becoming a member of New Human."

NEREZZA, surprised: "..."

EMMA: "That's the real purpose of all this isn't it?
Why you agreed to partake in this project."

NEREZZA, shook, looking down: "...Emma, listen carefully.
All the memories you thought you lost, the wedding, the rooftop, a peaceful life with Luc... They can't be found anywhere in your past. 
That's because... they are memories from the future.
Carried to you by the warm Currents of time."

\ 

Large panel showing Emma at the center, with large currents radially extended from her head.
She is visibly shocked with the revelation.
She begins to fade as the synthesis ends. 
Nerezza narrates as Emma gradually disappears with tears of intense joy; her head disappears last.

\ 

NEREZZA: "The New Human will be as devoted to reason as a scientist, as rich in emotion as an artist, as imaginative as a child.
Their brains will be more in tune with Currents, and radiate compassion, understanding, foresight.
You will become proto telepathic.

"But there were humans who started this process earlier, even before the plague.
Emma, you are most wonderful.
I'm proud to say you and Luc will get along."

\ 

\ 

Exterior of synthesis, in Aztoria.
The superstructure is torn through the center, with large volumes of newon following the powerful magnetic fields upward into the sky. 
The entire structure twists, deforms, is annihilated beyond recognition.
Eventually all of it - all of the newons - are flung into the air.
The collective mass of human consciousness rains down, breaking into smaller and smaller pieces, untill every newon is separated from another, as they fall and return to earth. 

Lucca sits inside shelter 427. 
Suddenly, Nerezza sits next to him.

\ 

NEREZZA: "I knew you could do it."

LUCCA: "Me too."

NEREZZA: "You too?"

LUCCA: "Mm."

NEREZZA: "Tell me, how did you come to that insight?"

LUCCA: "It was when I saw images of you appearing in various places."

NEREZZA, pointing towards a timely image of Nerezza: "Like that one?"

LUCCA: "Ever since that day I was walking along the shore, I started noticing those images more.
At times on the ground, at times in the air, at times in an impossible orientation. 
Always brief - silent and unmoving in a single instant.
A phenomenon with unknown origin; it surely was the final mystery."

NEREZZA: "A mystery indeed. 
I don't even know what those are."

LUCCA: "When we destroyed the superstructure... obliterating and ripping you apart...
All the pieces of your existence were... 
Scattered across spacetime."

\ 

Pause for that to sink in.
Montage of every scene of Nerezza's appearance.
Montage goes into the future, for example at Lucca's wedding.
Nerezza stands in the back.

\ 

LUCCA: "Powerful Currents deliver your images radially outward in space and time, with this event at the center.
That would explain why your images are more concentrated around this event, and there were not that many of you, the further we go in the past.
And I assume in the future, you will appear less and less frequently."

NEREZZA, a joyous and slow epiphany: "...Isn't that right! Hahaha!"

LUCCA: "So... What happens from now?"

NEREZZA, longingly looking upwards: "Well, humans will become proto-telepathic. 
Now, without the coercion of a central bureaucracy, humankind will be free to... do whatever it wants."

LUCCA: "And then?"

NEREZZA: "Our descendents will probably be spread across stars."

LUCCA: "And then?"

NEREZZA, standing up: "We may finally become active participants in a universal symphony we call Galactic History."

LUCCA: "And then?"

NEREZZA: "..."

\ 

The two stand facing each other.
The two embrace. 

\ 

LUCCA: "Thank you for being the mother of New Human.
We will remember you until the end of time."

NEREZZA, appearing in her older form, actually crying for the first time in the story: "Ahh... Luc, you've grown so tall."

\ 

\ 

The sun rises over earth.


\end{document}