\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Birth of the Superstructure}
\maketitle


Exterior, Aztoria. 
Nerezza lays down her suitcase. 

\ 

NEREZZA: "All the Newons I've been harvesting, it's time to come out!"

\ 

The suitcase opens, and all the contained Newons inside burst outward, climbing toward her.
They merge into her body and she grows.
Lucca is still devastated in his fetal position with eyes shut.

\ 

NEREZZA: "Won't even look at me?
Witness the birth of the Superstructure."

Nerezza sees Rachel standing behind a fallen Lucca, holding up a magnetic beam pistol.

RACHEL: "Take this!"

NEREZZA: "Too late."

Rachel fires, passing right through Nerezza. 
Nerezza's growth is unhindered.

\ 

Lucca doesn't move. 
People in the surrounding all dissolve into Newons.
The entire city dissolves and flies towards Nerezza, who is standing at the centre of Aztoria. 

\ 

\ 

Interior, Institute.
Some people around Emma have dissolved already.
She looks out the window towards the City Loop, still with tears in eyes.

\ 

DIRECTOR KATZ: "Looks like he failed."

EMMA, tired smile: "Yeah."

\ 

The two dissolve.

\ 

\ 

Exterior, Aztoria.
It is a colossal, grotesque object.
The product of the final Synthesis event.
Contained within is the sum of human consciousness.

Fever dream segment as all consciousness fly towards one another.
Mr Tree hallucinates seeing his wife - the first attractor, who says "the tragedy of District 47 repeats..."
Professor Lambda sees Einstein, who says "it is time we immediately reassert the value of humanity..."

Alex sees the launch of Sputnik.

RADIO HOST: "Coming live from British Broadcasting Centre: Soviet scientists have launched a symbol of Man's liberation from the forces that have hitherto bound Him to earth. For the first time, mankind has reached for the stars, and found it within his grasp."

NEREZZA: "Unlikely acquaintance, we meet again."

ALEX: "It's a joy. 
But I don't need Synthesis.
Though I can't deny it would be interesting to see what it subjectively feels like during the process.

LAMBDA: "From Newton to Tsiolkovsky, from Sputnik to the moon, from Mars to Europa, from Jupiter to beyond the infinite, it is a journey violently stopped before completion."

NEREZZA: "For the sake of Synthesis."

ALEX, smiling: "What a shame.
Suppose it is your story.
I'll leave you to do whatever you like."

\ 

Nerezza appears everywhere.
Aloh is the last to dissolve.

DIRECTORS, together: "We have synthesised humanity.
History is no more.
The sun sets on Aztoria.
All is right with the world."

\ 

\ 

Interior of the synthesis. 
Lucca opens his eyes finally. 
Nerezza is singing.

LUCCA: "Mum? Is that you?"

They are in her bedroom, in front of her desk.
Lucca is young.
She is drawing. 

LUCCA: "What are you drawing?"

MUM: "I'm recording a dream."

We see her comics.

LUCCA: "What was your dream about?"

MUM: "It's a vision of happiness. 
A message from another time.
It is raining, and it is a joyous moment."

LUCCA: "So... these pictures are from another time?
When?"

Silence.

LUCCA: "Mum?"

Extreme close up of mum's eye.
She looks disturbing.
Revelation shot of her looking deformed, like a Newon.

LUCCA: "Mum!"

She stands up, menacingly towers over him and pushes him to the floor.
Lucca stands up as an adult, seeing her from outside a building.
He is at the shore. 
Concrete buildings are behind.
He looks backwards.
The land is full of Newons staring at him.
Through the Newon crowd, he sees Emma lie on the ground in the distance. 

\ 

\ 

We change perspective to Emma. 
She lies on a beach.
The night sky is sinister, with shifting galaxies and nebulae appearing unusually close to earth.

EMMA: "I was insane."

She sees the first homo sapiens hunting.
They come towards her and gather around her body.

EMMA: "Two hundred thousand years of history.
Two hundred thousand years of murder, rape, starvation, stupidity."

EMMA: "And on the other side, two hundred thousand years of cooperation, progress, and painstakingly slow, but certain, enlightenment."

\ 

Emma sees herself when young, with Luc.

EMMA: "What did I do wrong here?"

LUCCA, EMMA listens absolutely absorbed: "Typical mistake.
It's because you're writing down the maths purely by pattern recognition, without actually understanding it.
You ought to be able to have an intuition for the meaning behind these notations, look past the complex notations, see the simple geometric truth hidden beneath formal statements. 
Otherwise you'll never be able to solve a previously unseen problem, innovate, or surpass Susan's abilities."

EMMA, making a face: "You could've said that a lot nicer."

Lucca doesn't move, continues doing the exam.

EMMA, anxious: "Mm, well, Susan can do the more powerful intuition stuff, and I can do the handy calculation stuff. 
It's all a team effort.
Heehee."

LUCCA: "Sure."

\ 

EMMA, narrating: "When I was small, people always seemed to unusually cater for me.
Explain to me things that should be common sense.
If there were lessons teaching me how the world worked in common sense, I surely missed out on all of them.
Like missing out on a grand inside joke between the rest of humanity."

EMMA, back on beach: "To believe in a delusional life and be absorbed in it...
I took advantage of Luc.
Ah... I messed up for sure."

MRS KOROLEV observes her with eyes widened.
After a while, she smiles and sighs and turns away and disappears.
It starts raining.

EMMA: "Rain... makes me happy. 
Why is that?
At what moment in time was there rain, that was a joyous moment?
Must be another sign... of my insanity."

EMMA: "It's better if I... 
Just stay here."

Emma closes her eyes.
Nerezza stands over her. 

NEREZZA: "I agree. 
That's how you feel at this moment."

EMMA: "Luc's mum? Have you come to mock me too?"

NEREZZA: "No, just an open question: do you think an insane human deserves to live?"

EMMA: "Depends on the practical utility they can provide, I suppose.
As long as they don't harm others, and supporting them is sustainable."

NEREZZA: "And what does `utility' look like?"

EMMA: "Economics is one giant exercise of utility calculus."

NEREZZA: "Your society has reached abundance.
You've eliminated hunger and material want.
What more utility do you need to provide?"

EMMA: "Social utility..."

NEREZZA: "Great. Do you think you can't provide social utility?"

EMMA: "I don't know. 
Maybe try not to harm others with my own delusions?
That's like... social utility in the negatives."

NEREZZA: "I agree."

Emma laughs.

NEREZZA: "I disagree when you say you don't provide value.
Your emotions are at worst still enviable by others.
Your curiosity and insights are fearsome.
You exude compassion."

Emma, still closed eyes.
She remembers telling Aloh "Aloh's trumpet exists to bring happiness to humankind."
She remembers sitting on the Aztoria Train, noticing the patterns on the side of the tracks, through the windows of the train.
She remembers guarding the door to the broadcasting room with her computer partners.
This makes her smile, and start descending into the sand.
Nerezza is satisfied.

TOM: "Emma! Emma! I finally found you."

EMMA, sleepily opening her eyes: "...Tom? 
Oh, of course you're here. 
Everyone is here.
We're all synthesising. Duh.
i can feel it."

TOM: "It's absolutely insane, this place."

EMMA: "And I'm absolutely insane. Wow, suddenly this place doesn't sound that bad."

TOM: "Huh? What are you talking about."

EMMA: "I don't know.
Maybe I just want to be a slob and lie here.
Whatchu gonna do, Tom?"

TOM: "If you don't get up, i'm going to drag you outta here."

Emma turns away on the beach.

TOM: "Come on, we'll go find Luc.
That'll get you going."

EMMA: "Foolishness to suggest my motivation is tied to one thing or one person."

TOM: "Then what is it?"

EMMA: "`For the happiness of all humankind', dumbass."

TOM: "I think it is simple curiosity.
And recently it just so happened that your memories of a life with Luc has unknown origin.
And so it became the primary mystery."

EMMA: "Whatever you say."

TOM: "Don't you want to solve the mystery?"

EMMA: "I already did. I don't care anymore."

TOM: "At least take a walk with me along the shore.
We need to find my wife as well."

\ 

\ 

Lucca.
Running through a labyrinth with Newons hiding around every corner.
In every corridor, he sees a memory with mum.
And the surroundings become more insane.

MUM, young: "Isn't it strange?
Why is it that staring at the universe makes us feel this way?
Don't you think this is a riddle for the ages?
Even when you and I pass away, we probably won't be anywhere closer to the answers."

Decades pass by.
Nerezza and Lucca stand at the coast, looking into the ocean.

NEREZZA: "Why did you abandon me?"

LUCCA: "I was simply... tired of taking care of me."

NEREZZA: "Why didn't you visit me?"

MR WILLIAMS in his young form stands over Lucca as he says the following.

MR WILLIAMS: "You couldn't see you. Not after what you did.
And the longer you didn't see her, the more scared you were to go see her...
the longer you ended up not seeing her...
The more scared you were to go see her...
the longer..."

NEREZZA: "Scared of what?
Scared of seeing me being angry at you?
And more angry?
And more angry?
The body I left behind, with half of my personality."

Lucca sits in front of a reception, about to sign the agreement for his mum to be admitted into the nursing home.
His expression is sinister, grotesque.
He thinks that he will be relieved when he does not have to take care of mum anymore.
Watching this scene, our Lucca screams. 
Montage of his interactions with Nerezza.

Newons approach and tower over him, tormenting him.
He clutches at himself crying and asking for forgiveness.

Nerezza waves her hand.

NEREZZA, caressing Luc in her lap: "Luc, the synthesis event is going smoothly.
Understand your human heart.
Ask yourself.
Are you really okay with your humanity?"

LUCCA is only capable of repeating: "I'm sorry... 
I'm sorry..."

NEREZZA, stroking his hair: "Luc... 
When you are no longer incapacitated by your past mistakes, you will have grown out of your infancy.
Show me some kindness in the present, Luc.
Luc?"

Nerezza looks at him with a tinge of pity.




\end{document}