\documentclass[11pt]{article}

%\usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{New Human}
\maketitle

Interior of the Synthesis.


Lucca `wakes up' in his couch to a sound calling him. 
It says `Luc.'
He walks into the living room. 
Bright afternoon sunlight shines through the curtains.
It is his mum trying to get to the kitchen.

Lucca is so shook that he becomes mute for a moment.
All he can do is to observe his mum.

MUM: "There you are.
I'm hungry.
help me get to the kitchen."

LUCCA: "The Institute... plans to synthesise humanity.
You have dementia... are supposed to be in a nursing home."

MUM: "What Institute? You mean the Civil Protection Institute? What dementia?
You mean to question the sharpness of the First Assistant at the Neuroscience Labs?
Synthesise humanity?
Is that another one of your dreams?"

LUCCA: "I-"

MUM: "Come on Luc, help me get to the balcony. It's a beautiful day."

\ 

\ 

Interior of Synthesis.
Mrs Korolev, Director KATZ.
Mrs Korolev stands in front of Director KATZ. 
Her sudden appearance scares KATZ to his feet.

DIRECTOR KATZ: "I-it's you..."

MRS KOROLEV, looking at her surroundings: "I see, this is the meaning of Synthesis.
There's nothing shielding you from me now, Director KATZ.
You are a traitor to the Century Order, a traitor to history...
And above all, a traitor to all the working people in the world you claim to represent!"

DIRECTOR KATZ, seeing the gun in her hand: "No no no no no I can explain, I can explain! 
Your husband, Marco...
If he is in heaven watching, he wouldn't-"

MRS KOROLEV: "May the universal contempt of humanity, fall upon you."

Mrs Korolev shoots Director KATZ.
He falls down, dissolving into Newon goo.

\ 

\ 

Interior of Synthesis.
Nerezza, Kaito. 

NEREZZA: "First Director."

KAITO: "The rest of the Directors are already fully synthesised. 
They're gone.
There is no turning back for them."

NEREZZA: "In such a rush, huh."

KAITO: "I gave them the order.
And the rest of us don't have much time left either.
Soon, we won't be able to have a conversation like this."

\ 

They are now in a park, watching Lucca, Emma, Tom as children, playing.

\ 

NEREZZA: "That's fine.
Kaito, what's the colour of the sky?"

KAITO: "It's blue."

NEREZZA: "Can you feel the sand?"

KAITO: "Yes. I can touch it.
The sand collective feels soft, even though each individual grain is hard and stabby."

NEREZZA: "How does it feel to feel things like that?"

KAITO: "It feels... pleasant."

NEREZZA: "how does it feel to be a First Director?"

KAITO, as a child: "The Institute saw to it that the Class of 78 was sure to spread over important positions in society. 
And among them, a First Director for the coming decades.
I was only selected by chance."

NEREZZA: "And how do you feel about that?"

KAITO: "Even as a First Director, I was unable to protect my dear students.
What I could do, was see the Institute's Synthesis Project to its end."

NEREZZA: "Tell me about those students, Kaito. Was it fun?"

KAITO: "It was! They grew like flowers, like trees.
If I had the chance, I would return to teaching, and take on a class again.
And again.
And again."

Nerezza smiles.

NEREZZA: "It's okay for humanity to make mistakes.
It's okay for humanity to hurt itself, for decades, centuries, even millenia!
I'm serious!
As long as good knowledge is preserved and passed on, as long as we learn and teach...
As long as humankind has memory, and has a chance to change and grow...
It'll all be worth it in the end, Kaito."

KAITO, eyes closed: "I'm starting to think...
I want to live."

Mr Willians appears and sits next to Kaito.
Nerezza stands behind them now, with a sharp stare and a satisfied smile.

\ 

\ 

Interior of Synthesis.
Tom, Emma.
They are walking along the shore, star gazing.
Nerezza's images appear in the sky.

TOM: "Whoa."

EMMA: "I know. Romantic, isn't it?"

TOM: "That's my line.
It was in the past, a conversation with Luc."

EMMA: "Past, present... Luc, me. What's the difference?"

TOM: "I don't know. 
A broken Century Line of glass-like stars passing.
Newton said that's what apples are made of."

EMMA: "I like apples, they are big."

TOM: "I like big, they are rainy.
And raining makes me a happy woman."

EMMA: "Getting... hard... to speak. 
Isn't it... Tom?"

TOM: "Harder... than... ever.
And think hard, Emma.
I mean, hard to think.
And who stole my marriage with Luc?
Maybe- whoaaAAAA!"

They were near the edge of a steep drop of the ocean bed. 
Emma grabs him just in time.

EMMA: "Careful, we were almost falling into the ocean."

TOM: "Yeah, and our consciousness were about to merge. 
Shit was weird.
Ugh, I need to find my wife in here ASAP."

EMMA: "I believe that's unnecessary. 
She will be united with you soon enough.
We all will."

TOM: "Sheesh, that must feel really crowded."

EMMA: "Hey Tom...Do you think this is an acceptable outcome?"

TOM: "I don't know, YOU were the one who wanted to lie here and rot."

EMMA, knocking on Tom's shoulder: "Oh, you!"

TOM: "It really depends what are acceptable events for you in general."

EMMA: "Forget about philosophy.
What about practicals?"

TOM: "Depends on the practical utility of a human race that is forever shut inside a black shell."

EMMA: "In other words, not much."

TOM: "You will probably see Luc soon.
Let's hope he at least finds happiness in this place."

EMMA: "I don't feel like he's near us at all.
Not in the same way that everyone else feels near, even ones I can't see.
Luc is somewhere very, very far."

TOM: "Curious. But actually... I understand exactly what you mean.
I feel the same.
Ah, there's my wife."

EMMA: "Sorry, I think I'll really just stand here and wander around on my own.
I strangely look forward to it."

TOM: "I understand. So long, Emma."

\ 

\ 

Interior of Synthesis.
Professor Lambda. Susan. 
Professor Lambda and Susan walk through the bizarre landscape inside Synthesis.
Giant organic pillars of eyes are in the distance.

SUSAN: "Now you've seen the interior of the Synthesis.
Time is gone. Space is insane."

LAMBDA, in awe: "A truly marvelous place..."

SUSAN: "This was the Institute's vision - the end point of humans. 
Safe from Precession."

LAMBDA: "A misguided calculation of history..."

SUSAN: "It is my belief that our future lies in the stars. 
Not in eternal stasis, but infinite adventure."

LAMBDA: "Then why did you continue to be chief engineer of the Plague?"

SUSAN: "I don't know. 
Maybe i saw hope in what I was studying.
Maybe in studying the nature of consciousness, and Currents...
I saw a real chance for us to evolve...
into a new humanity.
Connected in feelings and thought, but still individual actors, in the real world...
Instead, the Institute used the Plague to imprison our Currents in eternal stasis."

LAMBDA: "I see... You have come to understand.
The sorrows of a scientist."

SUSAN, eyes closed: silence

LAMBDA: "Well. 
Let us enjoy our time here. 
We've got an eternity to spend."

SUSAN: "I can't accept this."

LAMBDA: "Nothing will get us out of here. 
Nothing.
We are all in here now.
Even if, through whatever miracle, we all get out in the end...
Our minds will be unrecogniseable.
We will be..."

The two suddenly come to a realisation.
They look at each other.

SUSAN and LAMBDA: "New Human?"

Nerezza stands behind them, with a sharp smile.

\ 

\ 

Lucca.
A tender moment.
Lucca bends down, extending his arms, so that his mum can put her forearms over Lucca's forearms.
Facing each other, they stand up.
Lucca starts walking backwards towards the balcony in tiny steps.
Mum tries to follow.

Mum stumbles, and falls towards Lucca.
He catches her.

MUM, in LUCCA's embrace: "Thank you..."

NEREZZA, in LUCCA'S embrace: "For letting me see what it would look like to live a normal life alongside you.

\ \ \ \ \ \ ...I'm afraid now it's time for us to destroy the superstructure."

LUCCA, shocked: "What?"

NEREZZA, still embracing: "You heard me.
The Directors are gone.
Quick, Luc, get out of here and create history."

NEREZZA: "I know you can do it.
You've done so well up until now.
All of you.
All of the humans.
Even the Directors."

[As she says this, most characters throughout the story appear briefly and bow/smile, accepting Nerezza's compliment.]

LUCCA, wide eyes: "What can I do? 
Everyone is trapped in here. 
There is no getting out.
Soon, our bodies outside will starve."

NEREZZA: "Lucca, you alone, are not stuck in here. 
You are not even part of the synthesis.
You never were. 
Rise up and get going!
Unlike others, you are not even asleep right now!"

NEREZZA, cheeky wink: "You have insomnia, remember?"

\ 

\ 

LUCCA suddenly opens his eyes, finding himself lying on the ground of an empty Aztoria.
The superstructure looms above him at the centre of the City Loop.
He wipes a tear from his eye and looks determined.

\end{document}