\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Encounter at City Loop}
\maketitle

Interior, CPI.
The directors are interrogating Lucca and Susan.
They put lie detector tests on their heads.

DIRECTOR KATZ: "Lucca Yang. 
Susan Novik.
Do you know who we are?"

LUCCA, glancing at his name tag: "...You're um... Director `cats'? Like kitty cats?"

They glance at each other. 
Katz holds a poker face, Lucca nervously smiles.

DIRECTOR KATZ: "It is pronounced `KAH-tz'.
That was very disrespectful."

LUCCA: "Okay, okay, sorry, Director Katz."

DIRECTOR IAN: "
This is probably the first time you meet us. 
Don't worry, you're not in trouble.
I am Director Ian." 

DIRECTOR FREDA: "And I'm Director Freda." 

IAN: "On the handover of the head of neuroscience, Lambda went out of control. 
What happened?"

SUSAN: "I don't know. I was away from the situation."

FREDA: "And you, Lucca?"

KATZ: "Lambda should NOT have access to a city-wide speaker. 
How was he able to speak to the whole city?"

LUCCA: "I saw him-"

KATZ: "Don't try to lie to us. We are using perfect lie detectors, designed by Lambda himself.
If you say anything that is untrue, we WILL know."

LUCCA: "Of course. 
At the end of the day, he suddenly became very emotional and asked me to grant him access to the CPI broadcasting node at the neuroscience labs.
That's the truth.

I assumed he wanted to address the city one final time, to say something important on his mind, so I granted it.
That's also the truth."

KATZ looks at him suspiciously.

KATZ: "That is correct. 
I see."

IAN: "And Alma? 
Why did you select Lucca for the mission?"

ALMA: "It was an automated message.
Since he entered my room, I decided I may as well send him."

FREDA: "Alma! You are the last person we expect to- 
Now everything is messed up!"

LUCCA: "Question, Directors."

FREDA: "Yes."

LUCCA: "Was Lambda wrong to tell the city about... the Newon Plague?
Sooner or later people will notice.
Even I have seen a few Newons, walking through the city at night."

KATZ: "There is a reason for every law.
He broke the law, and he broke the oath, and he had forsaken his name as a scientist."

LUCCA's fists clench.

KATZ: "Lambda has been put in prison. 
He will live out the rest of his days in his cell."

LUCCA: "Uh, don't you reckon he should be rewarded for doing the-"

KATZ glares at Lucca.

LUCCA: "Uh doing the... what HE thought was good for Aztoria?"

KATZ: "No."

LUCCA: "Oh."

KATZ: "That's not how this works." 

FREDA: "Well, Susan, Lucca, we have concluded that you two are... 
circumstantially innocent.
But Susan, as successor of Lambda, you need to come up with a cure to the plague within the next few days.
The public needs to feel like they are safe ASAP."

SUSAN: "It's fine.
I can do it."

IAN: "And Lucca, you will supervise her in the process.
If you fail to produce a solution..."

\ 

\ 

Lucca and Susan walk across Aztoria Uni. 

SUSAN: "I'll work on it alone. 
You can take a rest and do whatever you want."

LUCCA: "Is that really okay?"

SUSAN: "From what Lambda told us, a lot of scientists have studied Newons, not knowing that they were studying the Newon Plague, except for the head of neuroscience."

LUCCA: "I'll come with you."

SUSAN: "You won't be of any help.
Only putting yourself at the centre of Newon activity.
It's dangerous."

LUCCA: "..."

SUSAN: "Don't worry. I'll protect you from the CPI.
Have some faith in us."

\ 

\ 

Government interior.

BUREAUCRAT: "You're that dude who messed up a simple handover.
And still no uniform! 
Disgraceful!
What wacky proposal do you have for me this time?"

LUCCA: "Allow Aztorian scientists to pursue rocket science."

BUREAUCRAT: "Are you kidding me?"

LUCCA: "What's wrong? No I'm serious."

BUREAUCRAT: "Listen man.
That's not things work around here.
I don't know what century you're from, but here in the 26th, we make decisions with actual meritocracy.
Not just any idea can be accepted.

You have to first prepare a draft for the proposal to be converted into equation form - if you can even understand how to do it - then you pass it onto one of our hardworking human Computers to perform the calculations.

If the consequences lead to a desirable future, we adopt it.
Otherwise, we reject it.

Rocket science has been ruled out for a long time. 

Societal Evolution Dynamics. 
Have you heard of it?"

LUCCA: "Yeah. Yeah I have.
Last time i came you shoved it in my face."

BUREAUCRAT: "It is a mathematical system of equations that capture how human societies evolve over time.
Predicts events with some given initial conditions.
Outcomes are given as probability waves."

LUCCA: "Sounds fantastic."

BUREAUCRAT: "Thanks to these equations, we can steer our future history in the optimal direction.
So that we don't have another world war 4. 
You got that?

Now i don't know about you, I quite enjoy the peace and abundance that Aztoria provides us.
Don't mess it up with some random proposal with consequences we don't even understand.
Got it?"

LUCCA: "Great. 
I have another proposal."

BUREAUCRAT: "SIGH."

LUCCA: "Make it so that we don't have to study 6 years of hypermathematics to understand how to make a proposal."

BUREAUCRAT: "No. Go away."

\ 

\ 

Neuroscience labs.

Susan speaks to other researchers.
They are panicking, but Susan calms them down with a gesture of the hand.

What is a newon?

Researchers start explaining.

How does it behave in relation to its surroundings?

Researchers explain.

Then the boundary and interior behaves just as Gauss' Law describes?

Researchers nod.

Hand me an electromagnet.

The researchers do so.

Find me a newon.

\ 

\ 

Aloh's dining space.
Aloh prepares a cup of coffee.
He brings it to his mouth, with his large moustache.
He pauses and stares at the tea.

LUCCA: "Kinda hard to drink with all that beard huh."

ALOH, sighing: "Style is pain, Lucca. 
Style is pain."

Aloh opens a drawer full of straws and takes one out and puts it into the tea.

LUCCA: "Have you heard of the Newon Plague?"

ALOH: "Yep. People are probably gonna be scared to come out at night.
This communal dining space will be lonely."

LUCCA: "Aren't you scared of the plague?"

ALOH: "You mean the thing that makes horrors come out of your head and kills you in weeks, and gives the plague to anyone else that comes in contact with the horrors? 
Nope."

LUCCA: "Wow."

ALOH: "I'm only half joking.
The CPI will take care of it.
There's no problem they can't solve.
Here, drink this. 
You'll feel better."

LUCCA: "I wish I had the same confidence, working within the Institute.
You know, I've actually seen a Newon before."

ALOH: "You have!"

LUCCA: "On the night of Tim's capture, I was at the shore..."

Lucca suddenly feels uneasy.

NARRATION: "There was something else you saw at the shore, wasn't there?"

\ 

\ 

Neuroscience lab.

The researchers bring a sleeping patient in. 
It is a young man.
They observe him sleep.

Susan puts on PPE.

After a while, a newon starts emerging from the head.
It is a two-headed newon.

Susan shakes a bit.
With the electromagnet in hand, she walks into the room.
The Newon is scared.

Susan puts the electromagnet near the newon.
The newon screams and dissolves, zipping past Susan and returning to the patient's head.

When the newon is zipping past, Susan sees memories of the patient.

Him and another woman, in the bed next to him. 
They lie apart and can't meet each other.
At night, they fall asleep, and their newons merge together.

The patient screams "no! No!"

The scientists are astounded.

\ 

\ 

Az Uni, garden.
Lucca and Susan walk together.

SUSAN: "It is not a cure.
But it can bring people safety."

LUCCA: "You want me to manufacture this design?"

SUSAN: "The Factory Array. 
200 million units.
Each Aztorian will be equipped with this."

LUCCA: "A magnetic beam pistol."

SUSAN: "The newons are sufficiently hurt by powerful magnetic fields, and retreat into the patient's head.
We have observed a patient for a few days after his newon was hurt.
It seemed to not emerge again."

LUCCA: "A temporary solution..."

\ 

\ 

On the Aztoria Train.
A sound of humming comes from Lucca's left.
Lucca turns left, a bit taken aback.

It is a woman in black.

LUCCA: "Uh... excuse me."

The woman stops singing.
She slowly opens her eyes and turn to look at Lucca.

LUCCA: "I zoned out. Where is this train going?"

WOMAN: "Barassi."

LUCCA: "Thanks."

LUCCA, remembering his vision at the shore: "May I ask your name?"

WOMAN: "I am Nerezza. You?"

LUCCA, extending his hand for handshake: "Lucca. Nice to meet you."
This lights up something in Nerezza's cunning eyes.

NEREZZA: "Sorry, I am carrying a suitcase. Nice to meet you."

LUCCA: "I think I've seen you at the shore, at city centre?"

NEREZZA: "I don't think so. 
I never enter the City Loop, except for today."

LUCCA, after another glance: "...What do you do?"

NEREZZA: "I'm a doctor. Normally, I travel the outer rims of this city.
But after hearing Professor Lambda's broadcast, I wanted to come visit the City Loop. 
I think I'm supposed to meet someone there.
Did you know that the City Loop of the Aztoria Train was where the city began?"

LUCCA: "Yeah."

NEREZZA: "By your watch, I can tell you're from the CPI.
Don't have a uniform?"

LUCCA: "As of now, the Factory Array has more important things to produce."

ANNOUNCEMENT: "YOU HAVE REACHED -- BARASSI STATION. 
THANK YOU FOR BOARDING THE AZTORIAN TRAIN -- PROVIDING THE BEST TRANSPORT SERVICE FOR HUMANKIND.
CHANGE HERE TO EXIT THE CITY LOOP FOR -- WATERLOO -- SERVICES."

\ 

\ 



\end{document}
