\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{The Spaceport Revolution}
\maketitle

Emma is singing in Aloh's dining area.

EMMA, singing: "Born out of ancient stars, a future no one can see.
Stars on the ground are the city lights, and the night becomes a silver screen.

Precession of history, evolution of human deeds.
City lights have a tale to tell, and an end is a start as well..."

\ 

\ 

Exterior, one of the outer distrcits. 
It is a long gate.
Beyond which, in the distance, is a grand and retired spaceport.
There are a lot of people standing in front of the gate.
A working man with hat and shovel stand at the forefront, together with hundreds of other workers. 
Colossal demolition vehicles stand in the background. inert.
Director KATZ stands in front of the scene, leading a team of Institute agents. 
It is a strike.

DIRECTOR KATZ: "What's the matter, dear citizens."

WORKER: "We won't demolish this spaceport.
We will wait for the day we can return it to its former glory."

DIRECTOR KATZ: "The city needs the materials from this spaceport elsewhere. 
I would show you the equations of SED, if you could even understand it."

WORKER B: "We may not understand the esoteric equations, but we have the intuition.
Throughout the ages, we have been the arms that build civilisation.
We know these projects most intimately.
We have been following all major construction projects in recent decades.
All of them - ALL of them - are of the form `expand one distrcit, shrink another one somewhere else.' 
`Destroy one district, build up another one somewhere else.'
Do you understand how that seems to us, like a ploy to waste all of humanity's productive potential?"

WORKER A: "On top of that, we've been asked to demolish these space ports one after another. 
This space port represents humanity's final stand against the vast space."

DIRECTOR KATZ, [Nerezza's image briefly flashes by in the background]: "Leave the worrying for humanity to us. 
Your job is to live, eat, and not start a scene."

WORKER: "We've waited long enough.
No more destruction! 
We ask for fulfilment of our promise!
Or at least an explanation!"

Residents of the district come outdoors and observe with concern.

DIRECTOR KATZ, in esoteric, disconnected form of speaking, quoting one of the popularised phrases of SED: "Civil projects in and of themselves, uses the wonderful productive power of humans to transform their surroundings. 
It is a symbol of-"

WORKER A: "What does any of that gibberish actually mean practically?"

DIRECTOR KATZ: "I have tried to explain and you fail to understand.
Enough drama.
Stop this at once. 
Get into the vehicles."

WORKER, hostile smile: "In the end you still have to rely on ordering us, huh? 
Without us you are nothing after all."

DIRECTOR KATZ, unimpressed: "Centuries of peace and abundance have made you people spoiled."

WORKER: "We are so lucky that we are not revolting because we're being starved to death.
I can't deny that you have brought us unprecedented advancements.
But today has today's problems.
We are not about to let humanity die on this planet."

DIRECTOR KATZ: "What a shame, we had hoped for you to have the dignity of demolishing the spaceport yourselves. Oh well. 
It's about time anyway."

DIRECTOR KATZ, calling the other Directors: "Type R event at Ocean Spaceport.
Send reinforcement."

\ 

\ 

Aloh's dining space.
A large explosion can be heard. 
Lucca, Emma and Aloh all look towards the noise, coming from the coast.

LUCCA: "The event has arrived."

A person barges into the dining space.

PERSON, shouting: "did you guys hear that?"

ALOH: "Yeah. What happened?"

PERSON: "It's the Ocean Spaceport! 
The Institute just destroyed it! 
It was an L-2 bomb!"

EMMA: "The spaceport? THE last spaceport?"

PERSON: "Apparently earlier there was a strike."

As he says this, we cut to the workers on the ground, some crying at the explosion in the distance past the gates.
A beautiful thing had been destroyed.
Most residents are fleeing the scene. 

LUCCA: "I'm heading to the Institute."

EMMA: "Can i please come?"

LUCCA: "You stay right here. When the masses arrive, join them on the streets. 
I'm only looking out for my own safety. I need to be safe within the Institute.
After whatever transpires, Aztoria - and the human race - is likely to be unrecognizeable.
Emma, what will you do afterwards?"

EMMA: "I wanna take on another course at the Aztoria University.
Maybe rocketry. 
What about you?"

LUCCA: "Return to the Factory Array as a mechanical engineer."

Emma looks towards him with moisture in her eyes.

ALOH: "Finish the drink before you go."

\ 

\ 

[NARRATION: At 3pm of October 9th, 2591, the news of the Spaceport Incident has spread across the entire society by mouth.
After centuries of peace, this kind of event is a whiplash to the citizens of Aztoria.
The Institute tries to release news articles, but no one has the heart to read them.
The social consciousness is at an unprecedented scale.]

Interior, Institute's broadcast room.
Director Freda walks in, Lucca, Rachel and a few other normal agents are sitting inside.

DIRECTOR FREDA: "Great, you are all here.
There is a mass movement outside.
Quickly write a script to address the city. 
The minister of relations will supervise your work."

\ 

Interior, Institute's emergency meeting room. 
Board of Directors. 

DIRECTOR FREDA: "More agents than usual today."

DIRECTOR IAN: "Of course, all of our agents congregated at the headquarter.
This is a historical event."

DIRECTOR KATZ: "So, that really backfired."

DIRECTOR IAN: "We have grown cocky.
It seems, KATZ, that being Director doesn't mean we can direct EVERYTHING."

DIRECTOR FREDA: "One more lesson to put into the SED equations."

FIRST DIRECTOR [as always, we can only see their back]: "The equations of SED predicts our disappearance from history.
That's the truth."

DIRECTOR FREDA: "First Director... The equations are not deterministic!"

FIRST DIRECTOR: "They are not. In the sense that they do not predetermine events.
And we have been able to delay emergent movements for 400 years.
But laws are laws, and a system in high tension must crumble, just as a heavy star must eventually undergo supernova.
Imagine... tension built up for 400 years..."

DIRECTOR IAN: "I personally tend to the equations. 
I can confirm that for a state-bureaucratic system in post scarcity, with a central authority that maintains peace but nonetheless refuses to die, after t = 320 years, certain type R events are enough to send the entire society into a revolution."

Freda and KATZ look down. 
Nerezza's image birefly flashes in a corner of the room.

FIRST DIRECTOR: "Let me ask you all to consider something. 
Way back before the birth of Aztoria, when we were still part of the final world war, the bureaucracy could justify its existence.

"We needed a strong leadership to protect against foreign threats.
We didn't even need our own military - we borrowed them from the Eurasian continental forces.

"Protection, protection, protection... against foreign threats. That's what we always say.

"But now earth is at peace, and humans only populate in Oceania.
Material is managed by an all-intelligent supply and distribution chain.
The Factory Arrays are well maintained with engineers from the greatest, Aztoria University.
Computers in the government process requests for all reforms, minor and major. 
The minds in Aztoria University are over-adequate for studying and researching the SED equations.

"So wait a moment - why DO we exist? 

"The only threats now come from within.
We've become... enemy of the people.
And enemies to history.
Enemies to the true desires of an awakened humankind."

Director Alma gives a sharp stare and an extremely subtle hint of a smile.

DIRECTOR FREDA: "We cannot let humankind do as it wills."

FIRST DIRECTOR: "Maybe."

DIRECTOR IAN: "We are still committed to the Synthesis Project.
Better to have humans in eternal stasis than to let them stumble into darkness again and again."

DIRECTOR KATZ: "Precession is a real threat."

FIRST DIRECTOR: "Alma, you've been quiet."

DIRECTOR ALMA: "I'm thinking about what to say to the city."

DIRECTOR KATZ: "That won't be necessary. 
We have a speech prepared. 
You just need to read the script."

\ 

We switch to outside the building.

\ 

\ 

Exterior, 500 meters away from Institute headquarters.
A young working man with a worker's hat stands at the front of a million-crowd.
A few lines of the Institute agents block their path.

MAN: "Join us! So that we can endlessly advance!"

AGENT: "We can't."

As he says this, about half of the agents walk over to the other side, joining the crowd.
The crowd marches on anyways, and the agents can do nothing but to be swept through by the crowd. 

\ 

ALMA, SPEAKER: "Citizens. I am Director Alma of the Civil Protection Institute.
You have all done so well up until now."

\ 

Alma is standing outside the Institute's building.
The entire city stops.
The Directors look at her through a screen.

ALMA, with a sudden grace that is unseen in the story until this point, as if a heavy burden is about to be lifted: "Right this moment, I can hear the dreams of humankind, crying out."

Everyone listens in suffocating silence.
After a long time, Alma looks down at the script handed to her.
THe script says "you must behave, and listen to our guidance. 
For we protect the happiness of all humankind."
She rips it apart.
Lucca's eyes widen.

\ 

ALMA: "PEOPLE! 
DO WHAT YOU THINK MUST BE DONE!
FOLLOW YOUR BRAINS AND DESIRES!
Do what you want to do, and do it for yourselves!
YOU are humankind! 
YOU determine history!
THE DOORS OF THE INSTITUTE, ARE OPEN TO YOU!
IT'S TIME FOR THE BUREAUCRACY, THE INSTITUTE, AND AZTORIA AS WE KNOW IT - TO END!!!"

\ 

THE DIRECTORS ARE ABSOLUTELY STUNNED! THE CROWD MARCHES ON! 
They begin singing the original anthem of the earth federation.
Mrs Korolev, the working man on the A train, the various people we see with working hats throughout the story all can be seen.

CROWD: "Stand up! All people of the earth! 
Stand up! You prisoners of war!
Machines! Have given us abundance,
now let us make them work for good! 

The old world, crumbles into nothing! 
All people, arise! Arise! 
And then, the vanity of empires,
makes way for humankind!

This is the final struggle! 
Solidarity till tomorrow!
A new earth federation,
unites the human race! 

This is the final struggle!
Solidarity till tomorrow!
A new earth federation,
unites the human race!

\ 

There never ever was a saviour,
nor do we rely on gods and kings.
Gotta create a happiness for humankind,
relying on ourselves!

No more heart to kill each other,
century bells ring loud and clear!
The earth is ready for eruption,
for a reborn humankind!

This is the final struggle! 
Solidarity till tomorrow!
A new earth federation,
unites the human race! 

This is the final struggle!
Solidarity till tomorrow!
A new earth federation,
unites the human race!"

\ 

ALMA, thinking: "Marco, the day has finally come..."
FIRST DIRECTOR: "The original Earth Federation anthem..."

\ 

CROWD: "It's time to grow out of infancy,
for the bureau fears mankind! (DIRECTOR IAN: "what is this? I didn't know there was a 3rd verse.")
The real theory of history, 
reveals at its end one more fight! (DIRECTOR FREDA: "When did they write a new verse??")

Government, Uni and Institute, 
the three pillars of our world;
thanks to you, we have all the things we need - 
to advance humankind! (DIRECTOR FREDA: "...just how long, have they been waiting...")

This is the final struggle!
Solidarity till tomorrow!
The dream! That! we! are! cry-ing! out!
Unites, the human race!

This is the final struggle!
Solidarity till tomorrow!
The dream that we are crying out!
Unites, the human race!"

CROWD, final verse: "Thank you, for ending all of war. (Director Freda, surprised.) Thank you, for giving us the world. (Director Freda cries.) There is just one more step to take, before we forge our own new path!

Here it is, the final graduation, from meaningless precession; (Director Freda and KATZ run out to join the crowd) we're gonna create a true happiness, for all of humankind!

This is the final struggle!
Solidarity till tomorrow!
The dream! That! we! are! cry-ing! out!
Unites, the human race!

This is the final struggle!
Solidarity till tomorrow!
Mankind spread across the stars,
It now, begins, on earth!"

\ 

Interior, Institute's broadcast room.

LUCCA, on speaker: "To those who can't see this, those on the outer rims: 
The Institute will be no more.
Tomorrow will be a new humanity."

DIRECTOR KATZ, hearing this from the meeting room: "It's Lucca! 
I knew it! 
This Institute has been infiltrated from the beginning!
Alma! 
May the universal contempt of humanity fall upon you!"

\ 

He walks out of the meeting room. 
The rest of the directors stare at him.
The entrance of the meeting room shuts behind him, with an unopenable lock. 
Director KATZ realises the board of Directors has shut itself in the room for protection. He grows bitter.

He walks towards the broadcast room with a pistol in hand, and a murderous glare. 
Just as he is about to open the door, a magnetic beam pistol is pointed into his back.

EMMA, wearing Institute uniform disguise: "I'm sorry Director, I'm afraid I can't let you do that."

Director KATZ turns back. 
The computers!
It is the computers from the government that the Institute disbanded months ago. 
They all throw aside their Institute uniform - that must be what Emma used the Factory Array to manufacture!

EMMA: "100 uniforms and deterrence weapons.
Only using 50 kilo watt hours.
The Factory Array really is a work of miracle.
The pinnacle of humanity's creation."

They have infiltrated the Institute. 
One of them is also recognizeable by the readers, appearing in the end of `Monster in District 14', whom had a humorous back and forth with Lucca.

EMMA: "Capture the directors."

They tie up Director KATZ.

COMPUTER A: "The emergency meeting room entrance is shut down!"

EMMA: "Let them hide in there then. 
As long as they are willing to starve.
We will guard this place all the same."

\ 

LUCCA, into mic: "no longer will we be kept in the dark.
The future belongs to all.
With the machines, mechanical creations of humanity's genius, we will reclaim the Northern Hemisphere.
And afterwards, we will explore space, expanding the boundaries of our knowledge."

EMMA, excitedly: "YEAH! YOU TELL EM!"

LUCCA: "There is only-"

\ 

Silence.

\ 

EMMA: "Hm? What happened?"

Emma and the computers open the door.
Lucca is frozen, holding his other phone.
After a long time, he puts the phone down and turns around to meet Emma's eyes.

EMMA: "Hello Luc, we came for you, sorry, hehe."

Lucca is serious.

EMMA: "What's wrong Luc?"

LUCCA: "Tom just called me from the observatories. 
The Newon Cloud is still approaching."

Director KATZ grins.

\end{document}