\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{The Things Troubling Emma}
\maketitle

Interior, Aloh's dining space.

EMMA, propping head up with her elbow: "Hey Luc... Do you remember your time working at the Factory Array?"

LUCCA: "Yep. Clear as ever.
I worked on the mechanical branch of the Factory Array.
Had a great friend called Marco, we talked about all kinds of things during lunch breaks."

EMMA, to herself: "Marco? I don't remember a Marco..."

LUCCA: "What was that?"

EMMA: "Oh, nothing!"

LUCCA: "Of course you don't know Marco.
My friendship with him started as a university thing.
You haven't been around at that time."

EMMA: "And? What was your home life like?"

LUCCA: "Home life? Uh, solitary? I don't know."

LUCCA, packing up: "There's a new case at the Institute.
Say hello to Aloh for me."

EMMA: "Ok, dear."

Emma suddenly realises what she said.
She blushes and looks at Luc with intense sadness.

\ 

\ 

Interior, Tom's house.
At the middle of the busy city centre of Aztoria.
Emma is visiting.

TOM: "You give off a weird vibe. 
What's wrong?"

EMMA: "It's been a year since something weird started.
I started remembering some memories. 
Memories with my husband."

TOM: "You were married?"

EMMA: "As you can see now, I'm alone.
I believe my husband has been erased from my life.
I saw Luc at the reunion.
He doesn't recognize me in the same way i recognize him.
I also found him at a dining space.
For weeks nothing has changed."

TOM: "Now hold on a minute. 
Luc?
Are you saying-"

EMMA: "Tom, surely you remember. 
Do you remember attending our wedding?"

TOM, after a few panels of excruciating contemplation: "Uh, I'm gonna have to say no. No, there was no wedding."

EMMA: "That's really troublesome.
We were married for years. 
He has absolutely no memory of it."

TOM: "I have no memory of it either, if it happened."

EMMA: "I knew it. Maybe the Institute..."

TOM: "Hold on Emma, I'm pretty sure that is impossible."

EMMA: "Who knows? With Professor Lambda's help, the Institute must have invented a ton of technology to control human psychology."

TOM: "Check the Department of Relations. 
If you were married, there should be a record of it."

EMMA: "Ok. True."

EMMA: "Do you think... I'm crazy?"

TOM: "Not for a second. You may have confused something you read in a fiction with actual memory.
Or a dream."

EMMA, blushing: "..."

TOM, playful look on his face: "So... Luc, hey?
I knew it!
You always followed him around.
Got mad when he got together with Susan for a while."

EMMA: "I just don't know how to feel about living in this city.
Every moment, it feels like things will break down.
The Institute... has created a weird environment."

TOM: "If the whole world is consistent and you are the only one with the problem...
Then it's likely it's something to do with you.
But again, if the memories are so vibrant, you may be onto something.
Go check the Department of Relations."

\ 

\ 

Interior, Department of Relations.
Emma is looking through a folder on the table.
The receptionist guides her through it.
Emma tries to follow.

RECEPTIONIST: "You see, we have the list of all registered unions between n individuals. 
You're looking for n=2.
Between the years 2578 and 2591.
Emma...
Emma..."

EMMA: "Mmmmm ok I don't see it."

RECEPTIONIST: "Sorry we couldn't be of more help."

EMMA: "That's ok."

\ 

\ 

Exterior, school excursion.
Kaito is leading his class through the city.
They walk along the Aztorian shore. 
They see the Aztoria Train.
Emma is in the crowd of students too.

KAITO: "The Aztoria Train. 
It is a relic from pre-extinction.
Back when humans populated the entire earth, there was a grand construction project led by the Earth Federation - an inter-continental railway network that connected all of Earth.
It was called the Century Line.

After World War 3, most of it is gone.
All that is left is the Oceania branch of the Century Line.

When the train is active, the entire track is electrified.
Current passes through the tracks, energizing the train.
Thanks to the powerful fusion stations situated near every train station."

KAITO: "Here is the Ocean Spaceport.
At one point, humanity was a space faring species. 
But after the war, we haven't gotten around to it yet.
When most of you grow up, we may have reconstructed the spaceport. 
We may be explorers of the stars and we may reclaim the Northern Hemisphere."

As Kaito says this, he notices Emma kneeling in the crowd, hiding.

KAITO: "Alright, you guys can freely explore for an hour.
We will meet in front of the Waterloo station at 2:30pm."

After the students disperse for free activity, Kaito walks up to Emma kneeling.

KAITO: "Aren't you too old to join a primary school excursion?"

EMMA: "You caught me. 
I'm out of work, so I have nothing to do. 
Thank the earth that I don't have to starve on the streets, but I'm bored.
You're so charismatic as a teacher, Kaito."

KAITO: "I see that means you want something from me. 
What is it?"

EMMA: "Ehehe..."

\ 

\ 

Emma and Kaito sit at a diner.

KAITO: "You're married to Luc? Congrats! Why hasn't he told me about it?"

EMMA: "No, that's not the case. 
I WAS. Past tense."

KAITO: "You married AND divorced?"

EMMA: "Oh, you! You won't listen to what I say!"

KAITO: "Ok ok I'm just kidding.
So, the problem is that you clearly remember having a different life from your present, right?
And no one else around you does."

EMMA: "I think the Institute may have erased it from my memory.
From everyone's memory."

KAITO: "The Institute is the greatest gift humankind could ever ask for.
They wouldn't do something like that."

EMMA: "Well then I'm lost."

Emma starts crying.

KAITO: "Oh... hey... hey...
Let's entertain the thought experiment for a little bit.
Suppose you did have a different life. 
Let's follow the timeline."

EMMA, suddenly sparkly eyed: "YES, YES!"
(Kaito: ...were you even really crying...)

KAITO: "So. 
We all graduate from our highschool. 
You enter the Aztoria University.
You study Societal Evolution Dynamics to become a human computer at the government.
I study education to become a teacher.
Tom studies astrophysics - a rarely permitted subject.
Lucca studies mechanical engineering.

"We enter our respective workplaces. 
You enter the now-gone government.
Lucca enters the Factory Array. (Picture of Lucca with a working hat)
Years later, he gets promoted to the Civil Protection Institute, who is now the effective governing body of Aztoria.

"Now the government is gone, the Institute takes over, and you start having memories of a life spent with Luc."

EMMA: "Correct."

KAITO: "Then the years of your marriage must have been during the gap of Lucca entering the Factory Array, and before he enters the Institute.

The Institute, for whatever reason, erased the time from your memory, and his memory, and all of our memory. 
That means we - Tom, Susan, I - must also have some gaps in our own timelines.
That is not the case.
I remember every single class I raised. 
The number simply cannot fit into a shortened time frame. 
I definitely remember full 8 years of my life, first 5 with the preivious class, next 3 with my current class."

EMMA: "You're right.
And there is no good reason for the Institute to do it. 
And there is nothing special about Luc, or me."

KAITO: "Exactly. They are too busy organising us on the civilisation scale."

EMMA: "mmmmm."

KAITO: "Even if something did happen...
Now you're with him again, and you can start rebuilding things right?"

EMMA: "I've been trying, i've been trying. 
Going on investigations... I hope the activities can mimic what we had done in the past."

KAITO: "Why not tell him everything?"

EMMA: "Do you really think he will think I'm honest?
He will think i'm making it up, coming onto him too strongly and I'll scare him away.
He hates pretenses."

EMMA, face buried in hands: "Ugh! This is such a mess."

KAITO, thinking: "The Institute wouldn't...
That's just not something the Institute would do!"


\ 

\ 

Emma walks alone through the streets at dusk, following the same path Lucca took in chapter 1.
It begins raining, and this makes her happy. 
She starts dancing and singing her way towards Aloh's dining space.
She performs the song "get on the A Train".



\end{document}

%life with lucca at the factory array, wearing working garb