\documentclass[11pt]{article}

% \usepackage{fullpage}

\setlength{\parskip}{10pt}


\begin{document}
\ttfamily
\title{Mystery in the Aztorian Sky}
\maketitle

Balcony, night.
Alex is stargazing through a telescope.

\ 

[NARRATION: "Alex likes to stargaze.

Nothing compares with the beauty, challenge, and mystery of space.

Darkness and lights of infinite depth.

Convolutions between space and time, uniting as one.

On some level, he must have expected that that's where humanity's future lies.

Pursuing truth, beauty, and knowledge.

Alex dreams that one day, he may go up there himself.

Becoming one with the ocean of stars."]

\ 

Alex works at a piano moving organisation.
They are currently hanging halfway high on a building, trying to bring a piano up.
[NARRATION: "During the day, Alex works like any other.
Be careful Alex, falling asleep is very dangerous when working in such places!"]

COWORKER A: "Careful!"

The coworker catches Alex, but his hammer falls down.

COWORKER A, to people below: "HAMMER!"

\ 

Lunch break. 
Alex clutching his head.

COWORKER A: "Alex, if this happens again, we're gonna have to get you fired for YOUR safety."

\ 

\ 

Riding bike on way home.
Alex passes a patch of grass, parks his bike and observes something in the distance. 

BOY: "Hello!
You dropped something."

He hands him binoculars.

ALEX: "Thanks."

\ 

Alex pushes his bike while walking, with boy next to him. 

BOY: "You look sleepy. 
What's wrong with ya?"

ALEX explains: "Have you noticed how bright the city lights are at night?
I have to stargaze at midnight, when the lights are lower.
That's why i'm sleepy all day.
Does that make sense?"

BOY: "Mmhm. Sounds fun.
Alright I have to go now. See ya!"

ALEX: "See ya."

\ 

\ 

Night, Alex's balcony.
He notices something wrong.
He runs back inside, grabs an image he took in the past, of the same patch of sky, and compares it against the current sky. 

ALEX: "How did I not see this yesterday!
A star, a star at the edge of a constellation, it's gone!"

ALEX: "It can't be that the star died.
A supernova happens over a really long time.
And there should be a nebula left behind."

ALEX, running out of his apartment: "I have to let someone know!"

ALEX, banging on a door: "WAKE UP! WAKE UP!"

WORKER A, opening the door, looking big and scary: "STOP IT YOU LUNATIC!"

ALEX: "WHAAAAA it's a monster!"

WORKER A: "No, idiot.
Whatsh the matter now?"

ALEX: "A star disappeared from the sky!"

WORKER A: "Ah yer crazy, get outta here!
You musta been dreaming."

\ 

Interior, Alex's bedroom.
ALEX: "...Maybe I should call the Institute."

\ 

\ 

Interior, Institute. 
An agent is sleeping on the control panel.
The phone rings, waking him up.

AGENT A: "Hello. Private citizen? Alright, put him through."

PHONE: inaudible.

AGENT A: "Yes, yes, this is the Civil Protection Institute."

PHONE: inaudible. 

AGENT A: "What? A star disappeared?
(grabbing a pen and paper)
Could you provide an exact coordinate?
Yes. Yes."

ALMA, walking in: "What's the problem?"

AGENT A: "An amateur astronomer. He said he saw a star disappear."

RACHEL, leaning against a wall: "Those amateurs are always seeing things."

LUCCA, holding a phone: "The observation towers report no anomaly. 
The star is still there."

RACHEL: "Told ya."

LUCCA: "Maybe it was a passing asteroid?"

ALMA: "Blocking the light from the star. Possibly. 
Check the observatories."

\ 

Rachel: "Hello? State Observatory? Civil Protection Institute speaking.
...No asteroid?"

AGENT A: "Hello? Cyan Hills Observatory? This is the Civil Protection Institute. 
...So no asteroid or anything like that?"

LUCCA: "Hello, Aztoria University Observatory? Can I get professor Tom Misko?"

\ 

RACHEL: "No results."

AGENT A: "I guess that's it. 
A false alarm."

\ 

\ 

Exterior, at a park. 
Tom and Lucca observe the night sky.

TOM: "The stars seem brighter than before."

LUCCA: "Because the city lights are low."

TOM, smiling: "Yeah, romantic, isn't it."

TOM, with binoculars: "Hmm. Nothing wrong with the star, that's for sure."

LUCCA: "What do you think it could have been?"

TOM: "There are many things in space that can obstruct light from a distant star. 
But if it is something in space, the observatories can pick up on it.
In other words, I have no idea."

TOM: "Well. It's time for me to head home.
I'm getting sleepy."

LUCCA, Nerezza standing in the background in a flash: "I don't feel sleepy at all."

TOM: "I too would have a hard time sleeping if there's a mystery going on.
But you have to learn to sleep.
My career depends on being able to sleep while there are 10 unsolved problems going on, heh."

\ 

\ 

Morning, on way to work.
Alex lies on the grass.
A ball hits his face.

GIRL: "Sorry, mister, that's our ball."

ALEX: "Here."

GIRL: "Thanks!"

The boy separates from the baseball group and slides down the grass slope.

ALEX: "Oh hey it's you again."

BOY, sitting next: "Yeah. Did you find something strange last night?"

Alex turns and stares at the boy.

ALEX: "*Should* I have found something?"

BOY: "Oh idk. It's just that you looked bored with your life, so I hoped you found something interesting in the night sky."

ALEX: "Heh, you're right.
Well, at the usual time of my stargazing, I found a star missing. 
I called the Institute about it."

BOY: "And they didn't believe you, did they."

ALEX: "That's right.
When I looked later, i think I saw the star there again.
So I probably looked wrongly."

BOY: "Aw, sorry to hear that.
But, if you tune your telescope tonight, you're sure to find something special. 
See ya."

ALEX: "Bye."

BOY, not looking back: "Watch the sky in the north."

\ 

\ 

Night, usual time on Alex's balcony.

ALEX: "It's not there... It's definitely not there!"

Alex runs to his neighbour, comically grabs WORKER A, and runs to his balcony.

ALEX: "You gotta see this!"

WORKER A: "Hey hey hey"

They are now at Alex's telescope.
Worker A puts his closed eye up to the telescope.

WORKER A: "Huh? Everything's just black."

ALEX: "You need to see with the eye that's actually open."

WORKER A, switching eyes: "Oh."

WORKER A, after looking back and forth between the star and Alex's photograph: "What the- it really is gone!"

ALEX: "I'll take some pictures!"

\ 

\ 

Interior, Institute.
Lucca is holding the photos in front of Director Alma. 

ALMA: "Go meet this astronomer.
Find out what's happening."

\ 

\ 

Day, exterior, grass slope. 
The boy looks just a bit more uncanny, very, very subtly deformed.
Like a Newon.

ALEX: "Don't like this place."

BOY: "Huh? What about your friends?"

ALEX: "Eh... I try to get along with people and I manage, I guess.
But I don't really have that many."

BOY: "Not even a girlfriend you can bring home?"

ALEX: "Tsh, how old are you. 
What do you know."

BOY: "Hmm... If no one on earth cares about you, you might as well leave this place.
Hey, you know what? 
I'll take you up to the sea of the stars some day."

ALEX: "*You?*"

BOY: "Hell yeah!
We'll journey through the universe, just the two of us.
You can be the captain of our own ship."

ALEX: "Sounds fun."

BOY: "You know, I have a massive collection of telescopes.
You should come visit with my friends."

The two leave the grass slope.
Behind them, Lucca and Nerezza stand, facing each other.

\ 

\ 

Interior, Aztoria Train, dusk.
Lucca and Nerezza both take the train.
Nerezza holds her suitcase.

LUCCA: "You went for the man sitting at the lake."

NEREZZA: "So did you."

LUCCA: "What are you going to do this time?"

NEREZZA: "I'm a doctor, remember?"

LUCCA: "A doctor of death.
So you're going to euthanise him. 
Did he order for your service?"

NEREZZA: "Not yet. I am only observing."

LUCCA: "Why?"

NEREZZA: "Why do you work for the Institute, Lucca?"

LUCCA: "I work for the happiness of humankind."

NEREZZA: "And what does that happiness look like?"

LUCCA: "Just wait a minute... am I really going to lose another civilisan to you?"

NEREZZA: "But he wasn't yours to begin with, Luc.
Have some faith in his own decision."

LUCCA: silence

NEREZZA, satisfied smile: "Forget that. Look at those buildings."

They see colossal concrete prismatic structures standing in the distance.

NEREZZA: "They look like buildings, but there are no windows or doors.
Just solid blocks of concrete.
What could they be for?"

LUCCA: "..."

NEREZZA, shriek of laughter: "Isn't this city so weird? HAHAHAHA!"

Lucca only sits there in silence.

\ 

\ 

Dusk, Aloh's dining space.

EMMA: "A star disappearing?"

LUCCA: "Yeah. I wonder what could cause it."

EMMA: "If it's consistently observed to disappear from only his telescope, then there might be a problem with the telescope."

LUCCA: "According to him, it's visible with the naked eye, when the city lights are low."

EMMA: "Maybe it's a problem with his eyes."

LUCCA: "He has also taken pictures of the sky."

EMMA: "Then it's a problem with his camera."

LUCCA: "Hm. If there's a problem with everything, then maybe it is possible for the star to straight up disappear. 
Just a problem with the universe."

EMMA, knocking his shoulder: "Oh, you!"

\ 

\ 

Interior, night, boy's home.

ALEX: "Where are your friends?
And where are your parents?"

BOY (looking tremendously deformed, like a Newon): "Oh, they aren't home.
They've been gone for a long time."

Alex feels a tinge of unease.

BOY: "Check out these telescopes."

ALEX: "Wow, they're quite amazing."

BOY: "You wait here, let me get some tea."

The boy exits the room.
Alex looks through the telescope, at the star.

After a while, when the door reopens, we see what became of the boy as a silhouette against the light coming from outside the door.

\ \ \ \ The boy is a Newon. His body shape is grotesque.

Alex slowly turns.

NEWON: "Alex."

ALEX: silence, clearly in shock.

NEWON: "It's been hard since my parents left me.
Do you know?
There is an alien space fleet approaching from that star.
It is undetectable with advanced equipment, only amateur telescopes.
It must be an alien space fleet. 
It is coming to pick us up."

ALEX: silence

NEWON: "Join me, Alex, and together we will achieve something grand. 
A Grand Synthesis. 
That's what the fleet is telling me.
Come, and become one with the ocean of stars."

Alex kneels down, his head going down more.
A tear escapes his eyes.

\ 

\ 

Interior, Institute.
Lucca is observing the night sky. 
Alma is sipping coffee.
One hour pass. Then another.

LUCCA: "Not very easy to see."

ALMA: "Gotta wait until the city lights are low."

Lucca's eyes widen as he hears this.

LUCCA: "Wait until... the city lights are low..."

\ 

\ 

ALEX: "I didn't know you had the plague...
I'm so sorry..."

NEWON, less coherently: "Join join join us, the apples are glass.
A-A-A-A Train."

ALEX, hopeful and lively stare: "I'm sorry.
Your speech is becoming incoherent.
I am not going with you."

NEREZZA, suddenly appearing and caressing his head, about to put on her device: "Is this really okay?
You have a chance to travel across the universe, pursuing truth..."

ALEX, pushing her hands away, causing her to smile: "No, it's okay. 
The Institute is protecting us.
I know exactly what to do."

ALEX, taking out the magnetic beam pistol in his pocket: "You are a Newon.
And you are destroyable with a magnetic field.
This magnetic beam pistol will do.
An electro-mechanical creation by humanity's genius."

ALEX, pointing the pistol towards the newon: "Thank you.
In our brief meeting, I felt understood."

After the shot, Alex stands alone in the room. 

\ 

Suddenly, the phone in his pocket rings.

LUCCA: "Hello Alex. I am from the Civil Protection Institute.
Is this the number you used to call us?"

ALEX: "Ah, yes! How can I help you?"

LUCCA: "Come visit us at the Institute headquarters. 
I think I have an answer for what's happening in the sky."

\ 

\ 

Interior, Institute.
Institute has a balcony.
Lucca, Alex, Alma, Emma, Tom all stand there.

LUCCA: "Right now, the star is still there."

ALEX: "I see."

LUCCA: "So Alex, do you stargaze every night?"

ALEX: "Yep."

LUCCA: "When do you stargaze?"

ALEX: "When the city lights become pretty much gone."

LUCCA: "Every night?"

ALEX: "Every night."

ALMA: "We shut down most of the city lights by 11 pm."

LUCCA: "And that is when you look up into the sky."

ALEX: "Mmhm."

It is 11pm. 
We see the city lights shut down one area by another.
Soon, we see the star disappear.

LUCCA: "That is the problem, Alex.
The problem is not just with a location on the star map, but also with *time*.
If I am to say to you `hey, let's meet at the library.'
You wouldn't know when.
If I only say `hey, let's meet next Wednesday.'
You would go `...WHERE?'"

ALEX: "Makes sense so far."

LUCCA: "In general, events require both a space AND time coordinate.
So let us discuss that.
Let us refine the question: you observe the star disappear every night at around 11pm, and the star reappears by the time we observe it, at midnight.
The star's disappearance is a periodic event.
What else is a periodic event?"

ALEX: "I... I don't..."

TOM: "It is the earth's rotation."

LUCCA, slowly: "*Suppose there was something not far in space, but very close to earth, so close that it's actually within the earth's atmosphere...*"

We see a diagram with the earth, an object with question mark, and a distant star.

LUCCA: "Every day during earth's rotation, there is only ONE tiny window, when the object just so happens to obstruct the light from THAT location in the star map."

LUCCA: "After the time period, earth has rotated far enough such that the star in the background has moved out of the way of the object."

ALEX: "The star is back again!"

EMMA: "And it has moved upwards in the sky.
If you care to observe the original place, you will notice, that a new star has disappeared - in the position associated with whatever object is there."

ALEX: "You're right!"

LUCCA: "Something massive is approaching very slowly from the skies of the Northern Hemisphere."

ALMA: "We believe it is a Newon Cloud, billions of Newons, for whatever reason, a huge mass of it had been at the Northern Hemisphere."

ALEX: "Whoa..."

TOM: "It's a remarkable discovery."

LUCCA, thinking in his head: a grand Synthesis event...

ALMA: "Honestly, no one has the energy to constantly observe every part of the night sky at all times.
It is lucky that you saw it.
Well done Alex, we will take note of this."

\ 

\ 

Morning.
Alex sits peacefully on the grass slope.
In the distance is a colossal, abandoned spaceport.
Looking at it and getting interrupted by the boys and girls behind him playing baseball, Alex smiles.



\end{document}